### 2022-01-17 Check_Data.Rmd
First commit of all files

---
title: "Check_Data"
author: "Amalan"
date: "21/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 7,fig.height = 7,warning = FALSE,message = FALSE)
library(readr)
library(here)
library(dplyr)
library(corrr)
library(corrplot)
library(GGally)
```

# Model 1 Testing

```{r Model 1 Testing}
load(here("Identical_r0","Generate_Big_Data","Model_1","No_Correlated_Covariate.RData"))
Original_Data<-as.data.frame(Simulated_Data$All_Data$Assumed_Model_3)
no_of_Variables<-2

colnames(Original_Data)<-c("Y","X0",paste0("X",1:no_of_Variables),
                           paste0("X",1:no_of_Variables,"^2"))

glm(Y~.-1,data=as.data.frame(Original_Data),family="poisson")->Model_1
stepAIC(Model_1,direction = "backward")
```

# Model 2 Testing

```{r Model 2 Testing}
load(here("Identical_r0","Generate_Big_Data","Model_2","No_Correlated_Covariate.RData"))
Original_Data<-as.data.frame(Simulated_Data$All_Data$Assumed_Model_3)
no_of_Variables<-2
colnames(Original_Data)<-c("Y","X0",paste0("X",1:no_of_Variables),
                           paste0("X",1:no_of_Variables,"^2"))
glm(Y~.-1,data=as.data.frame(Original_Data),family="poisson")->Model_2
stepAIC(Model_2,direction = "backward")
```

# Model 3 Testing

```{r Model 3 Testing}
load(here("Identical_r0","Generate_Big_Data","Model_3","No_Correlated_Covariate.RData"))
Original_Data<-as.data.frame(Simulated_Data$All_Data$Assumed_Model_3)
no_of_Variables<-2
colnames(Original_Data)<-c("Y","X0",paste0("X",1:no_of_Variables),
                           paste0("X",1:no_of_Variables,"^2"))
glm(Y~.-1,data=as.data.frame(Original_Data),family="poisson")->Model_3
stepAIC(Model_3,direction = "backward")
```

# Model 4 Testing

```{r Model 4 Testing}
load(here("Identical_r0","Generate_Big_Data","Model_4","No_Correlated_Covariate.RData"))
Original_Data<-as.data.frame(Simulated_Data$All_Data$Real_Model)
no_of_Variables<-2
colnames(Original_Data)<-c("Y","X0",paste0("X",1:no_of_Variables),
                           paste0("X",1:no_of_Variables,"^2"))
glm(Y~.-1,data=as.data.frame(Original_Data),family="poisson")->Model_4
stepAIC(Model_4,direction = "backward")
```

### 2022-01-17 Identical_r0/Rmarkdown/Classical/OSMAC_Method.Rmd
First commit of all files

---
title: "OSMAC_Method; Model: `r params$Model_Path`; "
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.height = 9,fig.width = 9,message = FALSE,warning=FALSE)
library(ggplot2)
library(here)
library(dplyr)
library(tidyr)
library(gganimate)
library(LaplacesDemon)
library(linguisticsdown)
library(gganimate)
library(viridis)
library(compiler)
library(data.table)
library(ggpubr)

# Cordeiro Bias Estimation ----
Cordeiro<-function(XData,With_bias)
{
  p <- as.vector(exp(XData%*%as.vector(With_bias)))
  W <- diag(p)
  inverse_term <- solve(t(XData)%*%W%*%XData)

  Term1 <- inverse_term%*%t(XData)%*%W
  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))

  bias <- as.vector(Term1%*%Term2)
  return(bias)
}

Cordeiro<-cmpfun(Cordeiro)

FullDataPath<-here("Identical_r0","Generate_Big_Data",params$Model_Path,"No_Correlated_Covariate.RData")
load(here(FullDataPath))
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = "poisson")
Real_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                       "Values"=Simulated_Data$Basic$Theta)
Estimated_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                            "Values"=Full_model$coefficients)
Bias_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),"Values"=0)
```

# OSMAC ;  Response Model : `r params$Model_Path`

## Real Model Data

```{r Load Data}
Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Real_Model/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_RM<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_RM<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_RM<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_RM)<-colnames(Est_Bias_RM)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_RM)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

## Assumed Model Data

### Old Probabilities

```{r Load Data Assumed Models}
Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_Old_1.RData"))

Est_Parameter_AM_Old_1<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_Old_1<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_Old_1<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_Old_1)<-colnames(Est_Bias_AM_Old_1)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_Old_1)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

# Assumed Model 2
load(here(Path,"OSMAC_output_Old_2.RData"))

Est_Parameter_AM_Old_2<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_Old_2<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_Old_2<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_Old_2)<-colnames(Est_Bias_AM_Old_2)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_Old_2)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

# Assumed Model 3

load(here(Path,"OSMAC_output_Old_3.RData"))

Est_Parameter_AM_Old_3<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_Old_3<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_Old_3<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_Old_3)<-colnames(Est_Bias_AM_Old_3)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_Old_3)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

### New Probabilities

```{r Load Data Assumed Models 2}
Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model/")
# Assumed Model 1
load(here(Path,"OSMAC_output_New_1.RData"))

Est_Parameter_AM_New_1<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_New_1<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_New_1<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_New_1)<-colnames(Est_Bias_AM_New_1)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_New_1)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

# Assumed Model 2
load(here(Path,"OSMAC_output_New_2.RData"))

Est_Parameter_AM_New_2<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_New_2<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_New_2<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_New_2)<-colnames(Est_Bias_AM_New_2)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_New_2)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)

# Assumed Model 3
load(here(Path,"OSMAC_output_New_3.RData"))

Est_Parameter_AM_New_3<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                         Results_OSMAC$mVc_Output)

Est_Bias_AM_New_3<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                                    Bias_OSMAC$mVc_Output)

Utility_AM_New_3<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                                   Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_New_3)<-colnames(Est_Bias_AM_New_3)<-c("Type","Subsample_Size",
                                                                 paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_New_3)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

## Model Free

```{r Load Data Model Free}
Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","ModelFree/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_MF<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_MF<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_MF<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_MF)<-colnames(Est_Bias_MF)<-c("Type","Subsample_Size",
                                                             paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_MF)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
```

```{r Combine all datasets}
Est_Parameter<-rbind(cbind(Model="Real",Est_Parameter_RM),
                     cbind(Model="Assumed Old 1",Est_Parameter_AM_Old_1),
                     cbind(Model="Assumed Old 2",Est_Parameter_AM_Old_2),
                     cbind(Model="Assumed Old 3",Est_Parameter_AM_Old_3),
                     cbind(Model="Assumed New 1",Est_Parameter_AM_New_1),
                     cbind(Model="Assumed New 2",Est_Parameter_AM_New_2),
                     cbind(Model="Assumed New 3",Est_Parameter_AM_New_3),
                     cbind(Model="Model Free",Est_Parameter_MF))

remove(Est_Parameter_RM,Est_Parameter_MF,
       Est_Parameter_AM_Old_1,Est_Parameter_AM_Old_2,Est_Parameter_AM_Old_3,
       Est_Parameter_AM_New_1,Est_Parameter_AM_New_2,Est_Parameter_AM_New_3)

Est_Bias<-rbind(cbind(Model="Real",Est_Bias_RM),
                cbind(Model="Assumed Old 1",Est_Bias_AM_Old_1),
                cbind(Model="Assumed Old 2",Est_Bias_AM_Old_2),
                cbind(Model="Assumed Old 3",Est_Bias_AM_Old_3),
                cbind(Model="Assumed New 1",Est_Bias_AM_New_1),
                cbind(Model="Assumed New 2",Est_Bias_AM_New_2),
                cbind(Model="Assumed New 3",Est_Bias_AM_New_3),
                cbind(Model="Model Free",Est_Bias_MF))

remove(Est_Bias_RM,Est_Bias_MF,
       Est_Bias_AM_Old_1,Est_Bias_AM_Old_2,Est_Bias_AM_Old_3,
       Est_Bias_AM_New_1,Est_Bias_AM_New_2,Est_Bias_AM_New_3)

Utility<-rbind(cbind(Model="Real",Utility_RM),
               cbind(Model="Assumed Old 1",Utility_AM_Old_1),
               cbind(Model="Assumed Old 2",Utility_AM_Old_2),
               cbind(Model="Assumed Old 3",Utility_AM_Old_3),
               cbind(Model="Assumed New 1",Utility_AM_New_1),
               cbind(Model="Assumed New 2",Utility_AM_New_2),
               cbind(Model="Assumed New 3",Utility_AM_New_3),
               cbind(Model="Model Free",Utility_MF))

remove(Utility_RM,Utility_MF,
       Utility_AM_Old_1,Utility_AM_Old_2,Utility_AM_Old_3,
       Utility_AM_New_1,Utility_AM_New_2,Utility_AM_New_3)
```

## Parameters

```{r Animated Plot for Parameter}
Est_Parameter %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, group = as.factor(Model), frame=Subsample_Size,fill=factor(Model))) + 
  geom_histogram(alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Estimated_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Parameter values", labels = c("Estimated"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Theta"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+
  theme_light()+ylab("Frequency")+xlab("Estimates")->para_1

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","para_1.gif"))
```

## Bias

```{r Animated Plots for Bias RM}
Est_Bias %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, group = as.factor(Model), frame=Subsample_Size,fill=factor(Model))) + 
  geom_histogram(alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Bias_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Bias values", labels = c("Real"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Bias"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+theme_light()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  ylab("Frequency")+xlab("Estimates")->Bias_1

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
```

## Utility values

```{r Animated Utility plots RM,fig.width=7,fig.height=7}
Utility %>%
  ggplot(.,aes(x=log(A_optimality),fill=Model))+
  geom_histogram()+facet_grid(~factor(Type))+
  theme_light()+ylab("Frequency")+xlab("log(A-optimality)")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_1

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_1.gif"))

Utility %>%
  ggplot(.,aes(x=log(D_optimality),fill=Model))+
  geom_histogram()+facet_grid(~factor(Type))+
  theme_light()+ylab("Frequency")+xlab("log(D-optimality) ")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_2

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_2.gif"))
```

# Comparison for Efficiency

```{r Comparison of Summary Data}
Final_MSE<-function(Real,Estimated_1,Estimated_2,Estimated_3,Estimated_4,Estimated_5,Model)
{
  For_Theta0<-sum((Real[1]-Estimated_1)^2,na.rm = TRUE)
  For_Theta1<-sum((Real[2]-Estimated_2)^2,na.rm = TRUE)
  For_Theta2<-sum((Real[3]-Estimated_3)^2,na.rm = TRUE)

  if(Model=="Model_1")
  {
    return((For_Theta0+For_Theta1+For_Theta2)/length(Estimated_1))
  }  
  if(Model=="Model_2" || Model=="Model_3")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3)/length(Estimated_1))
  }
  if(Model=="Model_4")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    For_Theta4<-sum((Real[5]-Estimated_5)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3+For_Theta4)/length(Estimated_1))
  }
}

# Summarise A- optimality
Utility %>%
  dplyr::select(Type,Model,Subsample_Size,A_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Variance=mean(A_optimality))%>%
  distinct(mean_Variance) %>% 
  forestmangr::round_df(8)->All_VAR

# Summarise D- optimality
Utility %>%
  dplyr::select(Type,Model,Subsample_Size,D_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Info=mean(D_optimality))%>%
  distinct(mean_Info) %>% 
  forestmangr::round_df(8)->All_Info

if(params$Model_Path=="Model_1")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
        group_by(Type,Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + Theta2*Theta2)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + Theta2*Theta2) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

if(params$Model_Path=="Model_2"||params$Model_Path=="Model_3")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
        group_by(Type,Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                             Theta2*Theta2 + Theta3*Theta3)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                        Theta2*Theta2 + Theta3*Theta3 ) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

if(params$Model_Path=="Model_4")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
        group_by(Type,Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Estimated_5=Theta4,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                             Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                        Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

# Summarise EMSE
inner_join(All_VAR,All_Bias_squared,by=c("Type","Model","Subsample_Size")) %>%
  mutate(EMSE=mean_Variance+mean_Bias) %>%
  select(Type,Model,Subsample_Size,EMSE)->All_EMSE
colnames(All_EMSE)<-c("Type","Model","Subsample_Size","EMSE")

# Full Data model Estimates
Full_Est_Parameter<-as.data.frame(t(Estimated_Vline$Values))
Full_Est_Bias<-as.data.frame(t(Cordeiro(XData = Simulated_Data[[2]]$Real_Model[,-1],
                                      With_bias = as.matrix(Full_Est_Parameter))))
colnames(Full_Est_Parameter)<-colnames(Full_Est_Bias)<-c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

Full_Bias<-sqrt(sum(Full_Est_Bias^2))
Temp_P<-invlogit(Simulated_Data[[2]]$Real_Model[,-1]%*% t(as.matrix(Full_Est_Parameter)))
Temp_W<-diag(as.vector(Temp_P*(1-Temp_P)))
Temp_Info<-t(Simulated_Data[[2]]$Real_Model[,-1])%*% Temp_W %*% Simulated_Data[[2]]$Real_Model[,-1]
Full_Variance<-tr(solve(Temp_Info))
Full_Information<-det(Temp_Info)

if(params$Model_Path=="Model_1")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Model=params$Model_Path)
}

if(params$Model_Path=="Model_2"||params$Model_Path=="Model_3")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Estimated_4 = Full_Est_Parameter$Theta3,
                Model=params$Model_Path)
}

if(params$Model_Path=="Model_4")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Estimated_4 = Full_Est_Parameter$Theta3,
                Estimated_5 = Full_Est_Parameter$Theta4,
                Model=params$Model_Path)
}

Full_EMSE<-Full_Variance+Full_Bias*Full_Bias

remove(Temp_P,Temp_W,Temp_Info)

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
     file = here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC.RData"))
```

## SMSE, EMSE, A-optimality, D-optimality, Bias Comparing Real Model and Assumed Models

```{r Final plots 1,fig.height=7,fig.width=20}
Plot_List<-list()

All_MSE %>%
  #ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("SMSE")+ggtitle("SMSE Comparison")->Plot_List[[1]]

All_VAR %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_List[[2]]

All_Info %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_List[[3]]

All_Bias %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_List[[4]]

All_EMSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_List[[5]]

ggarrange(plotlist = Plot_List,common.legend = TRUE,nrow=1)

```

## SMSE, EMSE, A-optimality, D-optimality, Bias Comparing Real Model and Assumed Models with Full Data Model

```{r Final plots 2,fig.height=7,fig.width=20}
Plot_List<-list()

All_MSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency")->Plot_List[[1]]

All_VAR %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_List[[2]]

All_Info %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_List[[3]]

All_Bias %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_List[[4]]

All_EMSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_List[[5]]

ggarrange(plotlist = Plot_List,common.legend = TRUE,nrow=1)

```

### 2022-01-17 Identical_r0/Rmarkdown/Classical/Summary/Best_Subsampling_Method.Rmd
First commit of all files

---
title: "Best Sub-sampling Method: `r params$Model_Path`"
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 12,fig.height = 12,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)
```

```{r load Data}
Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

# Random Sampling
load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_RS.RData"))

for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Bias<-All_Bias 
RS_EMSE<-All_EMSE
RS_Info<-All_Info
RS_MSE<-All_MSE
RS_VAR<-All_VAR

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))

All_Bias<-All_Bias[!(All_Bias$Model %in% remove_stuff),]
All_EMSE<-All_EMSE[!(All_EMSE$Model %in% remove_stuff),]
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
                OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"RS")])
```

# Best Sub-sampling Method : `r params$Model_Path`

# Compare SMSE, EMSE, Variance, Information and Bias for all methods.

```{r Compare All}
All_Bias%>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

All_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

All_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

All_VAR %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

All_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE)
```

# Compare  SMSE, EMSE, Variance, Information and Bias for mMSE.
## (Real Model and Assumed Model results with Full Data Real Model)

```{r Compare 1}
OSMAC_mMSE_Bias %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

OSMAC_mMSE_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

OSMAC_mMSE_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

OSMAC_mMSE_VAR %>% 
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

OSMAC_mMSE_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE)
```

# Compare  SMSE, EMSE, Variance, Information and Bias for mVc.
## (Real Model and Assumed Model results with Full Data Real Model)

```{r Compare 2}
OSMAC_mVc_Bias %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

OSMAC_mVc_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

OSMAC_mVc_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

OSMAC_mVc_VAR %>% 
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

OSMAC_mVc_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE)
```

### 2022-01-17 Non_Identical_r0/Rmarkdown/Classical/OSMAC_Method.Rmd
First commit of all files

---
title: "OSMAC_Method; Model: `r params$Model_Path`; "
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.height = 9,fig.width = 9,message = FALSE,warning=FALSE)
library(ggplot2)
library(here)
library(dplyr)
library(tidyr)
library(gganimate)
library(LaplacesDemon)
library(linguisticsdown)
library(gganimate)
library(viridis)
library(compiler)
library(data.table)

# Cordeiro Bias Estimation ----
Cordeiro<-function(XData,With_bias)
{
  p <- as.vector(exp(XData%*%as.vector(With_bias)))
  W <- diag(p)
  inverse_term <- solve(t(XData)%*%W%*%XData)

  Term1 <- inverse_term%*%t(XData)%*%W
  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))

  bias <- as.vector(Term1%*%Term2)
  return(bias)
}

Cordeiro<-cmpfun(Cordeiro)

FullDataPath<-here("Non_Identical_r0","Generate_Big_Data",params$Model_Path,"No_Correlated_Covariate.RData")
load(here(FullDataPath))
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = "poisson")
Real_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                       "Values"=Simulated_Data$Basic$Theta)
Estimated_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                            "Values"=Full_model$coefficients)
Bias_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),"Values"=0)
```

# OSMAC ;  Response Model : `r params$Model_Path`

# Real Model Data

```{r Load Data}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Real_Model/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_RM<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_RM<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_RM<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_RM)<-colnames(Est_Bias_RM)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_RM)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

# Assumed Model 1

```{r Load the Data AM 1}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model_1/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_AM_1<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_AM_1<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_AM_1<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_1)<-colnames(Est_Bias_AM_1)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_1)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

# Assumed Model 2

```{r Load the Data AM 2}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model_2/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_AM_2<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_AM_2<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_AM_2<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_2)<-colnames(Est_Bias_AM_2)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_2)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

# Assumed Model 3

```{r Load the Data AM 3}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model_3/")
load(here(Path,"OSMAC_output.RData"))

Est_Parameter_AM_3<-rbind.data.frame(Results_OSMAC$mMSE_Output,
                                   Results_OSMAC$mVc_Output)

Est_Bias_AM_3<-rbind.data.frame(Bias_OSMAC$mMSE_Output,
                              Bias_OSMAC$mVc_Output)

Utility_AM_3<-rbind.data.frame(Utility_OSMAC$mMSE_Output,
                             Utility_OSMAC$mVc_Output)

colnames(Est_Parameter_AM_3)<-colnames(Est_Bias_AM_3)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_AM_3)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC,Bias_OSMAC,Utility_OSMAC)
#remove(Sample_OSMAC)
```

```{r Combine datasets}
# Combine datasets
Est_Parameter<-rbind(data.frame("Model"="Real Model",Est_Parameter_RM),
                     data.frame("Model"="Assumed Model 1",Est_Parameter_AM_1),
                     data.frame("Model"="Assumed Model 2",Est_Parameter_AM_2),
                     data.frame("Model"="Assumed Model 3",Est_Parameter_AM_3))

Est_Bias<-rbind(data.frame("Model"="Real Model",Est_Bias_RM),
                data.frame("Model"="Assumed Model 1",Est_Bias_AM_1),
                data.frame("Model"="Assumed Model 2",Est_Bias_AM_2),
                data.frame("Model"="Assumed Model 3",Est_Bias_AM_3))

Est_Utility<-rbind(data.frame("Model"="Real Model",Utility_RM),
                   data.frame("Model"="Assumed Model 1",Utility_AM_1),
                   data.frame("Model"="Assumed Model 2",Utility_AM_2),
                   data.frame("Model"="Assumed Model 3",Utility_AM_3))

remove(Est_Bias_AM_1,Est_Bias_AM_2,Est_Bias_AM_3,Est_Bias_RM,
       Est_Parameter_AM_1,Est_Parameter_AM_2,Est_Parameter_AM_3,Est_Parameter_RM,
       Utility_AM_1,Utility_AM_2,Utility_AM_3,Utility_RM)
```

## Parameters

```{r Animated Plots}
Est_Parameter %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated,  frame=Subsample_Size,fill=as.factor(Model))) + 
  geom_histogram(alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Estimated_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Parameter values", labels = c("Estimated"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Theta"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+
  theme_light()+ylab("Frequency")+xlab("Estimates")->para_1

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","para_1.gif"))
```

## Bias

```{r Animated Plots for Bias}
Est_Bias %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, frame=Subsample_Size,fill=Model)) + 
  geom_histogram(alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Bias_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Bias values", labels = c("Real"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Bias"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+theme_light()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  ylab("Frequency")+xlab("Estimates")->Bias_1

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
```

## Utility values

```{r Animated Utility plots RM,fig.width=7,fig.height=7}
Est_Utility %>%
  ggplot(.,aes(x=log(A_optimality),fill=Model))+
  geom_histogram()+facet_wrap(~Type)+
  theme_light()+ylab("Frequency")+xlab("log(A-optimality)")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_1

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_1.gif"))

Est_Utility %>%
  ggplot(.,aes(x=log(D_optimality),fill=Model))+
  geom_histogram()+facet_wrap(~Type)+
  theme_light()+ylab("Frequency")+xlab("log(D-optimality) ")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_2

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_2.gif"))
```

## Response Data of the Subsamples

```{r Response Data RM,eval=FALSE}
Random_Sample_RM[Random_Sample_RM$Subsample_Size==1500,] %>%
  select(Type,Simulation,Y) %>%
  group_by(Simulation,Type) %>%
  dplyr::count(Y)-> Response

remove_missing(Response) %>% 
  ggplot(.,aes(x=Simulation,y=n,fill=as.factor(Y)))+
  geom_bar(stat = "identity")+facet_wrap(~Type)+
  scale_fill_viridis_d()+theme_light()+
  ylab("Count / Frequency")+xlab("Simulation")+
  labs(fill=c("Response Variable"))+
  ggtitle("Real Model : Dispersion of Y variable after multiple simulations")
```

# Comparison for Efficiency

```{r Comparison of Summary Data}
Final_MSE<-function(Real,Estimated_1,Estimated_2,Estimated_3,Estimated_4,Estimated_5,Model)
{
  For_Theta0<-sum((Real[1]-Estimated_1)^2,na.rm = TRUE)
  For_Theta1<-sum((Real[2]-Estimated_2)^2,na.rm = TRUE)
  For_Theta2<-sum((Real[3]-Estimated_3)^2,na.rm = TRUE)

  if(Model=="Model_1")
  {
    return((For_Theta0+For_Theta1+For_Theta2)/length(Estimated_1))
  }  
  if(Model=="Model_2" || Model=="Model_3")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3)/length(Estimated_1))
  }
  if(Model=="Model_4")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    For_Theta4<-sum((Real[5]-Estimated_5)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3+For_Theta4)/length(Estimated_1))
  }
}

# Summarise A- optimality
Est_Utility %>%
  dplyr::select(Type,Model,Subsample_Size,A_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Variance=mean(A_optimality))%>%
  distinct(mean_Variance) %>% 
  forestmangr::round_df(8)->All_VAR

# Summarise D- optimality
Est_Utility %>%
  dplyr::select(Type,Model,Subsample_Size,D_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Info=mean(D_optimality))%>%
  distinct(mean_Info) %>% 
  forestmangr::round_df(8)->All_Info

if(params$Model_Path=="Model_1")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
        group_by(Type,Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + Theta2*Theta2)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + Theta2*Theta2) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

if(params$Model_Path=="Model_2"||params$Model_Path=="Model_3")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
        group_by(Type,Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                             Theta2*Theta2 + Theta3*Theta3)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                        Theta2*Theta2 + Theta3*Theta3 ) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

if(params$Model_Path=="Model_4")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
        group_by(Type,Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Estimated_5=Theta4,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                             Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                        Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

# Summarise EMSE
inner_join(All_VAR,All_Bias_squared,by=c("Type","Model","Subsample_Size")) %>%
  mutate(EMSE=mean_Variance+mean_Bias) %>%
  select(Type,Model,Subsample_Size,EMSE)->All_EMSE
colnames(All_EMSE)<-c("Type","Model","Subsample_Size","EMSE")

# Full Data model Estimates
Full_Est_Parameter<-as.data.frame(t(Estimated_Vline$Values))
Full_Est_Bias<-as.data.frame(t(Cordeiro(XData = Simulated_Data[[2]]$Real_Model[,-1],
                                      With_bias = as.matrix(Full_Est_Parameter))))
colnames(Full_Est_Parameter)<-colnames(Full_Est_Bias)<-c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

Full_Bias<-sqrt(sum(Full_Est_Bias^2))
Temp_P<-exp(Simulated_Data[[2]]$Real_Model[,-1]%*% t(as.matrix(Full_Est_Parameter)))
Temp_W<-diag(as.vector(Temp_P))
Temp_Info<-t(Simulated_Data[[2]]$Real_Model[,-1])%*% Temp_W %*% Simulated_Data[[2]]$Real_Model[,-1]
Full_Variance<-tr(solve(Temp_Info))
Full_Information<-det(Temp_Info)

if(params$Model_Path=="Model_1")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Model=params$Model_Path)
}

if(params$Model_Path=="Model_2"||params$Model_Path=="Model_3")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Estimated_4 = Full_Est_Parameter$Theta3,
                Model=params$Model_Path)
}

if(params$Model_Path=="Model_4")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Estimated_4 = Full_Est_Parameter$Theta3,
                Estimated_5 = Full_Est_Parameter$Theta4,
                Model=params$Model_Path)
}

Full_EMSE<-Full_Variance+Full_Bias*Full_Bias

remove(Temp_P,Temp_W,Temp_Info)

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC.RData"))
```

## SMSE, EMSE, A-optimality, D-optimality, Bias Comparing Real Model and Assumed Models

```{r Final plots 1,fig.width=9,fig.height=20}
Plot_list<-list()
All_MSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("SMSE")+ggtitle("SMSE Comparison")->Plot_list[[1]]

All_VAR %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[2]]

All_Info %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[3]]

All_Bias %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[4]]

All_EMSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[5]]

ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)
```

## SMSE, EMSE, A-optimality, D-optimality, Bias Comparing Real Model and Assumed Models with Full Data Model

```{r Final plots 2,fig.width=9,fig.height=20}
Plot_list<-list()
All_MSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency")->Plot_list[[1]]

All_VAR %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[2]]

All_Info %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[3]]

All_Bias %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[4]]

All_EMSE %>%
  ungroup(Type,Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[5]]

ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)
```

### 2022-01-17 Non_Identical_r0/Rmarkdown/Classical/OSMAC_Model_Free_Method.Rmd
First commit of all files

---
title: "OSMAC_Model_Free_Method; Model: `r params$Model_Path`; "
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.height = 9,fig.width = 9,message = FALSE,warning=FALSE)
library(ggplot2)
library(here)
library(dplyr)
library(tidyr)
library(gganimate)
library(LaplacesDemon)
library(linguisticsdown)
library(gganimate)
library(viridis)
library(compiler)
library(data.table)
library(ggpubr)

# Cordeiro Bias Estimation ----
Cordeiro<-function(XData,With_bias)
{
  p <- as.vector(exp(XData%*%as.vector(With_bias)))
  W <- diag(p)
  inverse_term <- solve(t(XData)%*%W%*%XData)

  Term1 <- inverse_term%*%t(XData)%*%W
  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))

  bias <- as.vector(Term1%*%Term2)
  return(bias)
}

Cordeiro<-cmpfun(Cordeiro)

FullDataPath<-here("Non_Identical_r0","Generate_Big_Data",params$Model_Path,"No_Correlated_Covariate.RData")
load(here(FullDataPath))

Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = "poisson")
Real_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                       "Values"=Simulated_Data$Basic$Theta)
Estimated_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                            "Values"=Full_model$coefficients)
Bias_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),"Values"=0)
```

# OSMAC ;  Response Model : `r params$Model_Path`

## Real Model Data

```{r Load Data}
# Full Data RM
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = "poisson")
Estimated_Vline_RM<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                               "Values"=Full_model$coefficients)
Full_Est_Parameter_RM<-as.data.frame(t(Estimated_Vline_RM$Values))
Full_Est_Bias_RM<-as.data.frame(t(Cordeiro(XData = Simulated_Data[[2]]$Real_Model[,-1],
                                           With_bias = as.matrix(Full_Est_Parameter_RM))))
colnames(Full_Est_Parameter_RM)<-colnames(Full_Est_Bias_RM)<-c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
Full_Bias_RM<-sqrt(sum(Full_Est_Bias_RM^2))
Temp_P<-exp(Simulated_Data[[2]]$Real_Model[,-1]%*% t(as.matrix(Full_Est_Parameter_RM)))
Temp_W<-diag(as.vector(Temp_P))
Temp_Info<-t(Simulated_Data[[2]]$Real_Model[,-1])%*% Temp_W %*% Simulated_Data[[2]]$Real_Model[,-1]
Full_Variance_RM<-tr(solve(Temp_Info))
Full_Information_RM<-det(Temp_Info)

Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC_Model_Free/")
load(here(Path,"OSMAC_MF_output.RData"))

Est_Parameter_RM<-rbind.data.frame(Results_OSMAC_1$mMSE_Output,
                                   Results_OSMAC_1$mVc_Output)

Est_Bias_RM<-rbind.data.frame(Bias_OSMAC_1$mMSE_Output,
                              Bias_OSMAC_1$mVc_Output)

Utility_RM<-rbind.data.frame(Utility_OSMAC_1$mMSE_Output,
                             Utility_OSMAC_1$mVc_Output)

colnames(Est_Parameter_RM)<-colnames(Est_Bias_RM)<-c("Type","Subsample_Size",
                                                     paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))
colnames(Utility_RM)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC_1,Bias_OSMAC_1,Utility_OSMAC_1)
```

## Parameters

```{r Animated Plots RM}
Est_Parameter_RM %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, group = as.factor(Theta), frame=Subsample_Size)) + 
  geom_histogram(alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Estimated_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Parameter values", labels = c("Estimated"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Theta"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+
  theme_light()+ylab("Frequency")+xlab("Estimates")->para_1

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","para_1.gif"))
```

## Bias

```{r Animated Plots for Bias RM}
Est_Bias_RM %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, group = as.factor(Theta), frame=Subsample_Size)) + 
  geom_histogram(alpha=0.8)+
  facet_grid(Type~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Bias_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Bias values", labels = c("Real"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Bias"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+theme_light()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  ylab("Frequency")+xlab("Estimates")->Bias_1

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","Bias_1.gif"))
```

## Utility values

```{r Animated Utility plots RM,fig.width=7,fig.height=7}
Utility_RM %>%
  ggplot(.,aes(x=log(A_optimality)))+
  geom_histogram()+facet_wrap(~Type)+
  theme_light()+ylab("Frequency")+xlab("log(A-optimality)")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_1

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","U_1.gif"))

Utility_RM %>%
  ggplot(.,aes(x=log(D_optimality)))+
  geom_histogram()+facet_wrap(~Type)+
  theme_light()+ylab("Frequency")+xlab("log(D-optimality) ")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_2

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","U_2.gif"))
```

# Assumed Model 1

```{r Load the Data AM 1}
# Full Data AM 1
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Assumed_Model_1),family = "poisson")
Estimated_Vline_AM_1<-data.frame("Theta"=c(paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_1)-2))),
                                 "Values"=Full_model$coefficients)
Full_Est_Parameter_AM_1<-as.data.frame(t(Estimated_Vline_AM_1$Values))
Full_Est_Bias_AM_1<-as.data.frame(t(Cordeiro(XData = Simulated_Data[[2]]$Assumed_Model_1[,-1],
                                      With_bias = as.matrix(Full_Est_Parameter_AM_1))))
colnames(Full_Est_Parameter_AM_1)<-colnames(Full_Est_Bias_AM_1)<-c(paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_1)-2)))

Full_Bias_AM_1<-sqrt(sum(Full_Est_Bias_AM_1^2))
Temp_P<-exp(Simulated_Data[[2]]$Assumed_Model_1[,-1]%*% t(as.matrix(Full_Est_Parameter_AM_1)))
Temp_W<-diag(as.vector(Temp_P))
Temp_Info<-t(Simulated_Data[[2]]$Assumed_Model_1[,-1])%*% Temp_W %*% Simulated_Data[[2]]$Assumed_Model_1[,-1]
Full_Variance_AM_1<-tr(solve(Temp_Info))
Full_Information_AM_1<-det(Temp_Info)

Est_Parameter_AM_1<-rbind.data.frame(Results_OSMAC_2$mMSE_Output,
                                     Results_OSMAC_2$mVc_Output)

Est_Bias_AM_1<-rbind.data.frame(Bias_OSMAC_2$mMSE_Output,
                                Bias_OSMAC_2$mVc_Output)

Utility_AM_1<-rbind.data.frame(Utility_OSMAC_2$mMSE_Output,
                               Utility_OSMAC_2$mVc_Output)

colnames(Est_Parameter_AM_1)<-colnames(Est_Bias_AM_1)<-
  c("Type","Subsample_Size",paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_1)-2)))
colnames(Utility_AM_1)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC_2,Bias_OSMAC_2,Utility_OSMAC_2)

```

# Assumed Model 2

```{r Load the Data AM 2}
# Full Data AM 2
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Assumed_Model_2),family = "poisson")
Estimated_Vline_AM_2<-data.frame("Theta"=c(paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_2)-2))),
                                 "Values"=Full_model$coefficients)
Full_Est_Parameter_AM_2<-as.data.frame(t(Estimated_Vline_AM_2$Values))
Full_Est_Bias_AM_2<-as.data.frame(t(Cordeiro(XData = Simulated_Data[[2]]$Assumed_Model_2[,-1],
                                      With_bias = as.matrix(Full_Est_Parameter_AM_2))))
colnames(Full_Est_Parameter_AM_2)<-colnames(Full_Est_Bias_AM_2)<-c(paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_2)-2)))

Full_Bias_AM_2<-sqrt(sum(Full_Est_Bias_AM_2^2))
Temp_P<-exp(Simulated_Data[[2]]$Assumed_Model_2[,-1]%*% t(as.matrix(Full_Est_Parameter_AM_2)))
Temp_W<-diag(as.vector(Temp_P))
Temp_Info<-t(Simulated_Data[[2]]$Assumed_Model_2[,-1])%*% Temp_W %*% Simulated_Data[[2]]$Assumed_Model_2[,-1]
Full_Variance_AM_2<-tr(solve(Temp_Info))
Full_Information_AM_2<-det(Temp_Info)

Est_Parameter_AM_2<-rbind.data.frame(Results_OSMAC_3$mMSE_Output,
                                     Results_OSMAC_3$mVc_Output)

Est_Bias_AM_2<-rbind.data.frame(Bias_OSMAC_3$mMSE_Output,
                                Bias_OSMAC_3$mVc_Output)

Utility_AM_2<-rbind.data.frame(Utility_OSMAC_3$mMSE_Output,
                               Utility_OSMAC_3$mVc_Output)

colnames(Est_Parameter_AM_2)<-colnames(Est_Bias_AM_2)<-
  c("Type","Subsample_Size",paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_2)-2)))
colnames(Utility_AM_2)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC_3,Bias_OSMAC_3,Utility_OSMAC_3)

```

# Assumed Model 3

```{r Load the Data AM 3}
# Full Data AM 3
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Assumed_Model_3),family = "poisson")
Estimated_Vline_AM_3<-data.frame("Theta"=c(paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_3)-2))),
                                 "Values"=Full_model$coefficients)
Full_Est_Parameter_AM_3<-as.data.frame(t(Estimated_Vline_AM_3$Values))
Full_Est_Bias_AM_3<-as.data.frame(t(Cordeiro(XData = Simulated_Data[[2]]$Assumed_Model_3[,-1],
                                      With_bias = as.matrix(Full_Est_Parameter_AM_3))))
colnames(Full_Est_Parameter_AM_3)<-colnames(Full_Est_Bias_AM_3)<-c(paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_3)-2)))

Full_Bias_AM_3<-sqrt(sum(Full_Est_Bias_AM_3^2))
Temp_P<-exp(Simulated_Data[[2]]$Assumed_Model_3[,-1]%*% t(as.matrix(Full_Est_Parameter_AM_3)))
Temp_W<-diag(as.vector(Temp_P))
Temp_Info<-t(Simulated_Data[[2]]$Assumed_Model_3[,-1])%*% Temp_W %*% Simulated_Data[[2]]$Assumed_Model_3[,-1]
Full_Variance_AM_3<-tr(solve(Temp_Info))
Full_Information_AM_3<-det(Temp_Info)

Est_Parameter_AM_3<-rbind.data.frame(Results_OSMAC_4$mMSE_Output,
                                     Results_OSMAC_4$mVc_Output)

Est_Bias_AM_3<-rbind.data.frame(Bias_OSMAC_4$mMSE_Output,
                                Bias_OSMAC_4$mVc_Output)

Utility_AM_3<-rbind.data.frame(Utility_OSMAC_4$mMSE_Output,
                               Utility_OSMAC_4$mVc_Output)

colnames(Est_Parameter_AM_3)<-colnames(Est_Bias_AM_3)<-
  c("Type","Subsample_Size",paste0("Theta",0:(ncol(Simulated_Data[[2]]$Assumed_Model_3)-2)))
colnames(Utility_AM_3)<-c("Type","Subsample_Size","A_optimality","D_optimality")

remove(Results_OSMAC_4,Bias_OSMAC_4,Utility_OSMAC_4)

```

# Comparison for Efficiency

```{r Comparison of Summary Data}
Final_MSE<-function(Real,Estimated_1,Estimated_2,Estimated_3,Estimated_4,Estimated_5,Model)
{
  For_Theta0<-sum((Real[1]-Estimated_1)^2,na.rm = TRUE)
  For_Theta1<-sum((Real[2]-Estimated_2)^2,na.rm = TRUE)
  For_Theta2<-sum((Real[3]-Estimated_3)^2,na.rm = TRUE)

  if(Model=="Model_1")
  {
    return((For_Theta0+For_Theta1+For_Theta2)/length(Estimated_1))
  }  
  if(Model=="Model_2" || Model=="Model_3")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3)/length(Estimated_1))
  }
  if(Model=="Model_4")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    For_Theta4<-sum((Real[5]-Estimated_5)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3+For_Theta4)/length(Estimated_1))
  }
}

# Combine datasets
Est_Utility<-rbind(data.frame("Model"="Real Model",Utility_RM),
                   data.frame("Model"="Assumed Model 1",Utility_AM_1),
                   data.frame("Model"="Assumed Model 2",Utility_AM_2),
                   data.frame("Model"="Assumed Model 3",Utility_AM_3))

remove(Utility_AM_3,Utility_AM_2,Utility_AM_1,Utility_RM,
       Bias_Vline,Temp_Info,Temp_W,Temp_P,
       Estimated_Vline,Full_model)

# Summarise A- optimality
Est_Utility %>%
  dplyr::select(Type,Model,Subsample_Size,A_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Variance=mean(A_optimality))%>%
  distinct(mean_Variance) %>% 
  forestmangr::round_df(8)->All_VAR

# Summarise D- optimality
Est_Utility %>%
  dplyr::select(Type,Model,Subsample_Size,D_optimality) %>%
  group_by(Type,Model,Subsample_Size) %>%
  mutate(mean_Info=mean(D_optimality))%>%
  distinct(mean_Info) %>% 
  forestmangr::round_df(8)->All_Info

# Model 1
if(params$Model_Path=="Model_1")
{
  # Summarize SMSE
  Est_Parameter_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Model = params$Model_Path ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_RM

  Est_Parameter_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_1$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Model = "Model_2" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_1

  Est_Parameter_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_2$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Model = "Model_3" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_2

  Est_Parameter_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_3$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Estimated_5=Theta4,
                            Model = "Model_4" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_3

  All_MSE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                 data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
                 data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
                 data.frame("Model"="Assumed Model 3",All_MSE_AM_3))

  remove(All_MSE_RM,All_MSE_AM_1,All_MSE_AM_2,All_MSE_AM_3)

  # Summarise Bias
  Est_Bias_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_RM

  Est_Bias_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2+ Theta3*Theta3)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_1

   Est_Bias_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2+ Theta3*Theta3)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_2

  Est_Bias_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2+ Theta3*Theta3+ Theta4*Theta4)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_3

  All_Bias<-rbind(data.frame("Model"="Real Model",All_Bias_RM),
                  data.frame("Model"="Assumed Model 1",All_Bias_AM_1),
                  data.frame("Model"="Assumed Model 2",All_Bias_AM_2),
                  data.frame("Model"="Assumed Model 3",All_Bias_AM_3))

  remove(All_Bias_AM_1,All_Bias_AM_2,All_Bias_AM_3,All_Bias_RM)

  # Summarise Bias = sqrt(Bias^2)
  Est_Bias_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 +
                            Theta2*Theta2) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_RM

  Est_Bias_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2 + Theta3*Theta3) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_1

  Est_Bias_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2 + Theta3*Theta3) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_2

  Est_Bias_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_3

  All_Bias_squared<-rbind(data.frame("Model"="Real Model",All_Bias_squared_RM),
                          data.frame("Model"="Assumed Model 1",All_Bias_squared_AM_1),
                          data.frame("Model"="Assumed Model 2",All_Bias_squared_AM_2),
                          data.frame("Model"="Assumed Model 3",All_Bias_squared_AM_3))

  remove(All_Bias_squared_RM,All_Bias_squared_AM_1,All_Bias_squared_AM_2,All_Bias_squared_AM_3)
}

# Model 2 and Model 3
if(params$Model_Path=="Model_2" || params$Model_Path=="Model_3")
{
  # Summarize SMSE
  Est_Parameter_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Model = params$Model_Path ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_RM

  Est_Parameter_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_1$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Model = "Model_1" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_1

  Est_Parameter_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_2$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Model = "Model_3" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_2

  Est_Parameter_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_3$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Estimated_5=Theta4,
                            Model = "Model_4" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_3

  All_MSE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                 data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
                 data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
                 data.frame("Model"="Assumed Model 3",All_MSE_AM_3))

  remove(All_MSE_RM,All_MSE_AM_1,All_MSE_AM_2,All_MSE_AM_3)

  # Summarise Bias
  Est_Bias_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2 + Theta3*Theta3)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_RM

  Est_Bias_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_1

   Est_Bias_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2+ Theta3*Theta3)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_2

  Est_Bias_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2+ Theta3*Theta3+ Theta4*Theta4)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_3

  All_Bias<-rbind(data.frame("Model"="Real Model",All_Bias_RM),
                  data.frame("Model"="Assumed Model 1",All_Bias_AM_1),
                  data.frame("Model"="Assumed Model 2",All_Bias_AM_2),
                  data.frame("Model"="Assumed Model 3",All_Bias_AM_3))

  remove(All_Bias_AM_1,All_Bias_AM_2,All_Bias_AM_3,All_Bias_RM)

  # Summarise Bias = sqrt(Bias^2)
  Est_Bias_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                          Theta2*Theta2 + Theta3*Theta3 ) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_RM

  Est_Bias_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_1

  Est_Bias_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2 + Theta3*Theta3) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_2

  Est_Bias_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_3

  All_Bias_squared<-rbind(data.frame("Model"="Real Model",All_Bias_squared_RM),
                          data.frame("Model"="Assumed Model 1",All_Bias_squared_AM_1),
                          data.frame("Model"="Assumed Model 2",All_Bias_squared_AM_2),
                          data.frame("Model"="Assumed Model 3",All_Bias_squared_AM_3))

  remove(All_Bias_squared_RM,All_Bias_squared_AM_1,All_Bias_squared_AM_2,All_Bias_squared_AM_3)
}

# Model 4
if(params$Model_Path=="Model_4")
{
  # Summarize SMSE
  Est_Parameter_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Estimated_5=Theta4,
                            Model = params$Model_Path ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_RM

  Est_Parameter_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_1$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Model = "Model_1" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_1

  Est_Parameter_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_2$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Model = "Model_3" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_2

  Est_Parameter_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_3$Values,
                            Estimated_1=Theta0, 
                            Estimated_2=Theta1,
                            Estimated_3=Theta2,
                            Estimated_4=Theta3,
                            Model = "Model_2" ))%>%
    distinct(MSE) %>% 
    forestmangr::round_df(8)->All_MSE_AM_3

  All_MSE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                 data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
                 data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
                 data.frame("Model"="Assumed Model 3",All_MSE_AM_3))

  remove(All_MSE_RM,All_MSE_AM_1,All_MSE_AM_2,All_MSE_AM_3)

  # Summarise Bias
  Est_Bias_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_RM

  Est_Bias_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_1

   Est_Bias_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2+ Theta3*Theta3)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_2

  Est_Bias_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                                 Theta2*Theta2+ Theta3*Theta3)) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(8)->All_Bias_AM_3

  All_Bias<-rbind(data.frame("Model"="Real Model",All_Bias_RM),
                  data.frame("Model"="Assumed Model 1",All_Bias_AM_1),
                  data.frame("Model"="Assumed Model 2",All_Bias_AM_2),
                  data.frame("Model"="Assumed Model 3",All_Bias_AM_3))

  remove(All_Bias_AM_1,All_Bias_AM_2,All_Bias_AM_3,All_Bias_RM)

  # Summarise Bias = sqrt(Bias^2)
  Est_Bias_RM %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                          Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_RM

  Est_Bias_AM_1 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_1

  Est_Bias_AM_2 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2 + Theta3*Theta3) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_2

  Est_Bias_AM_3 %>%
    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
    group_by(Type,Subsample_Size) %>%
    mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                            Theta2*Theta2 + Theta3*Theta3 ) )%>%
    distinct(mean_Bias) %>% 
    forestmangr::round_df(4)->All_Bias_squared_AM_3

  All_Bias_squared<-rbind(data.frame("Model"="Real Model",All_Bias_squared_RM),
                          data.frame("Model"="Assumed Model 1",All_Bias_squared_AM_1),
                          data.frame("Model"="Assumed Model 2",All_Bias_squared_AM_2),
                          data.frame("Model"="Assumed Model 3",All_Bias_squared_AM_3))

  remove(All_Bias_squared_RM,All_Bias_squared_AM_1,All_Bias_squared_AM_2,All_Bias_squared_AM_3)
}

# Summarise EMSE
inner_join(All_VAR,All_Bias_squared,by=c('Type',"Model","Subsample_Size")) %>%
  mutate(EMSE=mean_Variance+mean_Bias) %>%
  select(Type,Model,Subsample_Size,EMSE)->All_EMSE
colnames(All_EMSE)<-c('Type',"Model","Subsample_Size","EMSE")

if(params$Model_Path=="Model_1")
{
  Full_SMSE_RM<-Final_MSE(Real=Real_Vline$Values,
                          Estimated_1 = Full_Est_Parameter_RM$Theta0,
                          Estimated_2 = Full_Est_Parameter_RM$Theta1,
                          Estimated_3 = Full_Est_Parameter_RM$Theta2,
                          Model=params$Model_Path)
}

if(params$Model_Path=="Model_2" || params$Model_Path=="Model_3")
{
  Full_SMSE_RM<-Final_MSE(Real=Real_Vline$Values,
                          Estimated_1 = Full_Est_Parameter_RM$Theta0,
                          Estimated_2 = Full_Est_Parameter_RM$Theta1,
                          Estimated_3 = Full_Est_Parameter_RM$Theta2,
                          Estimated_4 = Full_Est_Parameter_RM$Theta3,
                          Model=params$Model_Path)
}

if(params$Model_Path=="Model_4")
{
  Full_SMSE_RM<-Final_MSE(Real=Real_Vline$Values,
                          Estimated_1 = Full_Est_Parameter_RM$Theta0,
                          Estimated_2 = Full_Est_Parameter_RM$Theta1,
                          Estimated_3 = Full_Est_Parameter_RM$Theta2,
                          Estimated_4 = Full_Est_Parameter_RM$Theta3,
                          Estimated_5 = Full_Est_Parameter_RM$Theta4,
                          Model=params$Model_Path)
}

Full_EMSE_RM<-Full_Variance_RM+Full_Bias_RM*Full_Bias_RM
Full_EMSE_AM_1<-Full_Variance_AM_1+Full_Bias_AM_1*Full_Bias_AM_1
Full_EMSE_AM_2<-Full_Variance_AM_2+Full_Bias_AM_2*Full_Bias_AM_2
Full_EMSE_AM_3<-Full_Variance_AM_3+Full_Bias_AM_3*Full_Bias_AM_3

remove(Temp_P,Temp_W,Temp_Info)

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_OSMAC_MF.RData"))

```

## SMSE, EMSE, A-optimality, D-optimality, Bias Comparing Real Model with with Full Data Model

```{r Final plots 1,fig.width=20,fig.height=8}
Plot_list<-list()

All_MSE[All_MSE$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency")->Plot_list[[1]]

All_VAR[All_VAR$Model=="Real Model",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[2]]

All_Info[All_Info$Model=="Real Model",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[3]]

All_Bias[All_Bias$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[4]]

All_EMSE[All_EMSE$Model=="Real Model",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE_RM) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[5]]

ggarrange(plotlist = Plot_list,nrow = 1,ncol = 5,common.legend = TRUE)

```

## EMSE, A-optimality, D-optimality, Bias Comparing Assumed Model with Full Data Assumed Model 1

```{r Final plots AM 1,fig.width=16,fig.height=8}
Plot_list<-list()

All_VAR[All_VAR$Model=="Assumed Model 1",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance_AM_1) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[1]]

All_Info[All_Info$Model=="Assumed Model 1",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information_AM_1) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[2]]

All_Bias[All_Bias$Model=="Assumed Model 1",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias_AM_1) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[3]]

All_EMSE[All_EMSE$Model=="Assumed Model 1",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE_AM_1) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[4]]

ggarrange(plotlist = Plot_list,nrow = 1,ncol = 4,common.legend = TRUE)
```

## EMSE, A-optimality, D-optimality, Bias Comparing Assumed Model with Full Data Assumed Model 2

```{r Final plots AM 2,fig.width=16,fig.height=8}
Plot_list<-list()

All_VAR[All_VAR$Model=="Assumed Model 2",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance_AM_2) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[1]]

All_Info[All_Info$Model=="Assumed Model 2",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information_AM_2) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[2]]

All_Bias[All_Bias$Model=="Assumed Model 2",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias_AM_2) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[3]]

All_EMSE[All_EMSE$Model=="Assumed Model 2",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE_AM_2) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[4]]

ggarrange(plotlist = Plot_list,nrow = 1,ncol = 4,common.legend = TRUE)
```

## EMSE, A-optimality, D-optimality, Bias Comparing Assumed Model with Full Data Assumed Model 3

```{r Final plots AM 3,fig.width=16,fig.height=8}
Plot_list<-list()

All_VAR[All_VAR$Model=="Assumed Model 3",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance_AM_3) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[1]]

All_Info[All_Info$Model=="Assumed Model 3",] %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information_AM_3) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[2]]

All_Bias[All_Bias$Model=="Assumed Model 3",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias_AM_3) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[3]]

All_EMSE[All_EMSE$Model=="Assumed Model 3",] %>%
  #ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE_AM_3) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[4]]

ggarrange(plotlist = Plot_list,nrow = 1,ncol = 4,common.legend = TRUE)
```

### 2022-01-17 Non_Identical_r0/Rmarkdown/Classical/Random_Sampling.Rmd
First commit of all files

---
title: "Random_Sampling; Model: `r params$Model_Path`;"
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.height = 9,fig.width = 9,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(linguisticsdown)
library(gganimate)
library(viridis)
library(compiler)
library(ggpubr)

# Cordeiro Bias Estimation ----
Cordeiro<-function(XData,With_bias)
{
  p <- as.vector(exp(XData%*%as.vector(With_bias)))
  W <- diag(p)
  inverse_term <- solve(t(XData)%*%W%*%XData)

  Term1 <- inverse_term%*%t(XData)%*%W
  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))

  bias <- as.vector(Term1%*%Term2)
  return(bias)
}

Cordeiro<-cmpfun(Cordeiro)

FullDataPath<-here("Non_Identical_r0","Generate_Big_Data",params$Model_Path,"No_Correlated_Covariate.RData")
load(here(FullDataPath))
Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = "poisson")
Real_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                       "Values"=Simulated_Data$Basic$Theta)
Estimated_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),
                            "Values"=Full_model$coefficients)
Bias_Vline<-data.frame("Theta"=c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1]))),"Values"=0)
```

# Random Sampling; Model : `r params$Model_Path`

# Real Model Data

```{r Load Data RM}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Real_Model/")
load(here(Path,"Random_Sample_output.RData"))

Est_Parameter_RM<-as.data.frame(Est_Param_RandomSample)
colnames(Est_Parameter_RM)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

Utility_RM<-as.data.frame(Utility_RandomSample) 
colnames(Utility_RM)<-c("Subsample_Size",paste0(c("A","D"),"_optimality"))

Est_Bias_RM<-as.data.frame(Bias_RandomSample) 
colnames(Est_Bias_RM)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

remove(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample#,SelectedData_RandomSample
       )
```

# Assumed Model 1 Data

```{r Load Data AM 1}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Assumed_Model_1/")
load(here(Path,"Random_Sample_output.RData"))

Est_Parameter_AM_1<-as.data.frame(Est_Param_RandomSample)
colnames(Est_Parameter_AM_1)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

Utility_AM_1<-as.data.frame(Utility_RandomSample) 
colnames(Utility_AM_1)<-c("Subsample_Size",paste0(c("A","D"),"_optimality"))

Est_Bias_AM_1<-as.data.frame(Bias_RandomSample) 
colnames(Est_Bias_AM_1)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

remove(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample#,SelectedData_RandomSample
       )
```

# Assumed Model 2 Data

```{r Load Data AM 2}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Assumed_Model_2/")
load(here(Path,"Random_Sample_output.RData"))

Est_Parameter_AM_2<-as.data.frame(Est_Param_RandomSample)
colnames(Est_Parameter_AM_2)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

Utility_AM_2<-as.data.frame(Utility_RandomSample) 
colnames(Utility_AM_2)<-c("Subsample_Size",paste0(c("A","D"),"_optimality"))

Est_Bias_AM_2<-as.data.frame(Bias_RandomSample) 
colnames(Est_Bias_AM_2)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

remove(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample#,SelectedData_RandomSample
       )
```

# Assumed Model 3 Data

```{r Load Data AM 3}
Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Assumed_Model_3/")
load(here(Path,"Random_Sample_output.RData"))

Est_Parameter_AM_3<-as.data.frame(Est_Param_RandomSample)
colnames(Est_Parameter_AM_3)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

Utility_AM_3<-as.data.frame(Utility_RandomSample) 
colnames(Utility_AM_3)<-c("Subsample_Size",paste0(c("A","D"),"_optimality"))

Est_Bias_AM_3<-as.data.frame(Bias_RandomSample) 
colnames(Est_Bias_AM_3)<-c("Subsample_Size",paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

remove(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample#,SelectedData_RandomSample
       )
```

```{r Combine Datasets}
# Combine datasets
Est_Parameter<-rbind(data.frame("Model"="Real Model",Est_Parameter_RM),
                     data.frame("Model"="Assumed Model 1",Est_Parameter_AM_1),
                     data.frame("Model"="Assumed Model 2",Est_Parameter_AM_2),
                     data.frame("Model"="Assumed Model 3",Est_Parameter_AM_3))

Est_Bias<-rbind(data.frame("Model"="Real Model",Est_Bias_RM),
                data.frame("Model"="Assumed Model 1",Est_Bias_AM_1),
                data.frame("Model"="Assumed Model 2",Est_Bias_AM_2),
                data.frame("Model"="Assumed Model 3",Est_Bias_AM_3))

Est_Utility<-rbind(data.frame("Model"="Real Model",Utility_RM),
                   data.frame("Model"="Assumed Model 1",Utility_AM_1),
                   data.frame("Model"="Assumed Model 2",Utility_AM_2),
                   data.frame("Model"="Assumed Model 3",Utility_AM_3))

remove(Est_Bias_AM_1,Est_Bias_AM_2,Est_Bias_AM_3,Est_Bias_RM,
       Est_Parameter_AM_1,Est_Parameter_AM_2,Est_Parameter_AM_3,Est_Parameter_RM,
       Utility_AM_1,Utility_AM_2,Utility_AM_3,Utility_RM)
```

## Parameters

```{r Animated Plots}
Est_Parameter %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, fill=Model, frame=Subsample_Size)) + 
  geom_histogram(alpha=0.8)+
  facet_grid(~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Estimated_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Parameter values", labels = c("Estimated"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Theta"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+
  theme_light()+ylab("Frequency")+xlab("Estimates")->para_1

anim_save(filename="para_1.gif",animation = para_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","para_1.gif"))
```

## Bias

```{r Animated Plots for Bias}
Est_Bias %>%
  pivot_longer(starts_with("Theta"), names_to = "Theta", values_to = "Estimated") %>%
ggplot(., aes(x = Estimated, fill=Model, frame=Subsample_Size)) + 
  geom_histogram(alpha=0.8)+
  facet_grid(~Theta,scales = "free_x",shrink = TRUE)+
  geom_vline(data= Bias_Vline,aes(xintercept = Values,color="red"),linetype='dashed',size=1)+
  scale_color_discrete(name = "Bias values", labels = c("Real"))+
  labs(title=paste0("Real Model :",params$Model_Path," Data : Estimated Bias"),
      subtitle = "Sub-sample Size: {current_frame}")+
  transition_manual(Subsample_Size)+theme_light()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  ylab("Frequency")+xlab("Estimates")->Bias_1

anim_save(filename="Bias_1.gif",animation = Bias_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","Bias_1.gif"))
```

## Utility values

```{r Animated Utility plots RM,fig.width=7,fig.height=7}
Est_Utility %>%
  ggplot(.,aes(x=log(A_optimality),fill=Model))+
  geom_histogram()+
  theme_light()+ylab("Frequency")+xlab("log(A-optimality)")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_1

anim_save(filename="U_1.gif",animation = U_1,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","U_1.gif"))

Est_Utility %>%
  ggplot(.,aes(x=log(D_optimality),fill=Model))+
  geom_histogram()+
  theme_light()+ylab("Frequency")+xlab("log(D-optimality) ")+
  transition_states(Subsample_Size)+
  ggtitle("Real Model : Subsample : {closest_state}")->U_2

anim_save(filename="U_2.gif",animation = U_2,
          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))

include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","U_2.gif"))
```

## Response Data of the Subsamples

```{r Response Data RM,eval=FALSE}
Random_Sample %>%
  as.data.frame()%>%
  group_by(Simulation) %>%
  dplyr::count(Y)-> Response

remove_missing(Response) %>% 
  ggplot(.,aes(x=Simulation,y=n,fill=as.factor(Y)))+
  geom_bar(stat = "identity")+
  scale_fill_viridis_d()+theme_light()+
  ylab("Count / Frequency")+xlab("Simulation")+
  labs(fill=c("Response Variable"))+
  ggtitle("Real Model : Dispersion of Y variable after multiple simulations")
```

# Comparison for Efficiency

```{r Comparison of Summary Data}
Final_MSE<-function(Real,Estimated_1,Estimated_2,Estimated_3,Estimated_4,Estimated_5,Model)
{
  For_Theta0<-sum((Real[1]-Estimated_1)^2,na.rm = TRUE)
  For_Theta1<-sum((Real[2]-Estimated_2)^2,na.rm = TRUE)
  For_Theta2<-sum((Real[3]-Estimated_3)^2,na.rm = TRUE)

  if(Model=="Model_1")
  {
    return((For_Theta0+For_Theta1+For_Theta2)/length(Estimated_1))
  }  
  if(Model=="Model_2" || Model=="Model_3")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3)/length(Estimated_1))
  }
  if(Model=="Model_4")
  {
    For_Theta3<-sum((Real[4]-Estimated_4)^2,na.rm = TRUE)
    For_Theta4<-sum((Real[5]-Estimated_5)^2,na.rm = TRUE)
    return((For_Theta0+For_Theta1+For_Theta2+For_Theta3+For_Theta4)/length(Estimated_1))
  }
}

# Summarise A- optimality
Est_Utility %>%
  dplyr::select(Model,Subsample_Size,A_optimality) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Variance=mean(A_optimality))%>%
  distinct(mean_Variance) %>% 
  forestmangr::round_df(8)->All_VAR

# Summarise D- optimality
Est_Utility %>%
  dplyr::select(Model,Subsample_Size,D_optimality) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Info=mean(D_optimality))%>%
  distinct(mean_Info) %>% 
  forestmangr::round_df(8)->All_Info

if(params$Model_Path=="Model_1")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
        group_by(Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + Theta2*Theta2)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + Theta2*Theta2) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

if(params$Model_Path=="Model_2"||params$Model_Path=="Model_3")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
        group_by(Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                             Theta2*Theta2 + Theta3*Theta3)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                        Theta2*Theta2 + Theta3*Theta3 ) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

if(params$Model_Path=="Model_4")
{
  # Summarize SMSE
  Est_Parameter %>%
        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
        group_by(Model,Subsample_Size) %>%
        mutate( MSE=Final_MSE(Real = Real_Vline$Values,
                              Estimated_1=Theta0, 
                              Estimated_2=Theta1,
                              Estimated_3=Theta2,
                              Estimated_4=Theta3,
                              Estimated_5=Theta4,
                              Model = params$Model_Path ))%>%
        distinct(MSE) %>% 
        forestmangr::round_df(8)->All_MSE

# Summarise Bias
Est_Bias %>%
  dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(sqrt(Theta0*Theta0 + Theta1*Theta1 + 
                             Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4)) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(8)->All_Bias

# Summarise Bias = sqrt(Bias^2)
Est_Bias %>%
  dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
  group_by(Model,Subsample_Size) %>%
  mutate(mean_Bias=mean(Theta0*Theta0 + Theta1*Theta1 + 
                        Theta2*Theta2 + Theta3*Theta3 + Theta4*Theta4) )%>%
  distinct(mean_Bias) %>% 
  forestmangr::round_df(4)->All_Bias_squared
}

# Summarise EMSE
inner_join(All_VAR,All_Bias_squared,by=c("Model","Subsample_Size")) %>%
  mutate(EMSE=mean_Variance+mean_Bias) %>%
  select(Model,Subsample_Size,EMSE)->All_EMSE
colnames(All_EMSE)<-c("Model","Subsample_Size","EMSE")

# Full Data model Estimates
Full_Est_Parameter<-as.data.frame(t(Estimated_Vline$Values))
Full_Est_Bias<-as.data.frame(t(Cordeiro(XData = Simulated_Data[[2]]$Real_Model[,-1],
                                      With_bias = as.matrix(Full_Est_Parameter))))
colnames(Full_Est_Parameter)<-colnames(Full_Est_Bias)<-c(paste0("Theta",0:length(Simulated_Data$Basic$Theta[-1])))

Full_Bias<-sqrt(sum(Full_Est_Bias^2))
Temp_P<-exp(Simulated_Data[[2]]$Real_Model[,-1]%*% t(as.matrix(Full_Est_Parameter)))
Temp_W<-diag(as.vector(Temp_P))
Temp_Info<-t(Simulated_Data[[2]]$Real_Model[,-1])%*% Temp_W %*% Simulated_Data[[2]]$Real_Model[,-1]
Full_Variance<-tr(solve(Temp_Info))
Full_Information<-det(Temp_Info)

if(params$Model_Path=="Model_1")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Model=params$Model_Path)
}

if(params$Model_Path=="Model_2"||params$Model_Path=="Model_3")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Estimated_4 = Full_Est_Parameter$Theta3,
                Model=params$Model_Path)
}

if(params$Model_Path=="Model_4")
{
  Full_SMSE<-Final_MSE(Real=Real_Vline$Values,
                Estimated_1 = Full_Est_Parameter$Theta0,
                Estimated_2 = Full_Est_Parameter$Theta1,
                Estimated_3 = Full_Est_Parameter$Theta2,
                Estimated_4 = Full_Est_Parameter$Theta3,
                Estimated_5 = Full_Est_Parameter$Theta4,
                Model=params$Model_Path)
}

Full_EMSE<-Full_Variance+Full_Bias*Full_Bias

remove(Temp_P,Temp_W,Temp_Info)

# Store the Results
save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
                 "No_Correlated_Covariate_RS.RData"))
```

## SMSE, EMSE, A-optimality, D-optimality, Bias Comparing Real Model and Assumed Models

```{r Final plots 1,fig.width=6,fig.height=20}
Plot_list<-list()

All_MSE %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("SMSE")+ggtitle("SMSE Comparison")->Plot_list[[1]]

All_VAR %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[2]]

All_Info %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[3]]

All_Bias %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[4]]

All_EMSE %>%
  ungroup(Model,Subsample_Size) %>%
ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[5]]

ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)

```

## SMSE, EMSE, A-optimality, D-optimality, Bias Comparing Real Model and Assumed Models with Full Data Model

```{r Final plots 2,fig.width=6,fig.height=20}
Plot_list<-list()
All_MSE %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=MSE/Full_SMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency")->Plot_list[[1]]

All_VAR %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Variance/Full_Variance) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[2]]

All_Info %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Info/Full_Information) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[3]]

All_Bias %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=mean_Bias/Full_Bias) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[4]]

All_EMSE %>%
  ungroup(Model,Subsample_Size) %>%
  mutate(Efficiency=EMSE/Full_EMSE) %>%
ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
  geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[5]]

ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)
```

### 2022-01-17 Non_Identical_r0/Rmarkdown/Classical/Summary/Best_Subsampling_Method.Rmd
First commit of all files

---
title: "Best Sub-sampling Method: `r params$Model_Path`"
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 12,fig.height = 12,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)
```

```{r load Data}
Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

# Random Sampling
load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_RS.RData"))

for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Bias<-All_Bias 
RS_EMSE<-All_EMSE
RS_Info<-All_Info
RS_MSE<-All_MSE
RS_VAR<-All_VAR

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC Model Free
load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_MF.RData"))

All_Bias<-All_Bias[All_Bias$Model==Old_Labels[1],]
All_EMSE<-All_EMSE[All_EMSE$Model==Old_Labels[1],]
All_Info<-All_Info[All_Info$Model==Old_Labels[1],]
All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]

## mMSE
All_Bias$Model[All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_EMSE$Model[All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_Info$Model[All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")

OSMAC_MF_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_MF_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_MF_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

## mVc
All_Bias$Model[All_Bias$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_EMSE$Model[All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_Info$Model[All_Info$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")

OSMAC_MF_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_MF_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_MF_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")],
                OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")],
                OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
                OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
                OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")],
                OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")],
                OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
                OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")],
                OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])

# Special mMSE elements
SP_All_mMSE_Bias<-rbind(OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                        OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")])
SP_All_mMSE_EMSE<-rbind(OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                        OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")])
SP_All_mMSE_MSE<-rbind(OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                       OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")])
SP_All_mMSE_Info<-rbind(OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                        OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")])
SP_All_mMSE_VAR<-rbind(OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                       OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")])

# Special mVc elements
SP_All_mVc_Bias<-rbind(OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                        OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
SP_All_mVc_EMSE<-rbind(OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                        OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
SP_All_mVc_MSE<-rbind(OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
                       OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
SP_All_mVc_Info<-rbind(OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                        OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
SP_All_mVc_VAR<-rbind(OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
                       OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove(list = All_Objects[startsWith(All_Objects,"RS")])
```

# Best Sub-sampling Method : `r params$Model_Path`

# Compare SMSE, EMSE, Variance, Information and Bias for all methods.

```{r Compare All,fig.width=20,fig.height=12}
All_Bias %>% 
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

All_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

All_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

All_VAR %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

All_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE,nrow = 2,ncol = 3)
```

# Special Comparison of SMSE, EMSE, Variance, Information and Bias for mMSE.
## (Real Model and Assumed Model results with Full Data Real Model)

```{r Special Compare 1,fig.width=20,fig.height=12}
SP_All_mMSE_Bias %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

SP_All_mMSE_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

SP_All_mMSE_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

SP_All_mMSE_VAR %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

SP_All_mMSE_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE,nrow = 2,ncol = 3)
```

# Compare  SMSE, EMSE, Variance, Information and Bias for mVc.
## (Real Model and Assumed Model results with Full Data Real Model)

```{r Special Compare 2,fig.width=20,fig.height=12}
SP_All_mVc_Bias %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

SP_All_mVc_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

SP_All_mVc_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

SP_All_mVc_VAR %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

SP_All_mVc_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE,nrow = 2,ncol = 3)
```

### 2022-01-17 Publication_Ready.Rmd
First commit of all files

---
title: "Publication Ready"
author: "Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 15,fig.height = 20,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)
```

# Using Uniform Distribution for Data

## Model : `r params$Model_Path`

```{r load Identical Data}
Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

# Random Sampling
load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_RS.RData"))

for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Bias<-All_Bias 
RS_EMSE<-All_EMSE
RS_Info<-All_Info
RS_MSE<-All_MSE
RS_VAR<-All_VAR

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))

All_Bias<-All_Bias[!(All_Bias$Model %in% remove_stuff),]
All_EMSE<-All_EMSE[!(All_EMSE$Model %in% remove_stuff),]
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
                OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Bias)[3]<-"Estimated Values"
colnames(All_EMSE)[3]<-"Estimated Values"
colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_VAR)[3]<-"Estimated Values"

Final_Data_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
                               cbind.data.frame(Metric="EMSE",All_EMSE),
                               cbind.data.frame(Metric="Model Information",All_Info),
                               cbind.data.frame(Metric="MSE",All_MSE),
                               cbind.data.frame(Metric="Variance",All_VAR))

remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR)
```

```{r load Non Identical Data}
Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

# OSMAC
load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC Model Free
load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_MF.RData"))

Old_Labels[1]<-c("Real Model")

All_Bias<-All_Bias[All_Bias$Model==Old_Labels[1],]
All_EMSE<-All_EMSE[All_EMSE$Model==Old_Labels[1],]
All_Info<-All_Info[All_Info$Model==Old_Labels[1],]
All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]

## mMSE
All_Bias$Model[All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_EMSE$Model[All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_Info$Model[All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")

OSMAC_MF_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_MF_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_MF_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

## mVc
All_Bias$Model[All_Bias$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_EMSE$Model[All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_Info$Model[All_Info$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")

OSMAC_MF_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_MF_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_MF_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")],
                OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")],
                OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
               OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
                OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")],
                OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")],
                OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
               OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
               OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
               OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")],
               OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove(list = All_Objects[startsWith(All_Objects,"RS")])

All_Bias$Model<-factor(All_Bias$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                               "OSMAC mMSE RM","OSMAC mVc RM",
                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                               "OSMAC mMSE MF","OSMAC mVc MF"))
All_EMSE$Model<-factor(All_EMSE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                               "OSMAC mMSE RM","OSMAC mVc RM",
                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                               "OSMAC mMSE MF","OSMAC mVc MF"))
All_Info$Model<-factor(All_Info$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                               "OSMAC mMSE RM","OSMAC mVc RM",
                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                               "OSMAC mMSE MF","OSMAC mVc MF"))
All_MSE$Model<-factor(All_MSE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                             "OSMAC mMSE RM","OSMAC mVc RM",
                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                             "OSMAC mMSE MF","OSMAC mVc MF"))
All_VAR$Model<-factor(All_VAR$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                             "OSMAC mMSE RM","OSMAC mVc RM",
                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                             "OSMAC mMSE MF","OSMAC mVc MF"))

colnames(All_Bias)[3]<-"Estimated Values"
colnames(All_EMSE)[3]<-"Estimated Values"
colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_VAR)[3]<-"Estimated Values"

Final_Data_Non_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
                                   cbind.data.frame(Metric="EMSE",All_EMSE),
                                   cbind.data.frame(Metric="Model Information",All_Info),
                                   cbind.data.frame(Metric="MSE",All_MSE),
                                   cbind.data.frame(Metric="Variance",All_VAR))

remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR)
```

```{r Identical r0 Plots}
# mMSE models Colors
Selected_mMSE<-c(#"RS RM",
                 #"RS AM 1","RS AM 2","RS AM 3",
                 "OSMAC mMSE RM",
                 "OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                 "OSMAC mMSE MF")
Colors_mMSE<-c(#"#88CCEE",
               #"#A6C3D3","#5D92B0","#35586C", 
               "#FFC4D8", 
               "#E28490","#BB2C3E","#55141C", 
               "#DDCC77")
# mvc models
Selected_mVc<-c(#"RS RM",
                #"RS AM 1","RS AM 2","RS AM 3",
                "OSMAC mVc RM",
                "OSMAC mVc AM 1","OSMAC mVc AM 2","OSMAC mVc AM 3",
                "OSMAC mVc MF")
Colors_mVc<-c(#"#88CCEE",
              #"#A6C3D3","#5D92B0","#35586C", 
              "#FFC4D8", 
               "#E28490","#BB2C3E","#55141C", 
               "#DDCC77")

Final_Data<-rbind(cbind(Data="Identical r0",Final_Data_Identical_r0),
                  cbind(Data="Non Identical r0",Final_Data_Non_Identical_r0))

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p1

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p2

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p3

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p4

ggarrange(p1,p2,p3,p4,nrow = 4)
```

```{r Identical r0 Plots with gg.gap,fig.height=4}
SS_Choice<-100*c(10:15)

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p1_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p2_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p3_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p4_New
```

```{r All Plots}
ggarrange(p1,p1_New,
          p2,p2_New,nrow = 4)
```

### 2022-01-17 Checking_SP_Model_1_Exponential_Special.R

@@ -1,0 +1,886 @@
+# Model 1 ----
+
+# Real Model :$$ \lambda = \exp(\beta_0 + \beta_1 X_1 + \beta_2 X_2)$$
+# Assumed Model 1:$$ \lambda = \exp(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_1^2)$$
+# Assumed Model 2:$$ \lambda = \exp(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_2^2)$$
+# Assumed Model 3:$$ \lambda = \exp(\beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_1^2 + \beta_4 X_2^2)$$
+
+A_optimality<-function(x,Theta,Model)
+{
+  x1<-x[1]; x2<-x[2]
+  if(Model=="Real_Model") {X<-cbind(1,x1,x2)}
+         
+  if(Model=="Assumed_Model_1") {X<-cbind(1,x1,x2,x1^2)}
+  
+  if(Model=="Assumed_Model_2") {X<-cbind(1,x1,x2,x2^2)}
+  
+  if(Model=="Assumed_Model_3") {X<-cbind(1,x1,x2,x1^2,x2^2)}
+  
+  lp <- X%*%Theta
+  p <- as.vector(exp(lp))
+  W <- diag(p,1)
+  sum(diag(solve(t(X)%*%W%*%X)))
+}
+  
+All_Models<-list(Real_Model=c("X0","X1","X2"),
+                 Assumed_Model_1=c("X0","X1","X2","X1^2"),
+                 Assumed_Model_2=c("X0","X1","X2","X2^2"),
+                 Assumed_Model_3=c("X0","X1","X2","X1^2","X2^2"))
+
+Generate_Data<-function(Theta,N,All_Models)
+{
+  X<-replicate(2,runif(n = N,min = 0,max = 1))
+  Complete_Data<-cbind(1,X,X^2)
+  colnames(Complete_Data)<-c(paste0("X",0:ncol(X)),
+                             paste0("X",1:ncol(X),"^2"))
+  
+  Pi_Data <- exp(Complete_Data[,colnames(Complete_Data) %in% All_Models$Real_Model]%*%Theta)
+  Y_Data <- rpois(N,Pi_Data)
+  
+  All_Data<-list()
+  for (i in 1:length(All_Models)) 
+  {
[…]

### 2022-01-17 Identical_r0/Rmarkdown/Classical/OSMAC_Command.R

@@ -1,0 +1,18 @@
+library(here)
+library(ezknitr)
+library(rmarkdown)
+
+Model<-c("Model_1","Model_2",
+         "Model_3","Model_4") ; j=4
+
+for (j in 1:length(Model)) 
+{
+  # OSMAC Method ----
+  ezknit(file=here("Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
+         out_dir=here("Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
+         fig_dir = c("Plots"),
+         params=list("Model_Path"=Model[j]),
+         verbose = TRUE,keep_md = FALSE)
+  #open_output_dir()
+}
+

### 2022-01-17 Identical_r0/Rmarkdown/Classical/Summary/Summary_Rmarkdown.R

@@ -1,0 +1,18 @@
+library(here)
+library(ezknitr)
+library(rmarkdown)
+
+Model<-c("Model_1","Model_2",
+         "Model_3","Model_4"); i=4
+
+# Best_Subsampling_Method ----
+for (i in 1:length(Model))
+{
+ezknit(file=here("Identical_r0","Rmarkdown","Classical","Summary","Best_Subsampling_Method.Rmd"),
+        out_dir=here("Identical_r0","Summary","Classical",Model[i],"Best_Subsampling"),
+        fig_dir = c("Plots"),
+        params=list("Model_Path"=Model[i]),
+        verbose = TRUE,keep_md = FALSE)
+open_output_dir()
+}
+

### 2022-01-17 Identical_r0/Simulation_Setup/Classical/Analysis/OSMAC/Simulation_Results_OSMAC_Sampling.R

@@ -1,0 +1,92 @@
+# Run for OSMAC Sampling----
+library(compiler)
+library(here)
+library(LaplacesDemon)
+
+enableJIT(1)
+
+# Load the No Correlated Data----
+load(here("Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Init.RData"))
+#load(here("Init.RData"))
+
+# Load the OSMAC Sample----
+load(here("Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Run_OSMAC.RData"))
+#load(here("Run_OSMAC.RData"))
+
+All_Covariates<-c("X0","X1","X2","X1^2","X2^2")
+
+# Model 1----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+if(Model_Path=="Model_1")
+{
+  combs<-list(All_Covariates[-5],
+              All_Covariates[-4],
+              All_Covariates) 
+  
+  Final_Parameter<-Run_OSMAC(Replicates = Replicates, r1 = r0, r2 = c(100*(2:15)),
+                             Y = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                             X = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                             Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
+                             N = Simulated_Data$Basic$N,
+                             alpha = rep(1/4,length(combs)+1),
+                             combs = combs,
+                             All_Covariates = All_Covariates)
+}
+
+# Model 2----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+if(Model_Path=="Model_2")
+{
+  combs<-list(All_Covariates[-c(4,5)],
+              All_Covariates[-4],
+              All_Covariates) 
+  
+  Final_Parameter<-Run_OSMAC(Replicates = Replicates, r1 = r0, r2 = c(100*(2:15)),
+                             Y = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                             X = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                             Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
+                             N = Simulated_Data$Basic$N,
+                             alpha = rep(1/4,length(combs)+1),
+                             combs = combs,
[…]

### 2022-01-17 Identical_r0/Simulation_Setup/Classical/R_Scripts/OSMAC_Algorithm.R

@@ -1,0 +1,530 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two step OSMAC ----
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
+    Y_Real<-Real_Data[,1] #  Real Data
+    X_Real<-Real_Data[,-1] # Real Data
+    
+    PI.prop <- rep(1/n, n)
+    idx.prop <- sample(1:n, r1, T, PI.prop)
+    
+    x.prop<-lapply(1:length(combs),function(j){
+      X[idx.prop,All_Covariates %in% combs[[j]]] # Assumed Data 
+    })
+    y.prop <- Y[idx.prop,]  # Assumed Data 
+    
+    x_Real.prop<-X_Real[idx.prop,] # Real Data
+    y_Real.prop<-Y_Real[idx.prop] # Real Data
+    
+    pinv.prop <- rep(n,r1)
+    
+    fit.prop <- lapply(1:length(combs), function(j){
+      glm(y.prop~x.prop[[j]]-1,family = "poisson")# Assumed Data
+    })
+    fit_Real.prop <- glm(y_Real.prop~x_Real.prop-1,family = "poisson") # Real Data
+    
+    beta.prop<-list()
+    for (j in 1:length(combs)) 
+      {
+      beta.prop[[j]] <- fit.prop[[j]]$coefficients # Assumed Data
+      if(anyNA(beta.prop[[j]]))
+        {
+        return(list(opt=NA, msg="first stage not converge"))
+        }
+      }
+    beta_Real.prop <- fit_Real.prop$coefficients # Real Data
+    
+    if(anyNA(beta_Real.prop[1]))
+      return(list(opt=NA, msg="first stage not converge"))
+    
[…]

### 2022-01-17 Identical_r0/Simulation_Setup/Classical/R_Scripts/OSMAC_Setup.R

@@ -1,0 +1,352 @@
+library(here)
+library(compiler)
+library(LaplacesDemon)
+
+# Load the OSMAC algorithm
+source(here("Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Algorithm.R"))
+
+AlgTwoStp<-cmpfun(AlgTwoStp)
+Cordeiro<-cmpfun(Cordeiro)
+
+# Using OSMAC to Sub-sample from Big Data ----
+Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
+{
+  X_Real<-Real_Data[,-1]
+  # From r0 and r conduct OSMAC subsampling for Logistic regression-----
+  Parameter_Real_mMSE<-list(); Parameter_Real_mVc<-list()
+  Parameter_ModelFree_mMSE<-list(); Parameter_ModelFree_mVc<-list()
+  
+  for (j in 1:length(combs)) 
+  {
+    assign(paste0("Parameter_Assumed_Old_mMSE_",j),list())
+    assign(paste0("Parameter_Assumed_Old_mVc_",j),list())
+    assign(paste0("Parameter_Assumed_New_mMSE_",j),list())
+    assign(paste0("Parameter_Assumed_New_mVc_",j),list())  
+  }
+  
+  Bias_Real_mMSE<-list(); Bias_Real_mVc<-list()
+  Bias_ModelFree_mMSE<-list(); Bias_ModelFree_mVc<-list()
+  
+  for(j in 1:length(combs))
+  {
+    assign(paste0("Bias_Assumed_Old_mMSE_",j),list())
+    assign(paste0("Bias_Assumed_Old_mVc_",j),list())
+    assign(paste0("Bias_Assumed_New_mMSE_",j),list())
+    assign(paste0("Bias_Assumed_New_mVc_",j),list())
+  }
+  
+  Utility_Real_mMSE<-list(); Utility_Real_mVc<-list()
+  Utility_ModelFree_mMSE<-list(); Utility_ModelFree_mVc<-list()
+  
+  for(j in 1:length(combs))
+  {
+    assign(paste0("Utility_Assumed_Old_mMSE_",j),list())
+    assign(paste0("Utility_Assumed_Old_mVc_",j),list())
+    assign(paste0("Utility_Assumed_New_mMSE_",j),list())
[…]

### 2022-01-17 Identical_r0/Simulation_Setup/Classical/R_Scripts/Setup_Data.R

@@ -1,0 +1,19 @@
+library(here)
+
+#Model_Path<-"Model_1"
+#Model_Path<-"Model_2"
+#Model_Path<-"Model_3"
+Model_Path<-"Model_4"
+
+# OSMAC Data ----
+Base_Path<-"OSMAC"
+
+## No Correlated Covariate Data -----
+load(here("Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
+save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
+     file = here("Identical_r0","Simulation_Setup","Classical","Analysis",
+                 Base_Path,"Init.RData"))        
+
+remove(Base_Path)
+
+rm(list = ls())

### 2022-01-17 Non_Identical_r0/Rmarkdown/Classical/Random_Sampling_And_OSMAC.R

@@ -1,0 +1,34 @@
+library(here)
+library(ezknitr)
+library(rmarkdown)
+
+Model<-c("Model_1","Model_2",
+         "Model_3","Model_4") ; j=4
+
+# Random Sampling ----
+ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Random_Sampling.Rmd"),
+       out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"Random_Sampling"),
+       fig_dir = c("Plots"),
+       params=list("Model_Path"=Model[j]),
+       verbose = TRUE,keep_md = FALSE)
+open_output_dir()
+
+for (j in 1:length(Model)) 
+{
+        # OSMAC Method ----
+        ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
+               out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
+               fig_dir = c("Plots"),
+               params=list("Model_Path"=Model[j]),
+               verbose = TRUE,keep_md = FALSE)
+        #open_output_dir()
+        
+        # OSMAC Model Free Method ----
+        ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Model_Free_Method.Rmd"),
+               out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC_Model_Free"),
+               fig_dir = c("Plots"),
+               params=list("Model_Path"=Model[j]),
+               verbose = TRUE,keep_md = FALSE)
+        #open_output_dir()
+}
+

### 2022-01-17 Non_Identical_r0/Rmarkdown/Classical/Summary/Summary_Rmarkdown.R

@@ -1,0 +1,18 @@
+library(here)
+library(ezknitr)
+library(rmarkdown)
+
+Model<-c("Model_1","Model_2",
+         "Model_3","Model_4"); i=4
+
+# Best_Subsampling_Method ----
+for (i in 1:length(Model))
+{
+  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Summary","Best_Subsampling_Method.Rmd"),
+         out_dir=here("Non_Identical_r0","Summary","Classical",Model[i],"Best_Subsampling"),
+         fig_dir = c("Plots"),
+         params=list("Model_Path"=Model[i]),
+         verbose = TRUE,keep_md = FALSE)
+  open_output_dir()
+}
+

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/Analysis/OSMAC/Simulation_Results_OSMAC_Sampling.R

@@ -1,0 +1,48 @@
+# Run for OSMAC Sampling----
+library(compiler)
+library(here)
+library(LaplacesDemon)
+
+enableJIT(1)
+
+# Load the No Correlated Data----
+load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Init.RData"))
+
+# Load the OSMAC Sample----
+load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Run_OSMAC.RData"))
+
+# Real Model ----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
+                           Y=as.matrix(Simulated_Data[[2]]$Real_Model[,1]),
+                           X=as.matrix(Simulated_Data[[2]]$Real_Model[,-1]),
+                           Real_Data=as.matrix(Simulated_Data[[2]]$Real_Model),
+                           N=Simulated_Data$Basic$N,Model="Real_Model")
+
+# Assumed Model 1 ----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
+                           Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,1]),
+                           X=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,-1]),
+                           Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1")
+
+# Assumed Model 2 ----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
+                           Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,1]),
+                           X=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,-1]),
+                           Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/Analysis/OSMAC_Model_Free/Simulation_Results_OSMAC_Sampling.R

@@ -1,0 +1,88 @@
+# Run for OSMAC Sampling----
+library(compiler)
+library(here)
+library(LaplacesDemon)
+
+enableJIT(1)
+
+# Load the No Correlated Data----
+load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC_Model_Free","Init.RData"))
+
+# Load the OSMAC Sample----
+load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC_Model_Free","Run_OSMAC.RData"))
+
+All_Covariates<-c("X0","X1","X2","X1^2","X2^2")
+
+# Model 1 ----
+
+if(Model_Path=="Model_1")
+{
+  combs<-list(All_Covariates[-c(4,5)],
+              All_Covariates[-5],
+              All_Covariates[-4],
+              All_Covariates)
+  
+  # Generate for Random sample of 1000 different times ----
+  ## Pi=MMSE and Pi=MVC Proportional probabilities ---
+  Final_Parameter<-Run_OSMAC_MF(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
+                                Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                                X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                                alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
+                                All_Covariates=All_Covariates,
+                                combs=combs)
+}
+
+# Model 2 ----
+
+if(Model_Path=="Model_2")
+{
+  combs<-list(All_Covariates[-5],
+              All_Covariates[-c(4,5)],
+              All_Covariates[-4],
+              All_Covariates)
+  
+  # Generate for Random sample of 1000 different times ----
+  ## Pi=MMSE and Pi=MVC Proportional probabilities ---
+  Final_Parameter<-Run_OSMAC_MF(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
+                                Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                                X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                                alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
+                                All_Covariates=All_Covariates,
+                                combs=combs)
+}
+
+# Model 3 ----
+if(Model_Path=="Model_3")
+{
+  combs<-list(All_Covariates[-4],
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/Analysis/Random_Sampling/Simulation_Results_Random_Sampling.R

@@ -1,0 +1,82 @@
+# Run for Random Sampling----
+library(compiler)
+library(here)
+library(LaplacesDemon)
+
+enableJIT(1)
+
+# Load the No Correlated Data----
+load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling","Init.RData"))
+
+# Load the Random Sample----
+load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling","Run_RandomSample.RData"))
+
+# Real Model ----
+# Generate for Random sample of 1000 different times
+Final_Parameter<-Run_RandomSample(Replicates = Replicates, 
+                                  FullData = Simulated_Data[[2]]$Real_Model,
+                                  N=Simulated_Data$Basic$N,
+                                  Subsample_Size=Subsample_Size,Choices=c(100*(2:15)),
+                                  No_of_Models = 4)
+
+Est_Param_RandomSample<-Final_Parameter$EstPar[[1]]
+Utility_RandomSample<-Final_Parameter$Utility[[1]]
+#SelectedData_RandomSample<-Final_Parameter$Subsampled_Data[[1]]
+Bias_RandomSample<-Final_Parameter$Bias[[1]]
+
+# Save the Results ----
+save(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample,#SelectedData_RandomSample,
+     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling",
+                 "Results","Real_Model","Random_Sample_output.RData"))
+
+save(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample,#SelectedData_RandomSample,
+     file = here("Non_Identical_r0","Outputs","Classical",Model_Path,"Random_Sampling",
+                 "Real_Model","Random_Sample_output.RData"))
+
+# Assumed Model 1----
+# Generate for Random sample of 1000 different times
+Est_Param_RandomSample<-Final_Parameter$EstPar[[2]]
+Utility_RandomSample<-Final_Parameter$Utility[[2]]
+#SelectedData_RandomSample<-Final_Parameter$Subsampled_Data[[2]]
+Bias_RandomSample<-Final_Parameter$Bias[[2]]
+
+# Save the Results ---
+save(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample,#SelectedData_RandomSample,
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/R_Scripts/OSMAC_Algorithm.R

@@ -1,0 +1,203 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two step OSMAC ----
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
+  if(Model=="Real_Model")
+  {
+    PI.prop <- rep(1/n, n)
+    idx.prop <- sample(1:n, r1, T, PI.prop)
+    x.prop <- X[idx.prop,]
+    y.prop <- Y[idx.prop]
+    pinv.prop <- rep(n,r1)
+    fit.prop <- glm(y.prop~x.prop-1,family = "poisson")
+    beta.prop <- fit.prop$coefficients
+    if (is.na(beta.prop[1]))
+      return(list(opt=NA, msg="first stage not converge"))
+    P.prop  <- exp(X %*% beta.prop)
+    
+    beta.mVc<-matrix(nrow = length(r2),ncol = ncol(X) )
+    Utility_mVc<-matrix(nrow = length(r2),ncol = 3 )
+    Bias_mVc<-matrix(nrow = length(r2),ncol = ncol(X) )
+    
+    beta.mMSE<-matrix(nrow = length(r2),ncol = ncol(X) )
+    Utility_mMSE<-matrix(nrow = length(r2),ncol = 3 )
+    Bias_mMSE<-matrix(nrow = length(r2),ncol = ncol(X) )
+    
+    #Sample.mMSE<-list()
+    #Sample.mVc<-list()
+    
+    ## mVC
+    for (i in 1:length(r2)) 
+    {
+      PI.mVc <- sqrt((Y - P.prop)^2 * rowSums(X^2))
+      PI.mVc <- PI.mVc / sum(PI.mVc)
+      
+      idx.mVc <- sample(1:n, r2[i]-r1, T, PI.mVc)
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/R_Scripts/OSMAC_Model_Free/OSMAC_Algorithm_Model_Free.R

@@ -1,0 +1,183 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two Step OSMAC ----
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) {
+  
+  PI.prop <- rep(1/n, n)
+  idx.prop <- sample(1:n, r1, T, PI.prop)
+  
+  y.prop <- Y[idx.prop]
+  pinv.prop <- rep(n,r1)
+  
+  beta.prop<-list()
+  beta.prop<-lapply(1:length(combs),function(i) {
+    glm(y.prop~X[idx.prop,colnames(X) %in% combs[[i]]]-1, family = "poisson")})
+   
+  for (i in 1:length(combs)) 
+  {
+    if (anyNA(beta.prop[[i]]$coefficients))
+    {
+      stop("There are NA or NaN values")
+    }
+  }
+  
+  P.prop<-list()
+  P.prop<-lapply(1:length(combs), function(i)
+    exp(X[,colnames(X) %in% combs[[i]]] %*% beta.prop[[i]]$coefficients))
+  
+  beta.mVc<-Utility_mVc<-Bias_mVc<-list()
+  beta.mMSE<-Utility_mMSE<-Bias_mMSE<-list()
+  
+  for (a in 1:length(combs)) 
+  {
+    beta.mVc[[a]]<-matrix(nrow = length(r2),ncol = length(combs[[a]])) #
+    Utility_mVc[[a]]<-matrix(nrow = length(r2),ncol = 3 ) #
+    Bias_mVc[[a]]<-matrix(nrow = length(r2),ncol = length(combs[[a]])) #
+    
+    beta.mMSE[[a]]<-matrix(nrow = length(r2),ncol = length(combs[[a]])) #
+    Utility_mMSE[[a]]<-matrix(nrow = length(r2),ncol = 3) #
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/R_Scripts/OSMAC_Model_Free/OSMAC_Model_Free_Setup.R

@@ -1,0 +1,136 @@
+library(here)
+library(compiler)
+library(LaplacesDemon)
+library(matrixStats)
+
+# Load the OSMAC algorithm
+source(here("Non_Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Model_Free",
+            "OSMAC_Algorithm_Model_Free.R"))
+
+OSMAC_MF<-cmpfun(OSMAC_MF)
+Cordeiro<-cmpfun(Cordeiro)
+
+# Using OSMAC to Sub-sample from Big Data----
+Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N)
+{
+  # From r0 and r conduct OSMAC subsampling for Logistic regression-----
+  Parameter_mMSE<-replicate(length(combs),list()) ;
+  Parameter_mVc<-replicate(length(combs),list()) ;
+
+  Bias_mMSE<-replicate(length(combs),list()) ; 
+  Bias_mVc<-replicate(length(combs),list()) ; 
+
+  Utility_mMSE<-replicate(length(combs),list()) ; 
+  Utility_mVc<-replicate(length(combs),list()) ;
+
+  # Sample_mMSE<-replicate(length(combs),list()) ;  
+  # Sample_mVc<-replicate(length(combs),list()) ; 
+  
+  i=1
+  while(i <= Replicates)
+  {
+    tryCatch({
+      Results<-OSMAC_MF(r1,r2,Y,X,n=N,alpha,combs,All_Covariates)
+      
+      for (j in 1:length(combs)) 
+      {
+        Parameter_mMSE[[j]][[i]]<-Results$opt[[j]]$Est_Theta_mMSE
+        Parameter_mVc[[j]][[i]]<-Results$opt[[j]]$Est_Theta_mVc
+        
+        Bias_mMSE[[j]][[i]]<-Results$opt[[j]]$Bias_mMSE
+        Bias_mVc[[j]][[i]]<-Results$opt[[j]]$Bias_mVc
+        
+        Utility_mMSE[[j]][[i]]<-Results$opt[[j]]$Utility_mMSE
+        Utility_mVc[[j]][[i]]<-Results$opt[[j]]$Utility_mVc
+        
+        # Sample_mMSE[[j]][[i]]<-cbind(i,Results$Sample_mMSE[,colnames(Results$Sample_mMSE) %in% c("r2","Y","SP",combs[[j]]) ])
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/R_Scripts/OSMAC_Setup.R

@@ -1,0 +1,102 @@
+library(here)
+library(compiler)
+library(LaplacesDemon)
+
+# Load the OSMAC algorithm
+source(here("Non_Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Algorithm.R"))
+
+AlgTwoStp<-cmpfun(AlgTwoStp)
+Cordeiro<-cmpfun(Cordeiro)
+
+# Using OSMAC to Sub-sample from Big Data ----
+Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model)
+{
+  # From r0 and r conduct OSMAC subsampling for Logistic regression-----
+  Parameter_mMSE<-list()
+  Parameter_mVc<-list()
+
+  Bias_mMSE<-list()
+  Bias_mVc<-list()
+
+  Utility_mMSE<-list()
+  Utility_mVc<-list()
+
+  #Sample_mMSE<-list()
+  #Sample_mVc<-list()
+  i=1
+  while(i <= Replicates)
+  {
+    tryCatch({
+      Results<-AlgTwoStp(r1,r2,Y,X,Real_Data,n=N,Model)
+      
+      Parameter_mMSE[[i]]<-Results$opt$Est_Theta_mMSE
+      Parameter_mVc[[i]]<-Results$opt$Est_Theta_mVc
+      
+      Bias_mMSE[[i]]<-Results$opt$Bias_mMSE
+      Bias_mVc[[i]]<-Results$opt$Bias_mVc
+      
+      Utility_mMSE[[i]]<-Results$opt$Utility_mMSE
+      Utility_mVc[[i]]<-Results$opt$Utility_mVc
+      
+      #Sample_mMSE[[i]]<-cbind(i,Results$opt$Sample_mMSE)
+      #Sample_mVc[[i]]<-cbind(i,Results$opt$Sample_mVc)
+      
+      print(i)
+      i<-i+1
+    },error=function(e){ i=i})
+    
+  }
+
+  Final_param_mMSE<-do.call(rbind,Parameter_mMSE)
+  Final_param_mVc<-do.call(rbind,Parameter_mVc)
+
+  Final_bias_mMSE<-do.call(rbind,Bias_mMSE)
+  Final_bias_mVc<-do.call(rbind,Bias_mVc)
+
+  Final_utility_mMSE<-do.call(rbind,Utility_mMSE)
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/R_Scripts/Random_Sampling_Setup.R

@@ -1,0 +1,85 @@
+library(here)
+library(compiler)
+library(LaplacesDemon)
+
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Using Random Sampling Sub-sample from Big Data ----
+Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_Models)
+{
+  #RandomSample<-list()
+  #Sample_RS<-list()
+  
+  All_Parameter<-list()
+  Est_Parameter <- matrix(NA,nrow = length(Choices),ncol = ncol(FullData))
+
+  All_Bias<-list()
+  Bias <- matrix(NA,nrow = length(Choices),ncol = ncol(FullData))
+
+  All_optimality<-list()
+  optimality <- matrix(NA,nrow = length(Choices),ncol = 3)
+
+  Final_Parameter<-Final_optimality<-Final_Bias<-list()
+  
+  for (k in 1:No_of_Models) 
+  {
+    cat("Model :",k,"\n")
+    for(i in 1:Replicates)
+    {
+      Sampled<-sample(1:N,size = Subsample_Size)
+      Temp_Data<-as.data.frame(FullData[Sampled,])
+      #RandomSample[[i]]<-Temp_Data
+      
+      for (j in 1:length(Choices))
+      {
+        Temp_Temp_Data<-Temp_Data[1:Choices[j],]
+        Results<-glm(Y~.-1,data=Temp_Temp_Data,family = "poisson")
+        Est_Parameter[j,]<-c(Choices[j],Results$coefficients)
+        optimality[j,]<-c(Choices[j], psych::tr(vcov(Results)), det(solve(summary(Results)$cov.unscaled)) )
+        Bias[j,]<-c(Choices[j],Cordeiro(XData = as.matrix(Temp_Temp_Data[,-1]),
+                                        With_bias = as.vector(Results$coefficients)))
+      }
+      
+      All_Parameter[[i]]<-Est_Parameter
[…]

### 2022-01-17 Non_Identical_r0/Simulation_Setup/Classical/R_Scripts/Setup_Data.R

@@ -1,0 +1,39 @@
+library(here)
+
+#Model_Path<-"Model_1"
+#Model_Path<-"Model_2"
+#Model_Path<-"Model_3"
+Model_Path<-"Model_4"
+
+# Random Sampling Data ----
+Base_Path<-"Random_Sampling"
+
+## No Correlated Covariate Data -----
+load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
+save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path"),
+     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
+                 Base_Path,"Init.RData"))        
+
+# OSMAC Data ----
+Base_Path<-"OSMAC"
+
+## No Correlated Covariate Data -----
+load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
+save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
+     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
+                 Base_Path,"Init.RData"))        
+
+remove(Base_Path)
+
+# OSMAC Model Free Data ----
+Base_Path<-"OSMAC_Model_Free"
+
+## No Correlated Covariate Data -----
+load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
+save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
+     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
+                 Base_Path,"Init.RData"))
+
+remove(Base_Path)
+
+rm(list = ls())

### 2022-01-17 Publication_Ready_command.R

@@ -1,0 +1,17 @@
+library(here)
+library(ezknitr)
+library(rmarkdown)
+
+Model<-c("Model_1","Model_2",
+         "Model_3","Model_4"); #i=4
+
+for(i in 1:length(Model))
+{
+  # Publication Ready ----
+  ezknit(file=here("Publication_Ready.Rmd"),
+         out_dir=here("Publication_Ready",Model[i]),
+         fig_dir = c("Plots"),
+         params=list("Model_Path"=Model[i]),
+         verbose = TRUE,keep_md = TRUE,keep_html = FALSE)
+  open_output_dir()
+}

### 2022-01-29 Articles.Rmd
update article plots

---
title: "Articles_Plots"
author: "Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 14,fig.height = 16,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)

```

# Using Exponential Distribution for Data

```{r Load data model 1}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove("RS_Info","RS_MSE")

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r Load data model 2}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove("RS_Info","RS_MSE")

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r Load data model 3}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove("RS_Info","RS_MSE")

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r Load data model 4}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove("RS_Info","RS_MSE")

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r combine data and plot,fig.width = 18,fig.height = 10}
Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
                    M3_Identical_r0,M4_Identical_r0)

Identical_ro$Covariate<-factor(Identical_ro$Covariate,
                               levels = c("X1, X2","X1, X2, X1\u00B2",
                                          "X1, X2, X2\u00B2","X1, X2, X1\u00B2, X2\u00B2"))

Identical_ro$Model<-factor(Identical_ro$Model,
                           levels = c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                      "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                                      "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
                                      "OSMAC mMSE MF","OSMAC mVc MF"))

Selected_Models_mMSE<-c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                        "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                        "OSMAC mMSE MF")

Colors_mMSE<-c("#FFC4D8", "#E28490","#BB2C3E","#55141C",
               "#88CCEE", "#A6C3D3","#5D92B0","#35586C", 
               "#DDCC77")

Selected_Models_mVc<-c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                       "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
                       "OSMAC mVc MF")

Colors_mVc<-Colors_mVc<-c("#FFC4D8","#E28490","#BB2C3E","#55141C", 
                          "#88CCEE","#A6C3D3","#5D92B0","#35586C", 
                          "#DDCC77")

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("Model Information")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("Model Information")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("SMSE")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("SMSE")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p4

ggarrange(p1,p3,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
ggarrange(p2,p4,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
```

### 2022-02-01 Articles.Rmd
update article rmd with colors

@@
 Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
-New_Labels<-c("RM",paste0("AM ",1:3),"MF")
+New_Labels<-c("RM",paste0("AM ",1:3),"MR")
 
@@
                                       "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
-                                      "OSMAC mMSE MF","OSMAC mVc MF"))
+                                      "OSMAC mMSE MR","OSMAC mVc MR"))
 
-Selected_Models_mMSE<-c("RS RM","RS AM 1","RS AM 2","RS AM 3",
+Selected_Models_mMSE<-c("RS RM",#"RS AM 1","RS AM 2","RS AM 3",
                         "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
-                        "OSMAC mMSE MF")
+                        "OSMAC mMSE MR")
 
-Colors_mMSE<-c("#FFC4D8", "#E28490","#BB2C3E","#55141C",
-               "#88CCEE", "#A6C3D3","#5D92B0","#35586C", 
+Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
+               "#FFC4D8", "#E28490","#BB2C3E","#55141C",
                "#DDCC77")
 
-Selected_Models_mVc<-c("RS RM","RS AM 1","RS AM 2","RS AM 3",
+Selected_Models_mVc<-c("RS RM",#"RS AM 1","RS AM 2","RS AM 3",
                        "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
-                       "OSMAC mVc MF")
+                       "OSMAC mVc MR")
 
-Colors_mVc<-Colors_mVc<-c("#FFC4D8","#E28490","#BB2C3E","#55141C", 
-                          "#88CCEE","#A6C3D3","#5D92B0","#35586C", 
+Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
+                          "#FFC4D8","#E28490","#BB2C3E","#55141C", 
                           "#DDCC77")

### 2022-02-19 Articles.Rmd
update legend and axis's in articles

@@
 
-# Using Exponential Distribution for Data
+# Using Uniform Distribution for Data
 
@@
 Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
-New_Labels<-c("RM",paste0("AM ",1:3))
+New_Labels<-c("DM",paste0("AM ",1:3))
 
@@
 Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
-New_Labels<-c("RM",paste0("AM ",1:3),"MR")
+New_Labels<-c("DM",paste0("AM ",1:3),"MR")
 
@@
 {
-  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
 }
@@
 {
-  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
 }
@@
 remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
-remove("RS_Info","RS_MSE")
 
@@
 Identical_ro$Model<-factor(Identical_ro$Model,
-                           levels = c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                      "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
-                                      "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
-                                      "OSMAC mMSE MR","OSMAC mVc MR"))
+                           levels = c("RS DM","RS AM 1","RS AM 2","RS AM 3",
+                                      "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
+                                      "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
+                                      "mMSE MR","mVc MR"))
 
-Selected_Models_mMSE<-c("RS RM",#"RS AM 1","RS AM 2","RS AM 3",
-                        "OSMAC mMSE RM","OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
-                        "OSMAC mMSE MR")
+Selected_Models_mMSE<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
+                        "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
+                        "mMSE MR")
 
@@
 
-Selected_Models_mVc<-c("RS RM",#"RS AM 1","RS AM 2","RS AM 3",
-                       "OSMAC mVc RM", "OSMAC mVc AM 1", "OSMAC mVc AM 2","OSMAC mVc AM 3",
-                       "OSMAC mVc MR")
+Selected_Models_mVc<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
+                       "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
+                       "mVc MR")
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("Model Information")+
+  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
   theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p1
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank())->p1
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("Model Information")+
+  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
   theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p2
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank())->p2
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("SMSE")+
+  xlab("Sub-sample size")+ylab("SMSE")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
   theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p3
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank())->p3
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("SMSE")+
+  xlab("Sub-sample size")+ylab("SMSE")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
   theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))->p4
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank())->p4
 

### 2022-04-04 Articles.Rmd
update articles files and gifski package

@@
 
-# Using Uniform Distribution for Data
+```{r Load data model 1}
+load(here("Identical_r0","Generate_Big_Data","Model_1","No_Correlated_Covariate.RData"))
+Model_1_SS<-r0
 
-```{r Load data model 1}
+remove(Simulated_Data,Model_1,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M1_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2",Metric="MSE",All_MSE))
+M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M1_Identical_r0$Subsample_Size<-M1_Identical_r0$Subsample_Size-Model_1_SS
 ```
@@
 ```{r Load data model 2}
+load(here("Identical_r0","Generate_Big_Data","Model_2","No_Correlated_Covariate.RData"))
+Model_2_SS<-r0
+
+remove(Simulated_Data,Model_2,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M2_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="MSE",All_MSE))
+M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M2_Identical_r0$Subsample_Size<-M2_Identical_r0$Subsample_Size-Model_2_SS
 ```
@@
 ```{r Load data model 3}
+load(here("Identical_r0","Generate_Big_Data","Model_3","No_Correlated_Covariate.RData"))
+Model_3_SS<-r0
+
+remove(Simulated_Data,Model_3,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M3_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="MSE",All_MSE))
+M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M3_Identical_r0$Subsample_Size<-M3_Identical_r0$Subsample_Size-Model_3_SS
 ```
@@
 ```{r Load data model 4}
+load(here("Identical_r0","Generate_Big_Data","Model_4","No_Correlated_Covariate.RData"))
+Model_4_SS<-r0
+
+remove(Simulated_Data,Model_4,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M4_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",All_MSE))
+M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M4_Identical_r0$Subsample_Size<-M4_Identical_r0$Subsample_Size-Model_4_SS
 ```
@@
 Identical_ro$Covariate<-factor(Identical_ro$Covariate,
-                               levels = c("X1, X2","X1, X2, X1\u00B2",
-                                          "X1, X2, X2\u00B2","X1, X2, X1\u00B2, X2\u00B2"))
+                               levels = c("Data Model: X1, X2",
+                                          "Data Model: X1, X2, X1\u00B2",
+                                          "Data Model: X1, X2, X2\u00B2",
+                                          "Data Model: X1, X2, X1\u00B2, X2\u00B2"))
 
@@
                                       "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                                      "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
+                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
                                       "mMSE MR","mVc MR"))
 
-Selected_Models_mMSE<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
-                        "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                        "mMSE MR")
+Identical_ro$Model<-recode_factor(Identical_ro$Model,
+                                  `RS DM`="Random Sampling: Data Model",
+                                  `RS AM 1`="Random Sampling: Incorrect Model 1",
+                                  `RS AM 2`="Random Sampling: Incorrect Model 2",
+                                  `RS AM 3`="Random Sampling: Incorrect Model 3",
+                                  `mMSE DM`="Optimal Sub-sampling mMSE: Data Model",
+                                  `mMSE AM 1`="Optimal Sub-sampling mMSE: Incorrect Model 1",
+                                  `mMSE AM 2`="Optimal Sub-sampling mMSE: Incorrect Model 2",
+                                  `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
+                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model 1",
+                                  `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
+                                  `mVc AM 2`="Optimal Sub-sampling mVc: Incorrect Model 2",
+                                  `mVc AM 3`="Optimal Sub-sampling mVc: Incorrect Model 3",
+                                  `mMSE MR`="Model Robust Optimal Sub-sampling mMSE: Data Model",
+                                  `mVc MR`="Model Robust Optimal Sub-sampling mVc: Data Model")
+
+Selected_Models_mMSE<-c("Random Sampling: Data Model",
+                        #"Random Sampling: Incorrect Model 1",
+                        #"Random Sampling: Incorrect Model 2",
+                        #"Random Sampling: Incorrect Model 3",
+                        "Optimal Sub-sampling mMSE: Data Model",
+                        "Optimal Sub-sampling mMSE: Incorrect Model 1",
+                        "Optimal Sub-sampling mMSE: Incorrect Model 2",
+                        "Optimal Sub-sampling mMSE: Incorrect Model 3",
+                        "Model Robust Optimal Sub-sampling mMSE: Data Model")
 
@@
 
-Selected_Models_mVc<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
-                       "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
-                       "mVc MR")
+Selected_Models_mVc<-c("Random Sampling: Data Model",
+                       #"Random Sampling: Incorrect Model 1",
+                       #"Random Sampling: Incorrect Model 2",
+                       #"Random Sampling: Incorrect Model 3",
+                       "Optimal Sub-sampling mVc: Data Model 1",
+                       "Optimal Sub-sampling mVc: Incorrect Model 1",
+                       "Optimal Sub-sampling mVc: Incorrect Model 2",
+                       "Optimal Sub-sampling mVc: Incorrect Model 3",
+                       "Model Robust Optimal Sub-sampling mVc: Data Model")
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mMSE
+
+Temp_legend_mMSE<-get_legend(Temp_plot_mMSE)
+
+Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mVc
+
+Temp_legend_mVc<-get_legend(Temp_plot_mVc)
+
+Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p1
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
+
+Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p2
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p2
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("SMSE")+expand_limits(y = 0)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("SMSE")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p3
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p3
 
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p4
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p4
 
-ggarrange(p1,p3,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
-ggarrange(p2,p4,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
 ```

### 2022-04-09 Articles.Rmd
SMSE and model information stored as pdfs

@@
 ```
+
+# Using Uniform Distribution for Data
 
@@
 
-M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2",Metric="Model Information",
+M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                         All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2",Metric="MSE",
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                         All_MSE))
@@
 
-M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="Model Information",
+M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                         All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="MSE",
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                         All_MSE))
@@
 
-M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="Model Information",
+M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                         All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="MSE",
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                         All_MSE))
@@
 
-M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",
-                                        All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",
-                                        All_MSE))
+M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="Model Information",All_Info),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="MSE",All_MSE))
 
@@
 
-```{r combine data and plot,fig.width = 18,fig.height = 10}
+```{r combine data and plot,fig.width = 8,fig.height = 12}
 Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
@@
 Identical_ro$Covariate<-factor(Identical_ro$Covariate,
-                               levels = c("Data Model: X1, X2",
-                                          "Data Model: X1, X2, X1\u00B2",
-                                          "Data Model: X1, X2, X2\u00B2",
-                                          "Data Model: X1, X2, X1\u00B2, X2\u00B2"))
+                               levels = c("Data Model: x\u2081, x\u2082",
+                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",
+                                          "Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",
+                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"))
 
@@
 Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
-               "#FFC4D8", "#E28490","#BB2C3E","#55141C",
+               "#FFC4D8","#E28490","#BB2C3E","#55141C",
                "#DDCC77")
@@
 
+#Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]
+
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
@@
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
   xlab(expression(paste(r[0],' = 100 and r')))+
@@
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
   xlab(expression(paste(r[0],' = 100 and r')))+
@@
 
-ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
-ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
+
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
+  ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
+  ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
 ```

### 2022-06-02 Articles.Rmd
update the colors of the plots

@@
                                   `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
-                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model 1",
+                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model",
                                   `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
@@
 
-Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
-               "#FFC4D8","#E28490","#BB2C3E","#55141C",
-               "#DDCC77")
+# Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
+#                "#FFC4D8","#E28490","#BB2C3E","#55141C",
+#                "#DDCC77")
+
+Colors_mMSE<-c("black",#"grey","grey","grey",
+              "#cc0000", 
+              "#ff578a","#ff578a","#ff578a",
+              "darkgreen")
 
@@
                        #"Random Sampling: Incorrect Model 3",
-                       "Optimal Sub-sampling mVc: Data Model 1",
+                       "Optimal Sub-sampling mVc: Data Model",
                        "Optimal Sub-sampling mVc: Incorrect Model 1",
@@
 
-Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
-                          "#FFC4D8","#E28490","#BB2C3E","#55141C", 
-                          "#DDCC77")
+# Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
+#                           "#FFC4D8","#E28490","#BB2C3E","#55141C", 
+#                           "#DDCC77")
+
+Colors_mVc<-c("black",#"grey","grey","grey",
+              "#cc0000", 
+              "#ff578a","#ff578a","#ff578a",
+              "darkgreen")
 

### 2022-06-24 Manual.Rmd
Add manual with diagrams

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for Poisson Regression (Uniform Distribution)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Overview

* The project ***"Uniform_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Uniform"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the Poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.

* This document aims to state every important part of this R project thoroughly in terms of folder structure related to used sub-sampling methods.

# 2. Folder structure

![](Images/FullDiagram.png)

* The sub-sampling methods applied in this study are 
1. Random Sampling, 
2. Rare event random sampling, 
3. Optimal Sub-sampling (OSMAC), and
4. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).

* A detailed description of all methods are explained in the Figure below.

![](Images/All Methods Figure.png)

* Simulations are repeated ***Replicates*** times such that at each replicate only ***Subsample_Size*** data points are extracted from the Big Data set of ***N*** observations. It is necessary to have replications so that we can evaluate the methods through MSE and model information of the estimated model parameters.

* The results from this simulation setup are stored in a such way that they could be summarised through Rmarkdown files for individual or grouped assessment for the above mentioned methods.

* In optimal sub-sampling and model robust optimal sub-sampling an initial sub-sample of **r0** observations are used to estimate the model parameters of a given model. From these parameters only the sub-sampling probabilities are calculated. Therefore, to compare optimal sub-sampling with model robust optimal sub-sampling there are two options; 1). Identical **r0** and 2). Non-Identical **r0**.

* Hence, **Identical_r0** can be used for method comparison and **Non_Identical_r0** can be used for application purposes.

## 2.1 Generated_Big_Data

![](Images/Generate_Big_Data.png)

* Generate and store Big Data.

* Based on the real model of the Poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Uniform_Special.R***.

* To ensure that the data generated from the true model performs better than the assumed models run ***Check_Data.Rmd*** and look at the plots stored as **Model_[1 or 2 or 3 or 4]_X[1 or 2]**.

* In the Rscript, ***Replicates*** - number of unique simulations, ***Subsample_Size*** - target sample size, ***N*** - Big data size, ***Theta*** - Real model parameters, ***r0*** - initial sample size for optimal and model robust optimal sub-sampling.

* As of now the model parameters and their respective response compositions are 
1. $\theta=[-1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
2. $\theta=[-1.0, 0.5, 0.5, 0.7]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
3. $\theta=[-1.0, 0.5, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
4. $\theta=[-1.0, 0.5, 0.5, 0.5, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.

* For each model structure covariate data was generated only through a Uniform distribution.

## 2.2 Simulation_Setup

![](Images/Simulation_Setup.png)

* Contains the simulation setup for the above mentioned subsampling methods based on the variety of Big data sets and Rscripts to smoothly transfer methods and respective data based on real models.

### 2.2.1 Classical/R_Scripts

We need to transfer two forms of data,
1. Big Data set and other information essential for the methods.
2. Functions for the sub-sampling methods.

* Here we develop the functions and transfer them safely to the simulation setup.

#### 2.2.1.1 Setup_Data.R

* Data stored in **Generate_Big_Data** is transferred to **Classical/Analysis**.

#### 2.2.1.2 Random_Sampling_Setup.R

* A setup for random sampling such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.3 RE Random_Sampling_Setup.R

* A setup for rare event random sampling such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]

* The optimal sub-sampling, model robust optimal sub-sampling and a setup to apply these methods such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]

* The optimal sub-sampling and a setup to apply these methods such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.6 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]

* The model robust optimal sub-sampling and a setup to apply these methods such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

## 2.2.2 Classical/Analysis

Each model related covariate data is separately used on each subsampling method individually.

#### 2.2.2.1 Random Sampling

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_RandomSample.RData** - Random sampling function for **Replicates**.
* **Simulation_Results_Random_Sampling.R** - R script to run the random sampling method over **Replicates** on the **Init.RData** from **Run_RandomSample.RData**.
* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **Random_Sample_output.RData** is stored.

#### 2.2.2.2 RE Random Sampling

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **RE_RandomSample.RData** - RE Random sampling function for **Replicates**.
* **Simulation_Results_RE_Random_Sampling.R** - R script to run the rare event random sampling method over **Replicates** on the **Init.RData** from **RE_RandomSample.RData**.
* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **RE_Random_Sample_output.RData** is stored.

#### 2.2.2.3 OSMAC [Non Identical r0]

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_OSMAC.RData** - Optimal sampling function for **Replicates**.
* **Simulation_Results_OSMAC_Sampling.R** - R script to run the optimal sampling method over **Replicates** on the **Init.RData** from **Run_OSMAC.RData**.
* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **OSMAC_output.RData** is stored.

#### 2.2.2.4 OSMAC Model Free [Non Identical r0]

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_OSMAC.RData** - model robust optimal sampling function for **Replicates**.
* **Simulation_Results_OSMAC_Sampling.R** - R script to run the model robust optimal sampling method over **Replicates** on the **Init.RData** from **Run_OSMAC.RData**.
* **Results** - Results of the simulation are stored here as a single Rdata file **OSMAC_MF_output.RData**.

#### 2.2.2.5 OSMAC [Identical r0]

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_OSMAC.RData** - optimal sampling and model robust optimal sampling function for **Replicates**.
* **Simulation_Results_OSMAC_Sampling.R** - R script to run the optimal sampling and model robust optimal sampling methods over **Replicates** on the **Init.RData** from **Run_OSMAC.RData**.
* **Results** - Results of the simulation are stored here according to real models, assumed models and model robust (free) methods in each folder as Rdata files **OSMAC_output.RData**.

## 2.3 Outputs

* While in the **Simulation_Setup** results are stored for analysis purposes, the same results are stored here.

![](Images/Outputs.png)

## 2.4 Rmarkdown

![](Images/Rmarkdown.png)

* Rmarkdown files are used to individually assess the sub-sampling methods through plots for estimated model parameters, variance and bias.

* **RE_and_Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.

* **OSMAC_Command.R** - R script to summarise the results from the optimal sub-sampling and model robust optimal sampling methods through the Rmarkdown file **OSMAC_Method.Rmd**.

* **Summary_Rmarkdown.R** in the **Rmarkdown/Classical/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.

## 2.5 htmloutputs

![](Images/htmloutputs.png)

* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.

## 2.6 Summary

![](Images/Summary.png)

* Here, summaries from the Rmarkdown files **Best_Subsampling_Method.Rmd** are stored as html files.

### 2.6.1 Summary/Classical/Model_[1 or 2 or 3 or 4]/Data/Efficiency

* When running the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.

* Using these data files only summarising through the files in **Rmarkdown/Classical/Summary** occurs.

## 2.7 Articles.Rmd, Publication.Rmd and Publication_Ready_Command.R

* Use **Publication_Ready_command.R** to run **Publication.Rmd** on every model and its respective big data.

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_PR_TV_Uni_mMSE.pdf** and **SMSE_MI_PR_TV_Uni_mVc.pdf**.

### 2022-06-24 Manual.Rmd
Updated manual with diagram and title

@@
 ---
-title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for Poisson Regression (Uniform Distribution)"
+title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (uniform distribution)"
 output: github_document
@@
 
-* The project ***"Uniform_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Uniform"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the Poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.
+* The project ***"Uniform_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Uniform"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.
 
@@
 
-* Based on the real model of the Poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Uniform_Special.R***.
+* Based on the real model of the poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Uniform_Special.R***.
 
@@
 * As of now the model parameters and their respective response compositions are 
-1. $\theta=[-1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
-2. $\theta=[-1.0, 0.5, 0.5, 0.7]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
-3. $\theta=[-1.0, 0.5, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
-4. $\theta=[-1.0, 0.5, 0.5, 0.5, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.
+1. $\theta=[1.0, 0.3, 0.3]$ generates data for Model 1 of $x_1,x_2$.
+2. $\theta=[1.0, 0.7,-0.5, 0.4]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
+3. $\theta=[1.0,-0.4, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
+4. $\theta=[1.0, 0.5, 0.5,-0.3, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.
 
-* For each model structure covariate data was generated only through a Uniform distribution.
+* For each model structure covariate data was generated only through a uniform distribution.
 

### 2022-06-25 Manual.Rmd
clarification on OSMAC output

@@
 
+* In **Identical_r0** for OSMAC Assumed Models there are two forms of outputs, 1) **OSMAC_output_New_x.Rdata** is when optimal sub-sampling probabilities are selected from the re-calculated probabilities of the Data Generating model, 2) **OSMAC_output_Old_x.Rdata** is when optimal sub-sampling probabilities are calculated based on the Assumed model.
+Throughout the simulation setup the later output is used.
+
 ![](Images/Outputs.png)

### 2022-06-27 Manual.Rmd
updated manual with brief diagram in readme file

@@
 title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (uniform distribution)"
-output: github_document
+output: 
+  html_document:
+      keep_md: yes
 ---

### 2022-06-28 Identical_r0/Simulation_Setup/Classical/R_Scripts/Setup_Data.R
updated data and model_paths

@@ -1,9 +1,9 @@
 library(here)
 
-#Model_Path<-"Model_1"
+Model_Path<-"Model_1"
 #Model_Path<-"Model_2"
 #Model_Path<-"Model_3"
-Model_Path<-"Model_4"
+#Model_Path<-"Model_4"
 
 # OSMAC Data ----
 Base_Path<-"OSMAC"

### 2022-06-28 Non_Identical_r0/Rmarkdown/Classical/Random_Sampling_And_OSMAC.R

@@ -5,30 +5,30 @@ library(rmarkdown)
 Model<-c("Model_1","Model_2",
          "Model_3","Model_4") ; j=4
 
-# Random Sampling ----
-ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Random_Sampling.Rmd"),
-       out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"Random_Sampling"),
-       fig_dir = c("Plots"),
-       params=list("Model_Path"=Model[j]),
-       verbose = TRUE,keep_md = FALSE)
-open_output_dir()
-
 for (j in 1:length(Model)) 
 {
-        # OSMAC Method ----
-        ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
-               out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
-               fig_dir = c("Plots"),
-               params=list("Model_Path"=Model[j]),
-               verbose = TRUE,keep_md = FALSE)
-        #open_output_dir()
-        
-        # OSMAC Model Free Method ----
-        ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Model_Free_Method.Rmd"),
-               out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC_Model_Free"),
-               fig_dir = c("Plots"),
-               params=list("Model_Path"=Model[j]),
-               verbose = TRUE,keep_md = FALSE)
-        #open_output_dir()
+  # Random Sampling ----
+  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Random_Sampling.Rmd"),
+         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"Random_Sampling"),
+         fig_dir = c("Plots"),
+         params=list("Model_Path"=Model[j]),
+         verbose = TRUE,keep_md = FALSE)
+  #open_output_dir()
+  
+  # OSMAC Method ----
+  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
+         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
+         fig_dir = c("Plots"),
+         params=list("Model_Path"=Model[j]),
[…]

### 2022-06-28 Non_Identical_r0/Simulation_Setup/Classical/R_Scripts/Setup_Data.R

@@ -1,9 +1,9 @@
 library(here)
 
-#Model_Path<-"Model_1"
+Model_Path<-"Model_1"
 #Model_Path<-"Model_2"
 #Model_Path<-"Model_3"
-Model_Path<-"Model_4"
+#Model_Path<-"Model_4"
 
 # Random Sampling Data ----
 Base_Path<-"Random_Sampling"

### 2022-09-27 Articles.Rmd
Additional Average MSE Y for the existing Results are calculated

@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
 }
@@
 RS_MSE<-All_MSE
+RS_ACC<-Accuracy_Data
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
+All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]
 
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
 }
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
 }
@@
 OSMAC_MSE<-All_MSE
+OSMAC_ACC<-All_ACC
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
 All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
+All_ACC<-rbind(RS_ACC,OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])
 
@@
 colnames(All_MSE)[3]<-"Estimated Values"
+colnames(All_ACC)[3]<-"Estimated Values"
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
-                                        All_MSE))
+                                        All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
+                                        All_ACC))
 
-remove(All_Info,All_MSE,RS_Info,RS_MSE)
+remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)
 
@@
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
+Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]
 
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
 }
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
 }
@@
 OSMAC_MSE<-All_MSE
+OSMAC_ACC<-Accuracy_Data
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
-                                        All_MSE))
+                                        All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
+                                        All_ACC))
 
-remove(All_Info,All_MSE,RS_Info,RS_MSE)
+remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)
 
@@
 OSMAC_MSE<-All_MSE
+OSMAC_ACC<-All_ACC
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,All_ACC)
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
-                                        All_MSE))
+                                        All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
+                                        All_ACC))
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
-                                        Metric="MSE",All_MSE))
+                                        Metric="MSE",All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="Average MSE Y",All_ACC))
 
-remove(All_Info,All_MSE,RS_Info,RS_MSE)
+remove(All_Info,All_MSE,RS_Info,RS_MSE,RS_ACC)
 
@@
 
-Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
-
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
@@
 
+Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Average MSE Y")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p5
+
+Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Average MSE Y")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p6
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
+ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
+ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
 
@@
   ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
+ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_LR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_LR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
 ```

### 2022-09-27 Non_Identical_r0/Rmarkdown/Classical/OSMAC_Method.Rmd
Additional Average MSE Y for the existing Results are calculated

@@
 
-remove(Temp_P,Temp_W,Temp_Info)
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+Parameter_Data<-as.matrix(Est_Parameter[,-c(1:3)])
+Parameter<-Parameter_Data[1,]
+
+Predict_Poisson_Regression<-function(Parameter)
+{
+  Estimates<-matrix(Parameter)
+  fitted_lambda<-exp(Full_Data[,-1]%*%Estimates)
+  return((mean(fitted_lambda - Full_Data[,1]))^2)
+}
+
+Accuracy<-apply(Parameter_Data,1,Predict_Poisson_Regression)
+
+Accuracy_Data<-cbind.data.frame(Est_Parameter[,1:3],Accuracy)
+Accuracy_Data<-Accuracy_Data %>% 
+  group_by(Model,Type,Subsample_Size) %>%
+  summarize(Average_Accuracy=mean(Accuracy))
+
+remove(Temp_P,Temp_W,Temp_Info,Full_Data,Parameter_Data,Parameter,Accuracy)
 
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
+save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
      file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
@@
 
-ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)
+Accuracy_Data %>% 
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 2)+
+  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+
+ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
 ```
@@
 
-ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+Parameter_Data<-as.matrix(Est_Parameter[,-c(1:3)])
+Parameter<-Parameter_Data[1,]
+
+fitted_lambda<-as.vector(predict.glm(Full_model,newdata = as.data.frame(Simulated_Data$All_Data$Real_Model[,-1])))
+Full_Accuracy<-(mean(fitted_lambda - Simulated_Data$All_Data$Real_Model[,1]))^2
+
+Accuracy_Data %>% 
+  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
+  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 2)+
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+
+ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
 ```

### 2022-09-27 Non_Identical_r0/Rmarkdown/Classical/Random_Sampling.Rmd
Additional Average MSE Y for the existing Results are calculated

@@
 
-remove(Temp_P,Temp_W,Temp_Info)
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+Parameter_Data<-as.matrix(Est_Parameter[,-c(1:2)])
+Parameter<-Parameter_Data[1,]
+
+Predict_Poisson_Regression<-function(Parameter)
+{
+  Estimates<-matrix(Parameter)
+  fitted_lambda<-exp(Full_Data[,-1]%*%Estimates)
+  return((mean(fitted_lambda - Full_Data[,1]))^2)
+}
+
+Accuracy<-apply(Parameter_Data,1,Predict_Poisson_Regression)
+
+Accuracy_Data<-cbind.data.frame(Est_Parameter[,1:2],Accuracy)
+Accuracy_Data<-Accuracy_Data %>% 
+  group_by(Model,Subsample_Size) %>%
+  summarize(Average_Accuracy=mean(Accuracy))
+
+remove(Temp_P,Temp_W,Temp_Info,Full_Data,Parameter_Data,Parameter,Accuracy)
 
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
+save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
      file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
@@
 
-ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)
+Accuracy_Data %>%
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+
+ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
 
@@
 
-ggarrange(plotlist = Plot_list,nrow = 5,ncol = 1,common.legend = TRUE)
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+Parameter_Data<-as.matrix(Est_Parameter[,-c(1:3)])
+Parameter<-Parameter_Data[1,]
+
+fitted_lambda<-as.vector(predict.glm(Full_model,newdata = as.data.frame(Simulated_Data$All_Data$Real_Model[,-1])))
+Full_Accuracy<-(mean(fitted_lambda - Simulated_Data$All_Data$Real_Model[,1]))^2
+
+Accuracy_Data %>%
+  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
+  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+
+ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
 ```

### 2022-09-27 Non_Identical_r0/Rmarkdown/Classical/Summary/Best_Subsampling_Method.Rmd
Additional Average MSE Y for the existing Results are calculated

@@
   All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
 }
@@
 RS_VAR<-All_VAR
+RS_ACC<-Accuracy_Data
 
@@
   All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
 }
@@
 OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
+OSMAC_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]
 
@@
   All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
 }
@@
 OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
+OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
           "No_Correlated_Covariate_OSMAC_MF.RData"))
+
+Accuracy_Data<-cbind(Accuracy_Data[,1],Model="Real Model",Accuracy_Data[,-1])
 
@@
 All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]
+Accuracy_Data<-Accuracy_Data[Accuracy_Data$Model==Old_Labels[1],]
 
@@
 All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
+Accuracy_Data$Model[Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
 
@@
 OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
+OSMAC_MF_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]
 
@@
 All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")
+Accuracy_Data$Model[Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc MF")
 
@@
 OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
+OSMAC_MF_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
                 OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
+All_ACC<-rbind(RS_ACC,RE_RS_ACC,
+                OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
+                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
+                OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")],
+                OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])
 
@@
                        OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")])
+SP_All_mMSE_ACC<-rbind(OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
+                       OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")])
 
@@
                        OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
+SP_All_mVc_ACC<-rbind(OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
+                       OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])
 
@@
 
-ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE,nrow = 2,ncol = 3)
+All_ACC %>%
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
+
+ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
 ```
@@
 
-ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE,nrow = 2,ncol = 3)
+SP_All_mMSE_ACC %>%
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
+
+ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
 ```
@@
 
-ggarrange(p1,p2,p3,p4,p5,common.legend = TRUE,nrow = 2,ncol = 3)
+SP_All_mVc_ACC %>%
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
+
+ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
 ```

### 2022-09-27 Publication_Ready.Rmd
Additional Average MSE Y for the existing Results are calculated

@@
 
-# Using Uniform Distribution for Data
+# Using Normal Distribution for Data
 
@@
 RS_VAR<-All_VAR
+RS_ACC<-Accuracy_Data
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
 All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]
+Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]
 
@@
                 OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])
+All_ACC<-rbind(RS_ACC,
+                OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
+                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")])
 
@@
 colnames(All_VAR)[3]<-"Estimated Values"
+colnames(All_ACC)[3]<-"Estimated Values"
 
@@
                                cbind.data.frame(Metric="MSE",All_MSE),
-                               cbind.data.frame(Metric="Variance",All_VAR))
+                               cbind.data.frame(Metric="Variance",All_VAR),
+                               cbind.data.frame(Metric="Accuracy",All_ACC))
 
-remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR)
+remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR,All_ACC)
 ```
@@
 OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
+OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]
 
@@
           "No_Correlated_Covariate_OSMAC_MF.RData"))
+
+Accuracy_Data<-cbind(Model="Real Model",Accuracy_Data)
 
@@
                OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
+All_ACC<-rbind(RS_ACC,
+               OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
+               OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
+               OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")],
+               OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])
 
@@
                                              "OSMAC mMSE MF","OSMAC mVc MF"))
+All_ACC$Model<-factor(All_ACC$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
+                                             "OSMAC mMSE RM","OSMAC mVc RM",
+                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
+                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
+                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
+                                             "OSMAC mMSE MF","OSMAC mVc MF"))
 
@@
                                    cbind.data.frame(Metric="MSE",All_MSE),
-                                   cbind.data.frame(Metric="Variance",All_VAR))
+                                   cbind.data.frame(Metric="Variance",All_VAR),
+                                   cbind.data.frame(Metric="MSE Y",All_ACC))
 
@@
 
+Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y"),] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
+  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p5
+
+Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y"),] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
+  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p6
+
 ggarrange(p1,p2,p3,p4,nrow = 4)
+ggarrange(p5,p6,nrow = 2)
 ```
@@
   ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p1_New
+  ylab("Estimated Values")+facet_wrap(~Data)->p1_New
 
@@
   ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p2_New
+  ylab("Estimated Values")+facet_wrap(~Data)->p2_New
 
@@
   ylab("Estimated Values")+facet_wrap(~Data)->p4_New
+
+Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y") & 
+             Final_Data$Subsample_Size %in% SS_Choice,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
+  ylab("Estimated Values")+facet_wrap(~Data)->p5_New
+
+Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y") & 
+             Final_Data$Subsample_Size %in% SS_Choice,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
+  ylab("Estimated Values")+facet_wrap(~Data)->p6_New
 ```
@@
           p2,p2_New,nrow = 4)
+
+ggarrange(p5_New,p6_New,nrow = 2)
 ```

### 2022-09-27 Identical_r0/Rmarkdown/Classical/Summary/Summary_Rmarkdown.R

@@ -13,6 +13,6 @@ ezknit(file=here("Identical_r0","Rmarkdown","Classical","Summary","Best_Subsampl
         fig_dir = c("Plots"),
         params=list("Model_Path"=Model[i]),
         verbose = TRUE,keep_md = FALSE)
-open_output_dir()
+#open_output_dir()
 }
 

### 2022-09-27 Non_Identical_r0/Rmarkdown/Classical/Summary/Summary_Rmarkdown.R

@@ -13,6 +13,6 @@ for (i in 1:length(Model))
          fig_dir = c("Plots"),
          params=list("Model_Path"=Model[i]),
          verbose = TRUE,keep_md = FALSE)
-  open_output_dir()
+  #open_output_dir()
 }
 

### 2022-09-27 Publication_Ready_command.R

@@ -13,5 +13,5 @@ for(i in 1:length(Model))
          fig_dir = c("Plots"),
          params=list("Model_Path"=Model[i]),
          verbose = TRUE,keep_md = TRUE,keep_html = FALSE)
-  open_output_dir()
+  #open_output_dir()
 }

### 2022-09-27 Articles.Rmd
Change pdf output names and delete previous outputs

@@
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_LR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_LR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
 ```

### 2022-10-03 Articles.Rmd
plots are updated for visibility

@@
 
+Theme_special<-function()
+{
+  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
+        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
+        strip.text = element_text(colour = "black",size = 12,face="bold"),
+        panel.grid.minor.x = element_blank(),
+        axis.title= element_text(color = "black",face = "bold",size = 12),
+        legend.text = element_text(color = "black", size=11),
+        legend.position = "bottom",
+        legend.margin=margin(0,0,0,0),
+        legend.box.margin=margin(-1,-2,-1,-2)) 
+}
+
 #Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mMSE
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mVc
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
+  theme_bw()+Theme_special()->p1
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p2
+  theme_bw()+Theme_special()->p2
 
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p3
+  theme_bw()+Theme_special()->p3
 
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p4
+  theme_bw()+Theme_special()->p4
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Average MSE Y")+expand_limits(y = 0)+
+  ylab("Average MSE of Y")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p5
+  theme_bw()+Theme_special()->p5
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Average MSE Y")+expand_limits(y = 0)+
+  ylab("Average MSE of Y")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p6
+  theme_bw()+Theme_special()->p6
 

### 2022-10-03 Articles.Rmd
x axis title updated to r

@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("SMSE")+expand_limits(y = 0)+
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("Average MSE of Y")+expand_limits(y = 0)+

### 2022-10-11 Articles.Rmd
y axis scaled to log and log10

@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("Average Model Information")+expand_limits(y = 0)+
+  ylab("log10(Average Model Information)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("SMSE")+expand_limits(y = 0)+
+  ylab("log(SMSE)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("Average MSE of Y")+expand_limits(y = 0)+
+  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),

### 2022-10-13 Articles.Rmd
log10 to log scale

@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("log10(Average Model Information)")+#expand_limits(y = 0)+
+  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),

### 2022-11-05 Articles.Rmd
eps files saved for plots

@@
 
+# ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
+#   ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
+# ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
+#   ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
+# ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+#   ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+# ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+#   ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
+  ggsave(filename = "SMSE_MI_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-  ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
+  ggsave(filename = "SMSE_MI_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+  ggsave(filename = "ACCURACY_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+  ggsave(filename = "ACCURACY_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
 ```

### 2022-12-15 Articles.Rmd
update labels subsampling

@@
 
-remove(Simulated_Data,Model_1,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
 
-remove(Simulated_Data,Model_2,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
 
-remove(Simulated_Data,Model_3,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
 
-remove(Simulated_Data,Model_4,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
                                   `RS AM 3`="Random Sampling: Incorrect Model 3",
-                                  `mMSE DM`="Optimal Sub-sampling mMSE: Data Model",
-                                  `mMSE AM 1`="Optimal Sub-sampling mMSE: Incorrect Model 1",
-                                  `mMSE AM 2`="Optimal Sub-sampling mMSE: Incorrect Model 2",
-                                  `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
-                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model",
-                                  `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
-                                  `mVc AM 2`="Optimal Sub-sampling mVc: Incorrect Model 2",
-                                  `mVc AM 3`="Optimal Sub-sampling mVc: Incorrect Model 3",
-                                  `mMSE MR`="Model Robust Optimal Sub-sampling mMSE: Data Model",
-                                  `mVc MR`="Model Robust Optimal Sub-sampling mVc: Data Model")
+                                  `mMSE DM`="Optimal subsampling mMSE: Data Model",
+                                  `mMSE AM 1`="Optimal subsampling mMSE: Incorrect Model 1",
+                                  `mMSE AM 2`="Optimal subsampling mMSE: Incorrect Model 2",
+                                  `mMSE AM 3`="Optimal subsampling mMSE: Incorrect Model 3",
+                                  `mVc DM`="Optimal subsampling mVc: Data Model",
+                                  `mVc AM 1`="Optimal subsampling mVc: Incorrect Model 1",
+                                  `mVc AM 2`="Optimal subsampling mVc: Incorrect Model 2",
+                                  `mVc AM 3`="Optimal subsampling mVc: Incorrect Model 3",
+                                  `mMSE MR`="Model Robust subsampling mMSE: Data Model",
+                                  `mVc MR`="Model Robust subsampling mVc: Data Model")
 
@@
                         #"Random Sampling: Incorrect Model 3",
-                        "Optimal Sub-sampling mMSE: Data Model",
-                        "Optimal Sub-sampling mMSE: Incorrect Model 1",
-                        "Optimal Sub-sampling mMSE: Incorrect Model 2",
-                        "Optimal Sub-sampling mMSE: Incorrect Model 3",
-                        "Model Robust Optimal Sub-sampling mMSE: Data Model")
+                        "Optimal subsampling mMSE: Data Model",
+                        "Optimal subsampling mMSE: Incorrect Model 1",
+                        "Optimal subsampling mMSE: Incorrect Model 2",
+                        "Optimal subsampling mMSE: Incorrect Model 3",
+                        "Model Robust subsampling mMSE: Data Model")
 
@@
                        #"Random Sampling: Incorrect Model 3",
-                       "Optimal Sub-sampling mVc: Data Model",
-                       "Optimal Sub-sampling mVc: Incorrect Model 1",
-                       "Optimal Sub-sampling mVc: Incorrect Model 2",
-                       "Optimal Sub-sampling mVc: Incorrect Model 3",
-                       "Model Robust Optimal Sub-sampling mVc: Data Model")
+                       "Optimal subsampling mVc: Data Model",
+                       "Optimal subsampling mVc: Incorrect Model 1",
+                       "Optimal subsampling mVc: Incorrect Model 2",
+                       "Optimal subsampling mVc: Incorrect Model 3",
+                       "Model Robust subsampling mVc: Data Model")
 

### 2022-12-15 Articles.Rmd
updated pdf plots

@@
 
-# ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-#   ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
-# ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-#   ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
-# ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-#   ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
-# ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-#   ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
+  ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
+  ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
+ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
 

### 2023-02-11 Identical_r0/Rmarkdown/OSMAC_Method.Rmd
files renamed after deleting classical folder from the chain

--- 2022-01-17 Identical_r0/Rmarkdown/Classical/OSMAC_Method.Rmd
@@
 
-remove(Temp_P,Temp_W,Temp_Info)
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+Parameter_Data<-as.matrix(Est_Parameter[,-c(1:3)])
+Parameter<-Parameter_Data[1,]
+
+Predict_Poisson_Regression<-function(Parameter)
+{
+  Estimates<-matrix(Parameter)
+  fitted_lambda<-exp(Full_Data[,-1]%*%Estimates)
+  return((mean(fitted_lambda-Full_Data[,1]))^2)
+}
+
+Accuracy<-apply(Parameter_Data,1,Predict_Poisson_Regression)
+Accuracy_Data<-cbind.data.frame(Est_Parameter[,1:3],Accuracy)
+Accuracy_Data<-Accuracy_Data %>% 
+  group_by(Model,Type,Subsample_Size) %>%
+  summarize(Average_Accuracy=mean(Accuracy))
+
+remove(Temp_P,Temp_W,Temp_Info,Full_Data,Parameter_Data,Parameter,Accuracy)
 
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
+save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
      file = here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
@@
   ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_List[[5]]
+
+Accuracy_Data %>% 
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
+  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_List[[6]]
 
@@
 
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+Parameter_Data<-as.matrix(Est_Parameter[,-c(1:3)])
+Parameter<-Parameter_Data[1,]
+
+fitted_lambda<-as.vector(predict.glm(Full_model,newdata = as.data.frame(Simulated_Data$All_Data$Real_Model[,-1])))
+Full_Accuracy<-(mean(fitted_lambda-Simulated_Data$All_Data$Real_Model[,1]))^2
+
+Accuracy_Data %>% 
+  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
+  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_List[[6]]
+
 ggarrange(plotlist = Plot_List,common.legend = TRUE,nrow=1)

### 2023-02-11 Identical_r0/Rmarkdown/Summary/Best_Subsampling_Method.Rmd
files renamed after deleting classical folder from the chain

--- 2022-09-27 Non_Identical_r0/Rmarkdown/Classical/Summary/Best_Subsampling_Method.Rmd
@@
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
 # OSMAC
-load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+load(here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
           "No_Correlated_Covariate_OSMAC.RData"))
+remove_stuff<-c(paste0("Assumed New ",1:3))
+
+All_Bias<-All_Bias[!(All_Bias$Model %in% remove_stuff),]
+All_EMSE<-All_EMSE[!(All_EMSE$Model %in% remove_stuff),]
+All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
+All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]
+Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]
+
+Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
+New_Labels<-c("RM",paste0("AM ",1:3),"MF")
 
@@
 
-# OSMAC Model Free
-load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC_MF.RData"))
-
-Accuracy_Data<-cbind(Accuracy_Data[,1],Model="Real Model",Accuracy_Data[,-1])
-
-All_Bias<-All_Bias[All_Bias$Model==Old_Labels[1],]
-All_EMSE<-All_EMSE[All_EMSE$Model==Old_Labels[1],]
-All_Info<-All_Info[All_Info$Model==Old_Labels[1],]
-All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
-All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]
-Accuracy_Data<-Accuracy_Data[Accuracy_Data$Model==Old_Labels[1],]
-
-## mMSE
-All_Bias$Model[All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
-All_EMSE$Model[All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
-All_Info$Model[All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
-All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
-All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
-Accuracy_Data$Model[Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
-
-OSMAC_MF_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
-OSMAC_MF_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
-OSMAC_MF_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
-OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
-OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
-OSMAC_MF_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]
-
-## mVc
-All_Bias$Model[All_Bias$Type == "mVc"] <-paste0("OSMAC mVc MF")
-All_EMSE$Model[All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
-All_Info$Model[All_Info$Type == "mVc"] <-paste0("OSMAC mVc MF")
-All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
-All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")
-Accuracy_Data$Model[Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc MF")
-
-OSMAC_MF_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
-OSMAC_MF_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
-OSMAC_MF_mVc_Info<-All_Info[All_Info$Type == "mVc",]
-OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
-OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
-OSMAC_MF_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]
-
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
-
 # All elements
@@
                 OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
-                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
-                OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")],
-                OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
+                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")])
 All_EMSE<-rbind(RS_EMSE,
                 OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
-                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
-                OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")],
-                OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
+                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")])
 All_MSE<-rbind(RS_MSE,
                 OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
-                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
-                OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")],
-                OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
+                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
 All_Info<-rbind(RS_Info,
                 OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
-                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
-                OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")],
-                OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
+                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")])
 All_VAR<-rbind(RS_VAR,
                 OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
-                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
-                OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")],
-                OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
-All_ACC<-rbind(RS_ACC,RE_RS_ACC,
+                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])
+All_ACC<-rbind(RS_ACC,
                 OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
-                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
-                OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")],
-                OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])
-
-# Special mMSE elements
-SP_All_mMSE_Bias<-rbind(OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
-                        OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")])
-SP_All_mMSE_EMSE<-rbind(OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
-                        OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")])
-SP_All_mMSE_MSE<-rbind(OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
-                       OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")])
-SP_All_mMSE_Info<-rbind(OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
-                        OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")])
-SP_All_mMSE_VAR<-rbind(OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
-                       OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")])
-SP_All_mMSE_ACC<-rbind(OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
-                       OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")])
-
-# Special mVc elements
-SP_All_mVc_Bias<-rbind(OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
-                        OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
-SP_All_mVc_EMSE<-rbind(OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
-                        OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
-SP_All_mVc_MSE<-rbind(OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
-                       OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
-SP_All_mVc_Info<-rbind(OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
-                        OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
-SP_All_mVc_VAR<-rbind(OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
-                       OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
-SP_All_mVc_ACC<-rbind(OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
-                       OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])
+                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")])
 
 All_Objects<-ls()
-remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
 remove(list = All_Objects[startsWith(All_Objects,"RS")])
@@
 
-```{r Compare All,fig.width=20,fig.height=12}
-All_Bias %>% 
+```{r Compare All}
+All_Bias%>%
   ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
+  ylab("Average MSE y")+ggtitle("Average MSE y")->p6
 
-ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
+ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE)
 ```
 
-# Special Comparison of SMSE, EMSE, Variance, Information and Bias for mMSE.
+# Compare  SMSE, EMSE, Variance, Information and Bias for mMSE.
 ## (Real Model and Assumed Model results with Full Data Real Model)
 
-```{r Special Compare 1,fig.width=20,fig.height=12}
-SP_All_mMSE_Bias %>%
+```{r Compare 1}
+OSMAC_mMSE_Bias %>%
   ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
@@
 
-SP_All_mMSE_MSE %>%
+OSMAC_mMSE_MSE %>%
   ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
@@
 
-SP_All_mMSE_EMSE %>%
+OSMAC_mMSE_EMSE %>%
   ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
@@
 
-SP_All_mMSE_VAR %>%
+OSMAC_mMSE_VAR %>% 
   ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
@@
 
-SP_All_mMSE_Info %>%
+OSMAC_mMSE_Info %>%
   ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
@@
 
-SP_All_mMSE_ACC %>%
+OSMAC_mMSE_ACC %>%
   ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
+  ylab("Average MSE y")+ggtitle("Average MSE y")->p6
 
-ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
+ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE)
 ```
@@
 
-```{r Special Compare 2,fig.width=20,fig.height=12}
-SP_All_mVc_Bias %>%
+```{r Compare 2}
+OSMAC_mVc_Bias %>%
   ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
@@
 
-SP_All_mVc_MSE %>%
+OSMAC_mVc_MSE %>%
   ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
@@
 
-SP_All_mVc_EMSE %>%
+OSMAC_mVc_EMSE %>%
   ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
@@
 
-SP_All_mVc_VAR %>%
+OSMAC_mVc_VAR %>% 
   ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
@@
 
-SP_All_mVc_Info %>%
+OSMAC_mVc_Info %>%
   ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
@@
 
-SP_All_mVc_ACC %>%
+OSMAC_mVc_ACC %>%
   ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+

### 2023-02-11 Non_Identical_r0/Rmarkdown/OSMAC_Model_Free_Method.Rmd
files renamed after deleting classical folder from the chain

--- 2022-01-17 Non_Identical_r0/Rmarkdown/Classical/OSMAC_Model_Free_Method.Rmd
@@
 
-remove(Temp_P,Temp_W,Temp_Info)
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+Parameter_Data<-as.matrix(Est_Parameter_RM[,-c(1:2)])
+Parameter<-Parameter_Data[1,]
+
+Predict_Poisson_Regression<-function(Parameter)
+{
+  Estimates<-matrix(Parameter)
+  fitted_lambda<-exp(Full_Data[,-1]%*%Estimates)
+  return((mean(fitted_lambda - Full_Data[,1]))^2)
+}
+
+Accuracy<-apply(Parameter_Data,1,Predict_Poisson_Regression)
+
+Accuracy_Data<-cbind.data.frame(Est_Parameter_RM[,1:2],Accuracy)
+Accuracy_Data<-Accuracy_Data %>% 
+  group_by(Type,Subsample_Size) %>%
+  summarize(Average_Accuracy=mean(Accuracy))
+
+remove(Temp_P,Temp_W,Temp_Info,Full_Data,Parameter_Data,Parameter,Accuracy)
 
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,
+save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
      file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
@@
 
-ggarrange(plotlist = Plot_list,nrow = 1,ncol = 5,common.legend = TRUE)
+FullDataPath<-here("Non_Identical_r0","Generate_Big_Data",params$Model_Path,"No_Correlated_Covariate.RData")
+load(here(FullDataPath))
+
+Full_model<-glm(Y~.-1,data = as.data.frame(Simulated_Data[[2]]$Real_Model),family = poisson)
+Full_Data<-as.matrix(Simulated_Data$All_Data$Real_Model)
+
+fitted_lambda<-as.vector(predict.glm(Full_model,newdata = as.data.frame(Simulated_Data$All_Data$Real_Model[,-1])))
+Full_Accuracy<-(mean(fitted_lambda - Simulated_Data$All_Data$Real_Model[,1]))^2
+
+Accuracy_Data %>%
+  mutate(Relative_Accuracy=Average_Accuracy/Full_Accuracy) %>%
+  ggplot(.,aes(x=Subsample_Size,y=Relative_Accuracy))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+
+ggarrange(plotlist = Plot_list,nrow = 1,ncol = 6,common.legend = TRUE)
 

### 2023-02-12 Articles.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
   Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
@@
 RS_MSE<-All_MSE
+RS_MSE_MLE<-All_MSE_MLE
 RS_ACC<-Accuracy_Data
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
   All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
   All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
@@
 OSMAC_MSE<-All_MSE
+OSMAC_MSE_MLE<-All_MSE_MLE
 OSMAC_ACC<-All_ACC
@@
 All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
+All_MSE_MLE<-rbind(RS_MSE_MLE,OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
 All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
@@
 colnames(All_MSE)[3]<-"Estimated Values"
+colnames(All_MSE_MLE)[3]<-"Estimated Values"
 colnames(All_ACC)[3]<-"Estimated Values"
@@
                                         All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE for MLE",
+                                        All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
   Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
   Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
@@
 OSMAC_MSE<-All_MSE
+OSMAC_MSE_MLE<-All_MSE_MLE
 OSMAC_ACC<-Accuracy_Data
@@
 colnames(All_Info)[3]<-"Estimated Values"
+colnames(All_MSE_MLE)[3]<-"Estimated Values"
 colnames(All_MSE)[3]<-"Estimated Values"
@@
                                         All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE for MLE",
+                                        All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
                                         All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE for MLE",
+                                        All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
                                         Metric="MSE",All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="MSE for MLE",All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
@@
 
+Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab("r")+
+  ylab("log(SMSE)")+#expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+Theme_special()->p7
+
+Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab("r")+
+  ylab("log(SMSE)")+#expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+Theme_special()->p8
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
@@
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
+ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
+ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
 
@@
 
+ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
@@
   ggsave(filename = "ACCURACY_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
+
+ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mMSE.eps",res=300,width = 12,height = 12)
+ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mVc.eps",res=300,width = 12,height = 12)
 ```

### 2023-02-12 Identical_r0/Rmarkdown/OSMAC_Method.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

@@
 ---
+params:
+  Model_Path:
 title: "OSMAC_Method; Model: `r params$Model_Path`; "
@@
 ```{r Load Data}
-Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Real_Model/")
+Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
 load(here(Path,"OSMAC_output.RData"))
@@
 ```{r Load Data Assumed Models}
-Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model/")
+Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
 # Assumed Model 1
@@
 ```{r Load Data Assumed Models 2}
-Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model/")
+Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model/")
 # Assumed Model 1
@@
 ```{r Load Data Model Free}
-Path<-here("Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","ModelFree/")
+Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","ModelFree/")
 load(here(Path,"OSMAC_output.RData"))
@@
 anim_save(filename="para_1.gif",animation = para_1,
-          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","para_1.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","para_1.gif"))
 ```
@@
 anim_save(filename="Bias_1.gif",animation = Bias_1,
-          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
 ```
@@
 anim_save(filename="U_1.gif",animation = U_1,
-          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_1.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_1.gif"))
 
@@
 anim_save(filename="U_2.gif",animation = U_2,
-          path=here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_2.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_2.gif"))
 ```
@@
 
+  # Summarize SMSE MLE
+  Est_Parameter %>%
+        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
+        group_by(Type,Model,Subsample_Size) %>%
+        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                              Estimated_1=Theta0, 
+                              Estimated_2=Theta1,
+                              Estimated_3=Theta2,
+                              Model = params$Model_Path ))%>%
+        distinct(MSE) %>% 
+        forestmangr::round_df(8)->All_MSE_MLE
+
   # Summarise Bias
@@
         forestmangr::round_df(8)->All_MSE
+
+  # Summarize SMSE MLE
+  Est_Parameter %>%
+        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+        group_by(Type,Model,Subsample_Size) %>%
+        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                              Estimated_1=Theta0, 
+                              Estimated_2=Theta1,
+                              Estimated_3=Theta2,
+                              Estimated_4=Theta3,
+                              Model = params$Model_Path ))%>%
+        distinct(MSE) %>% 
+        forestmangr::round_df(8)->All_MSE_MLE
 
@@
         forestmangr::round_df(8)->All_MSE
+
+  # Summarize SMSE MLE
+  Est_Parameter %>%
+        dplyr::select(Type,Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
+        group_by(Type,Model,Subsample_Size) %>%
+        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                              Estimated_1=Theta0, 
+                              Estimated_2=Theta1,
+                              Estimated_3=Theta2,
+                              Estimated_4=Theta3,
+                              Estimated_5=Theta4,
+                              Model = params$Model_Path ))%>%
+        distinct(MSE) %>% 
+        forestmangr::round_df(8)->All_MSE_MLE
 
@@
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
-     file = here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
+     file = here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                  "No_Correlated_Covariate_OSMAC.RData"))
@@
 
+All_MSE_MLE %>%
+  #ungroup(Type,Model,Subsample_Size) %>%
+ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
+  ylab("SMSE")+ggtitle("SMSE Comparison for MLE")->Plot_List[[2]]
+
 All_VAR %>%
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_List[[2]]
+  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_List[[3]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_List[[3]]
+  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_List[[4]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_List[[4]]
+  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_List[[5]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_List[[5]]
+  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_List[[6]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_List[[6]]
+  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_List[[7]]
 
@@
 
+All_MSE_MLE %>%
+  ungroup(Type,Model,Subsample_Size) %>%
+  mutate(Efficiency=MSE/Full_SMSE) %>%
+ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
+  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency for MLE")->Plot_List[[2]]
+
 All_VAR %>%
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_List[[2]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_List[[3]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_List[[3]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_List[[4]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_List[[4]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_List[[5]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_List[[5]]
+  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_List[[6]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 1)+
-  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_List[[6]]
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_List[[7]]
 

### 2023-02-12 Identical_r0/Rmarkdown/Summary/Best_Subsampling_Method.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

@@
 ---
+params:
+  Model_Path:
 title: "Best Sub-sampling Method: `r params$Model_Path`"
@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
           "No_Correlated_Covariate_RS.RData"))
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
   All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
@@
 RS_MSE<-All_MSE
+RS_MSE_MLE<-All_MSE_MLE
 RS_VAR<-All_VAR
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+load(here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
           "No_Correlated_Covariate_OSMAC.RData"))
@@
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
   All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
 }
@@
 OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
+OSMAC_mMSE_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mMSE",]
 OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
@@
   All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
 }
@@
 OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
+OSMAC_mVc_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mVc",]
 OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
@@
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
+All_MSE_MLE<-rbind(RS_MSE_MLE,
+                   OSMAC_mMSE_MSE_MLE[,!(colnames(OSMAC_mMSE_MSE_MLE) %in% "Type")],
+                   OSMAC_mVc_MSE_MLE[,!(colnames(OSMAC_mVc_MSE_MLE) %in% "Type")])
 All_Info<-rbind(RS_Info,
@@
 
+All_MSE_MLE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("MSE")+ggtitle("MSE for MLE")->p7
+
 All_EMSE %>%
@@
 
-ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE)
+ggarrange(p7,p2,p1,p3,p4,p5,p6,common.legend = TRUE)
 ```
@@
   ylab("MSE")+ggtitle("MSE")->p2
+
+OSMAC_mMSE_MSE_MLE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("MSE")+ggtitle("MSE for MLE")->p7
 
@@
   ylab("MSE")+ggtitle("MSE")->p2
+
+OSMAC_mVc_MSE_MLE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("MSE")+ggtitle("MSE for MLE")->p7
 

### 2023-02-12 Identical_r0/Rmarkdown/Summary/r1_Best_Subsampling_Method.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

--- 2023-02-12 Identical_r0/Rmarkdown/Summary/Best_Subsampling_Method.Rmd
@@
 load(here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC.RData"))
+          "No_Correlated_Covariate_OSMAC_r1.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))

### 2023-02-12 Identical_r0/Rmarkdown/r1_OSMAC_Method.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

--- 2023-02-12 Identical_r0/Rmarkdown/OSMAC_Method.Rmd
@@
 Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
-load(here(Path,"OSMAC_output.RData"))
+load(here(Path,"OSMAC_output_r1.RData"))
 
@@
 # Assumed Model 1
-load(here(Path,"OSMAC_output_Old_1.RData"))
+load(here(Path,"OSMAC_output_Old_1_r1.RData"))
 
@@
 # Assumed Model 2
-load(here(Path,"OSMAC_output_Old_2.RData"))
+load(here(Path,"OSMAC_output_Old_2_r1.RData"))
 
@@
 
-load(here(Path,"OSMAC_output_Old_3.RData"))
+load(here(Path,"OSMAC_output_Old_3_r1.RData"))
 
@@
 # Assumed Model 1
-load(here(Path,"OSMAC_output_New_1.RData"))
+load(here(Path,"OSMAC_output_New_1_r1.RData"))
 
@@
 # Assumed Model 2
-load(here(Path,"OSMAC_output_New_2.RData"))
+load(here(Path,"OSMAC_output_New_2_r1.RData"))
 
@@
 # Assumed Model 3
-load(here(Path,"OSMAC_output_New_3.RData"))
+load(here(Path,"OSMAC_output_New_3_r1.RData"))
 
@@
 Path<-here("Identical_r0","Outputs",params$Model_Path,"OSMAC","ModelFree/")
-load(here(Path,"OSMAC_output.RData"))
+load(here(Path,"OSMAC_output_r1.RData"))
 
@@
 
-anim_save(filename="para_1.gif",animation = para_1,
+anim_save(filename="r1_para_1.gif",animation = para_1,
           path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","para_1.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_para_1.gif"))
 ```
@@
 
-anim_save(filename="Bias_1.gif",animation = Bias_1,
+anim_save(filename="r1_Bias_1.gif",animation = Bias_1,
           path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_Bias_1.gif"))
 ```
@@
 
-anim_save(filename="U_1.gif",animation = U_1,
+anim_save(filename="r1_U_1.gif",animation = U_1,
           path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_1.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_U_1.gif"))
 
@@
 
-anim_save(filename="U_2.gif",animation = U_2,
+anim_save(filename="r1_U_2.gif",animation = U_2,
           path=here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_2.gif"))
+include_graphics2(here("Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_U_2.gif"))
 ```
@@
      file = here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-                 "No_Correlated_Covariate_OSMAC.RData"))
+                 "No_Correlated_Covariate_OSMAC_r1.RData"))
 ```

### 2023-02-12 Publication_Ready.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

@@
 ---
+params:
+  Model_Path:
 title: "Publication Ready"
@@
 
-# Using Normal Distribution for Data
+# Using Uniform Distribution for Data
 
@@
   All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
 }
@@
 colnames(All_MSE)[3]<-"Estimated Values"
+colnames(All_MSE_MLE)[3]<-"Estimated Values"
 colnames(All_VAR)[3]<-"Estimated Values"
@@
                                cbind.data.frame(Metric="MSE",All_MSE),
+                               cbind.data.frame(Metric="MSE_MLE",All_MSE_MLE),
                                cbind.data.frame(Metric="Variance",All_VAR),
@@
 # OSMAC
-load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
           "No_Correlated_Covariate_OSMAC.RData"))
@@
 # OSMAC Model Free
-load(here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
           "No_Correlated_Covariate_OSMAC_MF.RData"))
@@
 All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
+All_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Model==Old_Labels[1],]
 All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]
@@
 All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
+All_MSE_MLE$Model[All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
 All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
@@
 OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
+OSMAC_MF_mMSE_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mMSE",]
 OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
@@
 All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
+All_MSE_MLE$Model[All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc MF")
 All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")
@@
 OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
+OSMAC_MF_mVc_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mVc",]
 OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
@@
                OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
+All_MSE_MLE<-rbind(RS_MSE_MLE,
+                   OSMAC_mMSE_MSE_MLE[,!(colnames(OSMAC_mMSE_MSE_MLE) %in% "Type")],
+                   OSMAC_mVc_MSE_MLE[,!(colnames(OSMAC_mVc_MSE_MLE) %in% "Type")],
+                   OSMAC_MF_mMSE_MSE_MLE[,!(colnames(OSMAC_MF_mMSE_MSE_MLE) %in% "Type")],
+                   OSMAC_MF_mVc_MSE_MLE[,!(colnames(OSMAC_MF_mVc_MSE_MLE) %in% "Type")])
 All_Info<-rbind(RS_Info,
@@
                                              "OSMAC mMSE MF","OSMAC mVc MF"))
+All_MSE_MLE$Model<-factor(All_MSE_MLE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
+                                                     "OSMAC mMSE RM","OSMAC mVc RM",
+                                                     "OSMAC mMSE AM 1","OSMAC mVc AM 1",
+                                                     "OSMAC mMSE AM 2","OSMAC mVc AM 2",
+                                                     "OSMAC mMSE AM 3","OSMAC mVc AM 3",
+                                                     "OSMAC mMSE MF","OSMAC mVc MF"))
 All_VAR$Model<-factor(All_VAR$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
@@
                                    cbind.data.frame(Metric="MSE",All_MSE),
+                                   cbind.data.frame(Metric="MSE_MLE",All_MSE_MLE),
                                    cbind.data.frame(Metric="Variance",All_VAR),
@@
 
+Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE"),] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
+  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p7
+
+Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE"),] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
+  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p8
+
 ggarrange(p1,p2,p3,p4,nrow = 4)
 ggarrange(p5,p6,nrow = 2)
+ggarrange(p7,p8,nrow = 2)
 ```
@@
   ylab("Estimated Values")+facet_wrap(~Data)->p6_New
+
+Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE") & 
+             Final_Data$Subsample_Size %in% SS_Choice,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
+  ylab("Estimated Values")+facet_wrap(~Data)->p7_New
+
+Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE") & 
+             Final_Data$Subsample_Size %in% SS_Choice,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  theme_light()+xlab("Sub sample size")+
+  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
+  ylab("Estimated Values")+facet_wrap(~Data)->p8_New
+
 ```
@@
 ggarrange(p5_New,p6_New,nrow = 2)
+ggarrange(p7_New,p8_New,nrow = 2)
 ```

### 2023-02-12 r1_Articles.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

---
title: "Articles_Plots"
author: "Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 14,fig.height = 16,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)

```

# Using Uniform Distribution for Data

```{r Load data model 1}
Model_1_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)

```

```{r Load data model 2}
Model_2_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)

```

```{r Load data model 3}
Model_3_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,All_ACC)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE)

```

```{r Load data model 4}
Model_4_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,All_ACC)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE",All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE for MLE",All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Average MSE Y",All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,RS_ACC)

```

```{r combine data and plot,fig.width = 8,fig.height = 12}
Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
                    M3_Identical_r0,M4_Identical_r0)

Identical_ro$Covariate<-factor(Identical_ro$Covariate,
                               levels = c("Data Model: x\u2081, x\u2082",
                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",
                                          "Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",
                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"))

Identical_ro$Model<-factor(Identical_ro$Model,
                           levels = c("mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
                                      "mMSE MR","mVc MR"))

Identical_ro$Model<-recode_factor(Identical_ro$Model,
                                  `mMSE DM`="Optimal subsampling mMSE: Data Model",
                                  `mMSE AM 1`="Optimal subsampling mMSE: Incorrect Model 1",
                                  `mMSE AM 2`="Optimal subsampling mMSE: Incorrect Model 2",
                                  `mMSE AM 3`="Optimal subsampling mMSE: Incorrect Model 3",
                                  `mVc DM`="Optimal subsampling mVc: Data Model",
                                  `mVc AM 1`="Optimal subsampling mVc: Incorrect Model 1",
                                  `mVc AM 2`="Optimal subsampling mVc: Incorrect Model 2",
                                  `mVc AM 3`="Optimal subsampling mVc: Incorrect Model 3",
                                  `mMSE MR`="Model Robust subsampling mMSE: Data Model",
                                  `mVc MR`="Model Robust subsampling mVc: Data Model")

Selected_Models_mMSE<-c("Optimal subsampling mMSE: Data Model",
                        "Optimal subsampling mMSE: Incorrect Model 1",
                        "Optimal subsampling mMSE: Incorrect Model 2",
                        "Optimal subsampling mMSE: Incorrect Model 3",
                        "Model Robust subsampling mMSE: Data Model")

# Colors_mMSE<-c("#FFC4D8","#E28490","#BB2C3E","#55141C",
#                "#DDCC77")

Colors_mMSE<-c("#cc0000", 
               "#ff578a","#ff578a","#ff578a",
               "darkgreen")

Selected_Models_mVc<-c("Optimal subsampling mVc: Data Model",
                       "Optimal subsampling mVc: Incorrect Model 1",
                       "Optimal subsampling mVc: Incorrect Model 2",
                       "Optimal subsampling mVc: Incorrect Model 3",
                       "Model Robust subsampling mVc: Data Model")

# Colors_mVc<-Colors_mVc<-c("#FFC4D8","#E28490","#BB2C3E","#55141C", 
#                           "#DDCC77")

Colors_mVc<-c("#cc0000", 
              "#ff578a","#ff578a","#ff578a",
              "darkgreen")

Theme_special<-function()
{
  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
        strip.text = element_text(colour = "black",size = 12,face="bold"),
        panel.grid.minor.x = element_blank(),
        axis.title= element_text(color = "black",face = "bold",size = 12),
        legend.text = element_text(color = "black", size=11),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-1,-2,-1,-2)) 
}

#Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE

Temp_legend_mMSE<-get_legend(Temp_plot_mMSE)

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc

Temp_legend_mVc<-get_legend(Temp_plot_mVc)

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p4

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p5

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p6

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p7

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p8

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggsave(filename = "r1_SMSE_MI_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggsave(filename = "r1_SMSE_MI_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 12)

ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mMSE.eps",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mVc.eps",res=300,width = 12,height = 12)
```

### 2023-02-12 r1_Publication_Ready.Rmd
Identical related files updated after increasing r0 values and MSE for MLE

--- 2023-02-12 Publication_Ready.Rmd
@@
 load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC.RData"))
+          "No_Correlated_Covariate_OSMAC_r1.RData"))
 
@@
 load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC_MF.RData"))
+          "No_Correlated_Covariate_OSMAC_MF_r1.RData"))
 
@@
 ```
-
-```{r Identical r0 Plots with gg.gap,fig.height=4}
-SS_Choice<-100*c(10:15)
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p1_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p2_New
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p3_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p4_New
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p5_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p6_New
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p7_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p8_New
-
-```
-
-```{r All Plots}
-ggarrange(p1,p1_New,
-          p2,p2_New,nrow = 4)
-
-ggarrange(p5_New,p6_New,nrow = 2)
-ggarrange(p7_New,p8_New,nrow = 2)
-```

### 2023-02-12 Identical_r0/Rmarkdown/OSMAC_Command.R

@@ -1,5 +1,4 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
@@ -8,11 +7,16 @@ Model<-c("Model_1","Model_2",
 for (j in 1:length(Model)) 
 {
   # OSMAC Method ----
-  ezknit(file=here("Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
-         out_dir=here("Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[j]),
-         verbose = TRUE,keep_md = FALSE)
-  #open_output_dir()
+  render(input=here("Identical_r0","Rmarkdown","OSMAC_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "OSMAC_Method",
+         output_dir=here("Identical_r0","htmloutputs",Model[j],"OSMAC"),
+         params=list("Model_Path"=Model[j]))
+  
+  render(input=here("Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "r1_OSMAC_Method",
+         output_dir=here("Identical_r0","htmloutputs",Model[j],"OSMAC"),
+         params=list("Model_Path"=Model[j]))
 }
 

### 2023-02-12 Identical_r0/Rmarkdown/Summary/Summary_Rmarkdown.R

@@ -1,5 +1,4 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
@@ -8,11 +7,16 @@ Model<-c("Model_1","Model_2",
 # Best_Subsampling_Method ----
 for (i in 1:length(Model))
 {
-ezknit(file=here("Identical_r0","Rmarkdown","Classical","Summary","Best_Subsampling_Method.Rmd"),
-        out_dir=here("Identical_r0","Summary","Classical",Model[i],"Best_Subsampling"),
-        fig_dir = c("Plots"),
-        params=list("Model_Path"=Model[i]),
-        verbose = TRUE,keep_md = FALSE)
-#open_output_dir()
+  render(input=here("Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "Best_Subsampling_Method",
+         output_dir=here("Identical_r0","Summary",Model[i],"Best_Subsampling"),
+         params=list("Model_Path"=Model[i]))
+  
+  # render(input=here("Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_Best_Subsampling_Method",
+  #        output_dir=here("Identical_r0","Summary",Model[i],"Best_Subsampling"),
+  #        params=list("Model_Path"=Model[i]))
 }
 

### 2023-02-12 Identical_r0/Simulation_Setup/Analysis/OSMAC/Simulation_Results_OSMAC_Sampling.R

@@ -6,11 +6,11 @@ library(LaplacesDemon)
 enableJIT(1)
 
 # Load the No Correlated Data----
-load(here("Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Init.RData"))
+load(here("Identical_r0","Simulation_Setup","Analysis","OSMAC","Init.RData"))
 #load(here("Init.RData"))
 
 # Load the OSMAC Sample----
-load(here("Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Run_OSMAC.RData"))
+load(here("Identical_r0","Simulation_Setup","Analysis","OSMAC","Run_OSMAC.RData"))
 #load(here("Run_OSMAC.RData"))
 
 All_Covariates<-c("X0","X1","X2","X1^2","X2^2")

### 2023-02-12 Identical_r0/Simulation_Setup/Analysis/OSMAC/r1_Simulation_Results_OSMAC_Sampling.R

@@ -1,0 +1,92 @@
+# Run for OSMAC Sampling----
+library(compiler)
+library(here)
+library(LaplacesDemon)
+
+enableJIT(1)
+
+# Load the No Correlated Data----
+load(here("Identical_r0","Simulation_Setup","Analysis","OSMAC","Init.RData"))
+#load(here("Init.RData"))
+
+# Load the OSMAC Sample----
+load(here("Identical_r0","Simulation_Setup","Analysis","OSMAC","r1_Run_OSMAC.RData"))
+#load(here("Run_OSMAC.RData"))
+
+All_Covariates<-c("X0","X1","X2","X1^2","X2^2")
+
+# Model 1----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+if(Model_Path=="Model_1")
+{
+  combs<-list(All_Covariates[-5],
+              All_Covariates[-4],
+              All_Covariates) 
+  
+  Final_Parameter<-Run_OSMAC(Replicates = Replicates, r1 = c(100*(1:9)), r2 = 1000,
+                             Y = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                             X = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                             Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
+                             N = Simulated_Data$Basic$N,
+                             alpha = rep(1/4,length(combs)+1),
+                             combs = combs,
+                             All_Covariates = All_Covariates)
+}
+
+# Model 2----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+if(Model_Path=="Model_2")
+{
+  combs<-list(All_Covariates[-c(4,5)],
+              All_Covariates[-4],
+              All_Covariates) 
+  
+  Final_Parameter<-Run_OSMAC(Replicates = Replicates, r1 = c(100*(1:9)), r2 = 1000,
+                             Y = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                             X = as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                             Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
+                             N = Simulated_Data$Basic$N,
+                             alpha = rep(1/4,length(combs)+1),
+                             combs = combs,
[…]

### 2023-02-12 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -14,517 +14,518 @@ Cordeiro<-function(XData,With_bias)
 
 # Two step OSMAC ----
 AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
-    Y_Real<-Real_Data[,1] #  Real Data
-    X_Real<-Real_Data[,-1] # Real Data
-    
-    PI.prop <- rep(1/n, n)
-    idx.prop <- sample(1:n, r1, T, PI.prop)
-    
-    x.prop<-lapply(1:length(combs),function(j){
-      X[idx.prop,All_Covariates %in% combs[[j]]] # Assumed Data 
-    })
-    y.prop <- Y[idx.prop,]  # Assumed Data 
-    
-    x_Real.prop<-X_Real[idx.prop,] # Real Data
-    y_Real.prop<-Y_Real[idx.prop] # Real Data
-    
-    pinv.prop <- rep(n,r1)
-    
-    fit.prop <- lapply(1:length(combs), function(j){
-      glm(y.prop~x.prop[[j]]-1,family = "poisson")# Assumed Data
-    })
-    fit_Real.prop <- glm(y_Real.prop~x_Real.prop-1,family = "poisson") # Real Data
-    
-    beta.prop<-list()
-    for (j in 1:length(combs)) 
-      {
-      beta.prop[[j]] <- fit.prop[[j]]$coefficients # Assumed Data
-      if(anyNA(beta.prop[[j]]))
-        {
-        return(list(opt=NA, msg="first stage not converge"))
-        }
-      }
-    beta_Real.prop <- fit_Real.prop$coefficients # Real Data
-    
-    if(anyNA(beta_Real.prop[1]))
+  Y_Real<-Real_Data[,1] #  Real Data
+  X_Real<-Real_Data[,-1] # Real Data
+  
+  PI.prop <- rep(1/n, n)
+  idx.prop <- sample(1:n, r1, T, PI.prop)
+  
+  x.prop<-lapply(1:length(combs),function(a){
+    X[idx.prop,All_Covariates %in% combs[[a]]] # Assumed Data 
+  })
+  y.prop <- Y[idx.prop,]  # Assumed Data 
+  
+  x_Real.prop<-X_Real[idx.prop,] # Real Data
[…]

### 2023-02-12 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R

@@ -3,7 +3,7 @@ library(compiler)
 library(LaplacesDemon)
 
 # Load the OSMAC algorithm
-source(here("Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Algorithm.R"))
+source(here("Identical_r0","Simulation_Setup","R_Scripts","OSMAC_Algorithm.R"))
 
 AlgTwoStp<-cmpfun(AlgTwoStp)
 Cordeiro<-cmpfun(Cordeiro)
@@ -101,7 +101,7 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
       Bias_Assumed_Old_mVc_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mVc
       Bias_Assumed_New_mMSE_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mMSE
       Bias_Assumed_New_mVc_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mVc
-     
+      
       Utility_Real_mMSE[[i]]<-Results$opt$opt_Real$Utility_mMSE
       Utility_Real_mVc[[i]]<-Results$opt$opt_Real$Utility_mVc
       Utility_ModelFree_mMSE[[i]]<-Results$opt$opt_join$Utility_mMSE
@@ -141,7 +141,7 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
     },error=function(e){ i=i; print("Failed")})
     
   }
-
+  
   # Real Model
   Final_param_mMSE<-do.call(rbind,Parameter_Real_mMSE)
   Final_param_mVc<-do.call(rbind,Parameter_Real_mVc)
@@ -181,13 +181,13 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
   # colnames(Probability)<-c("Simulation","Y",paste0("X",0:(ncol(X_Real)-1)),"mMSE","mVc")
   
   save(list= c("Results_OSMAC","Bias_OSMAC","Utility_OSMAC"#,"Sample_OSMAC","Probability"
-               ),
-       file = here("Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC",
-                   "Results","Real_Model","OSMAC_output.RData"))
+  ),
[…]

### 2023-02-12 Identical_r0/Simulation_Setup/R_Scripts/Setup_Data.R

@@ -1,9 +1,9 @@
 library(here)
 
-Model_Path<-"Model_1"
+#Model_Path<-"Model_1"
 #Model_Path<-"Model_2"
 #Model_Path<-"Model_3"
-#Model_Path<-"Model_4"
+Model_Path<-"Model_4"
 
 # OSMAC Data ----
 Base_Path<-"OSMAC"
@@ -11,7 +11,7 @@ Base_Path<-"OSMAC"
 ## No Correlated Covariate Data -----
 load(here("Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
 save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
-     file = here("Identical_r0","Simulation_Setup","Classical","Analysis",
+     file = here("Identical_r0","Simulation_Setup","Analysis",
                  Base_Path,"Init.RData"))        
 
 remove(Base_Path)

### 2023-02-12 Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Algorithm.R

@@ -1,0 +1,533 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two step OSMAC ----
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
+  Y_Real<-Real_Data[,1] #  Real Data
+  X_Real<-Real_Data[,-1] # Real Data
+  
+  PI.prop <- rep(1/n, n)
+  
+  # For the Real Model 
+  beta.mVc_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  Utility_mVc_Real<-matrix(nrow = length(r1),ncol = 3 )
+  Bias_mVc_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  
+  beta.mMSE_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  Utility_mMSE_Real<-matrix(nrow = length(r1),ncol = 3 )
+  Bias_mMSE_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  
+  #Sample.mMSE_Real<-list()
+  #Sample.mVc_Real<-list()
+  
+  beta.mVc_Old<-Utility_mVc_Old<-Bias_mVc_Old<-list()
+  beta.mMSE_Old<-Utility_mMSE_Old<-Bias_mMSE_Old<-list()
+  #Sample.mMSE_Assumed_Old<-list()
+  #Sample.mVc_Assumed_Old<-list()
+  
+  # For the Assumed Model with Already Available Sub-sampling probabilities
+  for (a in 1:length(combs)) 
+  {
+    beta.mVc_Old[[a]]<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+    Utility_mVc_Old[[a]]<-matrix(nrow = length(r1),ncol = 3 )
[…]

### 2023-02-12 Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Setup.R

@@ -1,0 +1,352 @@
+library(here)
+library(compiler)
+library(LaplacesDemon)
+
+# Load the OSMAC algorithm
+source(here("Identical_r0","Simulation_Setup","R_Scripts","r1_OSMAC_Algorithm.R"))
+
+AlgTwoStp<-cmpfun(AlgTwoStp)
+Cordeiro<-cmpfun(Cordeiro)
+
+# Using OSMAC to Sub-sample from Big Data ----
+Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
+{
+  X_Real<-Real_Data[,-1]
+  # From r0 and r conduct OSMAC subsampling for Logistic regression-----
+  Parameter_Real_mMSE<-list(); Parameter_Real_mVc<-list()
+  Parameter_ModelFree_mMSE<-list(); Parameter_ModelFree_mVc<-list()
+  
+  for (j in 1:length(combs)) 
+  {
+    assign(paste0("Parameter_Assumed_Old_mMSE_",j),list())
+    assign(paste0("Parameter_Assumed_Old_mVc_",j),list())
+    assign(paste0("Parameter_Assumed_New_mMSE_",j),list())
+    assign(paste0("Parameter_Assumed_New_mVc_",j),list())  
+  }
+  
+  Bias_Real_mMSE<-list(); Bias_Real_mVc<-list()
+  Bias_ModelFree_mMSE<-list(); Bias_ModelFree_mVc<-list()
+  
+  for(j in 1:length(combs))
+  {
+    assign(paste0("Bias_Assumed_Old_mMSE_",j),list())
+    assign(paste0("Bias_Assumed_Old_mVc_",j),list())
+    assign(paste0("Bias_Assumed_New_mMSE_",j),list())
+    assign(paste0("Bias_Assumed_New_mVc_",j),list())
+  }
+  
+  Utility_Real_mMSE<-list(); Utility_Real_mVc<-list()
+  Utility_ModelFree_mMSE<-list(); Utility_ModelFree_mVc<-list()
+  
+  for(j in 1:length(combs))
+  {
+    assign(paste0("Utility_Assumed_Old_mMSE_",j),list())
+    assign(paste0("Utility_Assumed_Old_mVc_",j),list())
+    assign(paste0("Utility_Assumed_New_mMSE_",j),list())
[…]

### 2023-02-12 Publication_Ready_command.R

@@ -1,17 +1,21 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
-         "Model_3","Model_4"); #i=4
+         "Model_3","Model_4"); i=1
 
 for(i in 1:length(Model))
 {
   # Publication Ready ----
-  ezknit(file=here("Publication_Ready.Rmd"),
-         out_dir=here("Publication_Ready",Model[i]),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[i]),
-         verbose = TRUE,keep_md = TRUE,keep_html = FALSE)
-  #open_output_dir()
+  render(input=here("Publication_Ready.Rmd"),
+         output_format = "github_document",
+         output_file = "Publication_Ready",
+         output_dir=here("Publication_Ready",Model[i]),
+         params=list("Model_Path"=Model[i]))
+  
+  # render(input=here("r1_Publication_Ready.Rmd"),
+  #        output_format = "github_document",
+  #        output_file = "r1_Publication_Ready",
+  #        output_dir=here("Publication_Ready",Model[i]),
+  #        params=list("Model_Path"=Model[i]))
 }

### 2023-02-12 Non_Identical_r0/Rmarkdown/OSMAC_Method.Rmd
Non identical related files updated after increasing r0 values and MSE for MLE

--- 2022-09-27 Non_Identical_r0/Rmarkdown/Classical/OSMAC_Method.Rmd
@@
 ```{r Load Data}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Real_Model/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
 load(here(Path,"OSMAC_output.RData"))
@@
 ```{r Load the Data AM 1}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model_1/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_1/")
 load(here(Path,"OSMAC_output.RData"))
@@
 ```{r Load the Data AM 2}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model_2/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_2/")
 load(here(Path,"OSMAC_output.RData"))
@@
 ```{r Load the Data AM 3}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC","Assumed_Model_3/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_3/")
 load(here(Path,"OSMAC_output.RData"))
@@
 anim_save(filename="para_1.gif",animation = para_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","para_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","para_1.gif"))
 ```
@@
 anim_save(filename="Bias_1.gif",animation = Bias_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
 ```
@@
 anim_save(filename="U_1.gif",animation = U_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_1.gif"))
 
@@
 anim_save(filename="U_2.gif",animation = U_2,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC","Plots","U_2.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_2.gif"))
 ```
@@
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
-     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
+     file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                  "No_Correlated_Covariate_OSMAC.RData"))
@@
 Plot_list<-list()
+
 All_MSE %>%
@@
 
+All_MSE_MLE %>%
+  ungroup(Type,Model,Subsample_Size) %>%
+ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
+  ylab("SMSE")+ggtitle("SMSE Comparison for MLE")->Plot_list[[2]]
+
 All_VAR %>%
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[2]]
+  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[3]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[3]]
+  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[4]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[4]]
+  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[5]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[5]]
+  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[6]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 2)+
-  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_list[[7]]
 
-ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
+ggarrange(plotlist = Plot_list,nrow = 7,ncol = 1,common.legend = TRUE)
 ```
@@
 
+All_MSE_MLE %>%
+  ungroup(Type,Model,Subsample_Size) %>%
+  mutate(Efficiency=MSE/Full_SMSE) %>%
+ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
+  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency for MLE")->Plot_list[[2]]
+
 All_VAR %>%
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[2]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[3]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[3]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[4]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[4]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[5]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type)+
-  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[5]]
+  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[6]]
 
@@
   theme_light()+xlab("Sub sample size")+facet_wrap(~Type,ncol = 2)+
-  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[7]]
 
-ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
+ggarrange(plotlist = Plot_list,nrow = 7,ncol = 1,common.legend = TRUE)
 ```

### 2023-02-12 Non_Identical_r0/Rmarkdown/OSMAC_Model_Free_Method.Rmd
Non identical related files updated after increasing r0 values and MSE for MLE

@@
 ---
+params:
+  Model_Path:
 title: "OSMAC_Model_Free_Method; Model: `r params$Model_Path`; "
@@
 
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"OSMAC_Model_Free/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC_Model_Free/")
 load(here(Path,"OSMAC_MF_output.RData"))
@@
 anim_save(filename="para_1.gif",animation = para_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))
-
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","para_1.gif"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
+
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","para_1.gif"))
 ```
@@
 anim_save(filename="Bias_1.gif",animation = Bias_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))
-
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","Bias_1.gif"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
+
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","Bias_1.gif"))
 ```
@@
 anim_save(filename="U_1.gif",animation = U_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))
-
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","U_1.gif"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
+
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","U_1.gif"))
 
@@
 anim_save(filename="U_2.gif",animation = U_2,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots"))
-
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"OSMAC_Model_Free","Plots","U_2.gif"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
+
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","U_2.gif"))
 ```
@@
        Bias_Vline,Temp_Info,Temp_W,Temp_P,
-       Estimated_Vline,Full_model)
+       Full_model)
 
@@
 
+  # Summarize SMSE MLE
+  Est_Parameter_RM %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Model = params$Model_Path ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_RM
+
+  Est_Parameter_AM_1 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_1$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Model = "Model_2" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_1
+
+  Est_Parameter_AM_2 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_2$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Model = "Model_3" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_2
+
+  Est_Parameter_AM_3 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_3$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Estimated_5=Theta4,
+                            Model = "Model_4" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_3
+
+  All_MSE_MLE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
+                     data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
+                     data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
+                     data.frame("Model"="Assumed Model 3",All_MSE_AM_3))
+
+  remove(All_MSE_RM,All_MSE_AM_1,All_MSE_AM_2,All_MSE_AM_3)
+
   # Summarise Bias
@@
   All_MSE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
+                 data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
+                 data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
+                 data.frame("Model"="Assumed Model 3",All_MSE_AM_3))
+
+  remove(All_MSE_RM,All_MSE_AM_1,All_MSE_AM_2,All_MSE_AM_3)
+
+  # Summarize SMSE MLE
+  Est_Parameter_RM %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Model = params$Model_Path ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_RM
+
+  Est_Parameter_AM_1 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_1$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Model = "Model_1" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_1
+
+  Est_Parameter_AM_2 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_2$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Model = "Model_3" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_2
+
+  Est_Parameter_AM_3 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_3$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Estimated_5=Theta4,
+                            Model = "Model_4" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_3
+
+  All_MSE_MLE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                      data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
@@
   All_MSE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
+                 data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
+                 data.frame("Model"="Assumed Model 2",All_MSE_AM_2),
+                 data.frame("Model"="Assumed Model 3",All_MSE_AM_3))
+
+  remove(All_MSE_RM,All_MSE_AM_1,All_MSE_AM_2,All_MSE_AM_3)
+
+  # Summarize SMSE MLE
+  Est_Parameter_RM %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Estimated_5=Theta4,
+                            Model = params$Model_Path ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_RM
+
+  Est_Parameter_AM_1 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_1$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Model = "Model_1" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_1
+
+  Est_Parameter_AM_2 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_2$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Model = "Model_3" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_2
+
+  Est_Parameter_AM_3 %>%
+    dplyr::select(Type,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+    group_by(Type,Subsample_Size) %>%
+    mutate( MSE=Final_MSE(Real = Estimated_Vline_AM_3$Values,
+                            Estimated_1=Theta0, 
+                            Estimated_2=Theta1,
+                            Estimated_3=Theta2,
+                            Estimated_4=Theta3,
+                            Model = "Model_2" ))%>%
+    distinct(MSE) %>% 
+    forestmangr::round_df(8)->All_MSE_AM_3
+
+  All_MSE_MLE<-rbind(data.frame("Model"="Real Model",All_MSE_RM),
                      data.frame("Model"="Assumed Model 1",All_MSE_AM_1),
@@
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
-     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
+     file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                  "No_Correlated_Covariate_OSMAC_MF.RData"))
@@
 
+All_MSE_MLE[All_MSE_MLE$Model=="Real Model",] %>%
+  #ungroup(Model,Subsample_Size) %>%
+  mutate(Efficiency=MSE/Full_SMSE_RM) %>%
+ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+facet_wrap(~Type,ncol = 1)+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency for MLE")->Plot_list[[2]]
+
 All_VAR[All_VAR$Model=="Real Model",] %>%
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[2]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Variance Efficiency")->Plot_list[[3]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[3]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Model Information Efficiency")->Plot_list[[4]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[4]]
+  ylab("Relative Efficiency")+ggtitle("Estimated Bias Efficiency")->Plot_list[[5]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[5]]
+  ylab("Relative Efficiency")+ggtitle("EMSE Efficiency")->Plot_list[[6]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
-
-ggarrange(plotlist = Plot_list,nrow = 1,ncol = 6,common.legend = TRUE)
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[7]]
+
+ggarrange(plotlist = Plot_list,nrow = 1,ncol = 7,common.legend = TRUE)
 

### 2023-02-12 Non_Identical_r0/Rmarkdown/Random_Sampling.Rmd
Non identical related files updated after increasing r0 values and MSE for MLE

--- 2022-09-27 Non_Identical_r0/Rmarkdown/Classical/Random_Sampling.Rmd
@@
 ---
+params:
+  Model_Path:
 title: "Random_Sampling; Model: `r params$Model_Path`;"
@@
 ```{r Load Data RM}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Real_Model/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"Random_Sampling","Real_Model/")
 load(here(Path,"Random_Sample_output.RData"))
@@
 ```{r Load Data AM 1}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Assumed_Model_1/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"Random_Sampling","Assumed_Model_1/")
 load(here(Path,"Random_Sample_output.RData"))
@@
 ```{r Load Data AM 2}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Assumed_Model_2/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"Random_Sampling","Assumed_Model_2/")
 load(here(Path,"Random_Sample_output.RData"))
@@
 ```{r Load Data AM 3}
-Path<-here("Non_Identical_r0","Outputs","Classical",params$Model_Path,"Random_Sampling","Assumed_Model_3/")
+Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"Random_Sampling","Assumed_Model_3/")
 load(here(Path,"Random_Sample_output.RData"))
@@
 anim_save(filename="para_1.gif",animation = para_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","para_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots","para_1.gif"))
 ```
@@
 anim_save(filename="Bias_1.gif",animation = Bias_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","Bias_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots","Bias_1.gif"))
 ```
@@
 anim_save(filename="U_1.gif",animation = U_1,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","U_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots","U_1.gif"))
 
@@
 anim_save(filename="U_2.gif",animation = U_2,
-          path=here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots"))
+          path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs","Classical",params$Model_Path,"Random_Sampling","Plots","U_2.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"Random_Sampling","Plots","U_2.gif"))
 ```
@@
 
+  # Summarize SMSE MLE
+  Est_Parameter %>%
+        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2) %>%
+        group_by(Model,Subsample_Size) %>%
+        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                              Estimated_1=Theta0, 
+                              Estimated_2=Theta1,
+                              Estimated_3=Theta2,
+                              Model = params$Model_Path ))%>%
+        distinct(MSE) %>% 
+        forestmangr::round_df(8)->All_MSE_MLE
+
   # Summarise Bias
@@
         forestmangr::round_df(8)->All_MSE
+
+  # Summarize SMSE MLE
+  Est_Parameter %>%
+        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3) %>%
+        group_by(Model,Subsample_Size) %>%
+        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                              Estimated_1=Theta0, 
+                              Estimated_2=Theta1,
+                              Estimated_3=Theta2,
+                              Estimated_4=Theta3,
+                              Model = params$Model_Path ))%>%
+        distinct(MSE) %>% 
+        forestmangr::round_df(8)->All_MSE_MLE
 
@@
         forestmangr::round_df(8)->All_MSE
+
+  # Summarize SMSE MLE
+  Est_Parameter %>%
+        dplyr::select(Model,Subsample_Size,Theta0,Theta1,Theta2,Theta3,Theta4) %>%
+        group_by(Model,Subsample_Size) %>%
+        mutate( MSE=Final_MSE(Real = Estimated_Vline$Values,
+                              Estimated_1=Theta0, 
+                              Estimated_2=Theta1,
+                              Estimated_3=Theta2,
+                              Estimated_4=Theta3,
+                              Estimated_5=Theta4,
+                              Model = params$Model_Path ))%>%
+        distinct(MSE) %>% 
+        forestmangr::round_df(8)->All_MSE_MLE
 
@@
 # Store the Results
-save(All_MSE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
-     file = here("Non_Identical_r0","Summary","Classical",params$Model_Path,"Data","Efficiency",
+save(All_MSE,All_MSE_MLE,All_EMSE,All_Bias,All_VAR,All_Info,Accuracy_Data,
+     file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
                  "No_Correlated_Covariate_RS.RData"))
@@
 
+All_MSE_MLE %>%
+  ungroup(Model,Subsample_Size) %>%
+ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("SMSE")+ggtitle("SMSE Comparison for MLE")->Plot_list[[2]]
+
 All_VAR %>%
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[2]]
+  ylab("Mean Variance")+ggtitle("Estimated Variance Comparison")->Plot_list[[3]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[3]]
+  ylab("Average Information")+ggtitle("Estimated Model Information Comparison")->Plot_list[[4]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[4]]
+  ylab("Average Bias")+ggtitle("Estimated Bias Comparison")->Plot_list[[5]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[5]]
+  ylab("EMSE")+ggtitle("EMSE Comparison")->Plot_list[[6]]
 
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+  ylab("Average MSE y")+ggtitle("Average MSE y")->Plot_list[[7]]
 
-ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
+ggarrange(plotlist = Plot_list,nrow = 7,ncol = 1,common.legend = TRUE)
 
@@
 
+All_MSE_MLE %>%
+  ungroup(Model,Subsample_Size) %>%
+  mutate(Efficiency=MSE/Full_SMSE) %>%
+ggplot(.,aes(x=Subsample_Size,y=Efficiency,color=Model))+geom_point()+
+  geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Relative Efficiency")+ggtitle("SMSE Efficiency for MLE")->Plot_list[[2]]
+
 All_VAR %>%
@@
   theme_light()+xlab("Sub sample size")+
-  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[6]]
+  ylab("Relative Average MSE y")+ggtitle("Average MSE y")->Plot_list[[7]]
 
-ggarrange(plotlist = Plot_list,nrow = 6,ncol = 1,common.legend = TRUE)
+ggarrange(plotlist = Plot_list,nrow = 7,ncol = 1,common.legend = TRUE)
 ```

### 2023-02-12 Non_Identical_r0/Rmarkdown/Summary/Best_Subsampling_Method.Rmd
Non identical related files updated after increasing r0 values and MSE for MLE

--- 2023-02-12 Publication_Ready.Rmd
@@
   Model_Path:
-title: "Publication Ready"
-author: "Amalan"
+title: "Best Sub-sampling Method: `r params$Model_Path`"
+author: "M.Amalan"
 date: '`r format(Sys.Date(), "%B %d, %Y")`'
-output: github_document
+output: html_document
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,fig.width = 15,fig.height = 20,message = FALSE,warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE,fig.width = 12,fig.height = 12,message = FALSE,warning = FALSE)
 library(here)
@@
 
-# Using Uniform Distribution for Data
-
-## Model : `r params$Model_Path`
-
-```{r load Identical Data}
+```{r load Data}
 Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
@@
   All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
   All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
-  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
   All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
@@
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
-
-# OSMAC
-load(here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC.RData"))
-remove_stuff<-c(paste0("Assumed New ",1:3))
-
-All_Bias<-All_Bias[!(All_Bias$Model %in% remove_stuff),]
-All_EMSE<-All_EMSE[!(All_EMSE$Model %in% remove_stuff),]
-All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
-All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
-All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
-All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]
-Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]
-
-Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
-New_Labels<-c("RM",paste0("AM ",1:3),"MF")
-
-## mMSE
-for (i in 1:length(Old_Labels)) 
-{
-  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
-}
-
-## mVc
-for (i in 1:length(Old_Labels)) 
-{
-  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-}
-
-OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
-OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
-OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
-OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
-OSMAC_mMSE_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mMSE",]
-OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
-OSMAC_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]
-
-OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
-OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
-OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
-OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
-OSMAC_mVc_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mVc",]
-OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
-OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]
-
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
-
-# All elements
-All_Bias<-rbind(RS_Bias,
-                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
-                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")])
-All_EMSE<-rbind(RS_EMSE,
-                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
-                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")])
-All_MSE<-rbind(RS_MSE,
-               OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
-               OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
-All_MSE_MLE<-rbind(RS_MSE_MLE,
-                   OSMAC_mMSE_MSE_MLE[,!(colnames(OSMAC_mMSE_MSE_MLE) %in% "Type")],
-                   OSMAC_mVc_MSE_MLE[,!(colnames(OSMAC_mVc_MSE_MLE) %in% "Type")])
-All_Info<-rbind(RS_Info,
-                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
-                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")])
-All_VAR<-rbind(RS_VAR,
-                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
-                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])
-All_ACC<-rbind(RS_ACC,
-                OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
-                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")])
-
-All_Objects<-ls()
-remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
-
-colnames(All_Bias)[3]<-"Estimated Values"
-colnames(All_EMSE)[3]<-"Estimated Values"
-colnames(All_Info)[3]<-"Estimated Values"
-colnames(All_MSE)[3]<-"Estimated Values"
-colnames(All_MSE_MLE)[3]<-"Estimated Values"
-colnames(All_VAR)[3]<-"Estimated Values"
-colnames(All_ACC)[3]<-"Estimated Values"
-
-Final_Data_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
-                               cbind.data.frame(Metric="EMSE",All_EMSE),
-                               cbind.data.frame(Metric="Model Information",All_Info),
-                               cbind.data.frame(Metric="MSE",All_MSE),
-                               cbind.data.frame(Metric="MSE_MLE",All_MSE_MLE),
-                               cbind.data.frame(Metric="Variance",All_VAR),
-                               cbind.data.frame(Metric="Accuracy",All_ACC))
-
-remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR,All_ACC)
-```
-
-```{r load Non Identical Data}
-Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
-New_Labels<-c("RM",paste0("AM ",1:3))
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
 
@@
   All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
-  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
+  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
   Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
@@
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
 
-Accuracy_Data<-cbind(Model="Real Model",Accuracy_Data)
-
-Old_Labels[1]<-c("Real Model")
+Accuracy_Data<-cbind(Accuracy_Data[,1],Model="Real Model",Accuracy_Data[,-1])
 
@@
 
+# Special mMSE elements
+SP_All_mMSE_Bias<-rbind(OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
+                        OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")])
+SP_All_mMSE_EMSE<-rbind(OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
+                        OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")])
+SP_All_mMSE_MSE<-rbind(OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
+                       OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")])
+SP_All_mMSE_MSE_MLE<-rbind(OSMAC_mMSE_MSE_MLE[,!(colnames(OSMAC_mMSE_MSE_MLE) %in% "Type")],
+                           OSMAC_MF_mMSE_MSE_MLE[,!(colnames(OSMAC_MF_mMSE_MSE_MLE) %in% "Type")])
+SP_All_mMSE_Info<-rbind(OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
+                        OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")])
+SP_All_mMSE_VAR<-rbind(OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
+                       OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")])
+SP_All_mMSE_ACC<-rbind(OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
+                       OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")])
+
+# Special mVc elements
+SP_All_mVc_Bias<-rbind(OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
+                        OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
+SP_All_mVc_EMSE<-rbind(OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
+                        OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
+SP_All_mVc_MSE<-rbind(OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
+                       OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
+SP_All_mVc_MSE_MLE<-rbind(OSMAC_mVc_MSE_MLE[,!(colnames(OSMAC_mVc_MSE_MLE) %in% "Type")],
+                          OSMAC_MF_mVc_MSE_MLE[,!(colnames(OSMAC_MF_mVc_MSE_MLE) %in% "Type")])
+SP_All_mVc_Info<-rbind(OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
+                        OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
+SP_All_mVc_VAR<-rbind(OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
+                       OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
+SP_All_mVc_ACC<-rbind(OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
+                       OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])
+
 All_Objects<-ls()
@@
 remove(list = All_Objects[startsWith(All_Objects,"RS")])
-
-All_Bias$Model<-factor(All_Bias$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                               "OSMAC mMSE RM","OSMAC mVc RM",
-                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
-                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
-                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
-                                               "OSMAC mMSE MF","OSMAC mVc MF"))
-All_EMSE$Model<-factor(All_EMSE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                               "OSMAC mMSE RM","OSMAC mVc RM",
-                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
-                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
-                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
-                                               "OSMAC mMSE MF","OSMAC mVc MF"))
-All_Info$Model<-factor(All_Info$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                               "OSMAC mMSE RM","OSMAC mVc RM",
-                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
-                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
-                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
-                                               "OSMAC mMSE MF","OSMAC mVc MF"))
-All_MSE$Model<-factor(All_MSE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                             "OSMAC mMSE RM","OSMAC mVc RM",
-                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
-                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
-                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
-                                             "OSMAC mMSE MF","OSMAC mVc MF"))
-All_MSE_MLE$Model<-factor(All_MSE_MLE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                                     "OSMAC mMSE RM","OSMAC mVc RM",
-                                                     "OSMAC mMSE AM 1","OSMAC mVc AM 1",
-                                                     "OSMAC mMSE AM 2","OSMAC mVc AM 2",
-                                                     "OSMAC mMSE AM 3","OSMAC mVc AM 3",
-                                                     "OSMAC mMSE MF","OSMAC mVc MF"))
-All_VAR$Model<-factor(All_VAR$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                             "OSMAC mMSE RM","OSMAC mVc RM",
-                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
-                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
-                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
-                                             "OSMAC mMSE MF","OSMAC mVc MF"))
-All_ACC$Model<-factor(All_ACC$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
-                                             "OSMAC mMSE RM","OSMAC mVc RM",
-                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
-                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
-                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
-                                             "OSMAC mMSE MF","OSMAC mVc MF"))
-
-colnames(All_Bias)[3]<-"Estimated Values"
-colnames(All_EMSE)[3]<-"Estimated Values"
-colnames(All_Info)[3]<-"Estimated Values"
-colnames(All_MSE)[3]<-"Estimated Values"
-colnames(All_MSE_MLE)[3]<-"Estimated Values"
-colnames(All_VAR)[3]<-"Estimated Values"
-colnames(All_ACC)[3]<-"Estimated Values"
-
-Final_Data_Non_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
-                                   cbind.data.frame(Metric="EMSE",All_EMSE),
-                                   cbind.data.frame(Metric="Model Information",All_Info),
-                                   cbind.data.frame(Metric="MSE",All_MSE),
-                                   cbind.data.frame(Metric="MSE_MLE",All_MSE_MLE),
-                                   cbind.data.frame(Metric="Variance",All_VAR),
-                                   cbind.data.frame(Metric="MSE Y",All_ACC))
-
-remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR)
 ```
 
-```{r Identical r0 Plots}
-# mMSE models Colors
-Selected_mMSE<-c(#"RS RM",
-                 #"RS AM 1","RS AM 2","RS AM 3",
-                 "OSMAC mMSE RM",
-                 "OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
-                 "OSMAC mMSE MF")
-Colors_mMSE<-c(#"#88CCEE",
-               #"#A6C3D3","#5D92B0","#35586C", 
-               "#FFC4D8", 
-               "#E28490","#BB2C3E","#55141C", 
-               "#DDCC77")
-# mvc models
-Selected_mVc<-c(#"RS RM",
-                #"RS AM 1","RS AM 2","RS AM 3",
-                "OSMAC mVc RM",
-                "OSMAC mVc AM 1","OSMAC mVc AM 2","OSMAC mVc AM 3",
-                "OSMAC mVc MF")
-Colors_mVc<-c(#"#88CCEE",
-              #"#A6C3D3","#5D92B0","#35586C", 
-              "#FFC4D8", 
-               "#E28490","#BB2C3E","#55141C", 
-               "#DDCC77")
+# Best Sub-sampling Method : `r params$Model_Path`
 
-Final_Data<-rbind(cbind(Data="Identical r0",Final_Data_Identical_r0),
-                  cbind(Data="Non Identical r0",Final_Data_Non_Identical_r0))
+# Compare SMSE, EMSE, Variance, Information and Bias for all methods.
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+```{r Compare All,fig.width=20,fig.height=12}
+All_Bias %>% 
+  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p1
+  ylab("Bias")+ggtitle("Bias")->p1
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+All_MSE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p2
+  ylab("MSE")+ggtitle("MSE")->p2
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+All_MSE_MLE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p3
+  ylab("MSE")+ggtitle("MSE for MLE")->p7
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+All_EMSE %>%
+  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p4
+  ylab("EMSE")+ggtitle("EMSE")->p3
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+All_VAR %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p5
+  ylab("Variance")+ggtitle("Variance")->p4
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+All_Info %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p6
+  ylab("Information")+ggtitle("Information")->p5
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+All_ACC %>%
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p7
+  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE"),] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p8
-
-ggarrange(p1,p2,p3,p4,nrow = 4)
-ggarrange(p5,p6,nrow = 2)
-ggarrange(p7,p8,nrow = 2)
+ggarrange(p7,p2,p1,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 4)
 ```
 
-```{r Identical r0 Plots with gg.gap,fig.height=4}
-SS_Choice<-100*c(10:15)
+# Special Comparison of SMSE, EMSE, Variance, Information and Bias for mMSE.
+## (Real Model and Assumed Model results with Full Data Real Model)
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+```{r Special Compare 1,fig.width=20,fig.height=12}
+SP_All_mMSE_Bias %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p1_New
+  ylab("Bias")+ggtitle("Bias")->p1
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+SP_All_mMSE_MSE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p2_New
+  ylab("MSE")+ggtitle("MSE")->p2
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+SP_All_mMSE_MSE_MLE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p3_New
+  ylab("MSE")+ggtitle("MSE for MLE")->p7
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+SP_All_mMSE_EMSE %>%
+  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p4_New
+  ylab("EMSE")+ggtitle("EMSE")->p3
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+SP_All_mMSE_VAR %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p5_New
+  ylab("Variance")+ggtitle("Variance")->p4
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+SP_All_mMSE_Info %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p6_New
+  ylab("Information")+ggtitle("Information")->p5
 
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+SP_All_mMSE_ACC %>%
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
   theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p7_New
+  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
 
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p8_New
-
+ggarrange(p7,p2,p1,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 4)
 ```
 
-```{r All Plots}
-ggarrange(p1,p1_New,
-          p2,p2_New,nrow = 4)
+# Compare  SMSE, EMSE, Variance, Information and Bias for mVc.
+## (Real Model and Assumed Model results with Full Data Real Model)
 
-ggarrange(p5_New,p6_New,nrow = 2)
-ggarrange(p7_New,p8_New,nrow = 2)
+```{r Special Compare 2,fig.width=20,fig.height=12}
+SP_All_mVc_Bias %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Bias")+ggtitle("Bias")->p1
+
+SP_All_mVc_MSE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("MSE")+ggtitle("MSE")->p2
+
+SP_All_mVc_MSE_MLE %>%
+  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("MSE")+ggtitle("MSE for MLE")->p7
+
+SP_All_mVc_EMSE %>%
+  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("EMSE")+ggtitle("EMSE")->p3
+
+SP_All_mVc_VAR %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Variance")+ggtitle("Variance")->p4
+
+SP_All_mVc_Info %>%
+  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Information")+ggtitle("Information")->p5
+
+SP_All_mVc_ACC %>%
+  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
+  geom_point()+geom_line()+scale_colour_viridis_d()+
+  theme_light()+xlab("Sub sample size")+
+  ylab("Average Accuracy")+ggtitle("Accuracy")->p6
+
+ggarrange(p7,p2,p1,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 4)
 ```

### 2023-02-12 Non_Identical_r0/Rmarkdown/r1_OSMAC_Method.Rmd
Non identical related files updated after increasing r0 values and MSE for MLE

--- 2023-02-12 Non_Identical_r0/Rmarkdown/OSMAC_Method.Rmd
@@
 Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Real_Model/")
-load(here(Path,"OSMAC_output.RData"))
+load(here(Path,"OSMAC_output_r1.RData"))
 
@@
 Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_1/")
-load(here(Path,"OSMAC_output.RData"))
+load(here(Path,"OSMAC_output_r1.RData"))
 
@@
 Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_2/")
-load(here(Path,"OSMAC_output.RData"))
+load(here(Path,"OSMAC_output_r1.RData"))
 
@@
 Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC","Assumed_Model_3/")
-load(here(Path,"OSMAC_output.RData"))
+load(here(Path,"OSMAC_output_r1.RData"))
 
@@
 
-anim_save(filename="para_1.gif",animation = para_1,
+anim_save(filename="r1_para_1.gif",animation = para_1,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","para_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_para_1.gif"))
 ```
@@
 
-anim_save(filename="Bias_1.gif",animation = Bias_1,
+anim_save(filename="r1_Bias_1.gif",animation = Bias_1,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","Bias_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_Bias_1.gif"))
 ```
@@
 
-anim_save(filename="U_1.gif",animation = U_1,
+anim_save(filename="r1_U_1.gif",animation = U_1,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_U_1.gif"))
 
@@
 
-anim_save(filename="U_2.gif",animation = U_2,
+anim_save(filename="r1_U_2.gif",animation = U_2,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","U_2.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC","Plots","r1_U_2.gif"))
 ```
@@
      file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-                 "No_Correlated_Covariate_OSMAC.RData"))
+                 "No_Correlated_Covariate_OSMAC_r1.RData"))
 ```

### 2023-02-12 Non_Identical_r0/Rmarkdown/r1_OSMAC_Model_Free_Method.Rmd
Non identical related files updated after increasing r0 values and MSE for MLE

--- 2023-02-12 Non_Identical_r0/Rmarkdown/OSMAC_Model_Free_Method.Rmd
@@
 Path<-here("Non_Identical_r0","Outputs",params$Model_Path,"OSMAC_Model_Free/")
-load(here(Path,"OSMAC_MF_output.RData"))
+load(here(Path,"OSMAC_MF_output_r1.RData"))
 
@@
 
-anim_save(filename="para_1.gif",animation = para_1,
+anim_save(filename="r1_para_1.gif",animation = para_1,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","para_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","r1_para_1.gif"))
 ```
@@
 
-anim_save(filename="Bias_1.gif",animation = Bias_1,
+anim_save(filename="r1_Bias_1.gif",animation = Bias_1,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","Bias_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","r1_Bias_1.gif"))
 ```
@@
 
-anim_save(filename="U_1.gif",animation = U_1,
+anim_save(filename="r1_U_1.gif",animation = U_1,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","U_1.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","r1_U_1.gif"))
 
@@
 
-anim_save(filename="U_2.gif",animation = U_2,
+anim_save(filename="r1_U_2.gif",animation = U_2,
           path=here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots"))
 
-include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","U_2.gif"))
+include_graphics2(here("Non_Identical_r0","htmloutputs",params$Model_Path,"OSMAC_Model_Free","Plots","r1_U_2.gif"))
 ```
@@
      file = here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-                 "No_Correlated_Covariate_OSMAC_MF.RData"))
+                 "No_Correlated_Covariate_OSMAC_MF_r1.RData"))
 

### 2023-02-12 Non_Identical_r0/Rmarkdown/Random_Sampling_And_OSMAC.R

@@ -1,34 +1,42 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
-         "Model_3","Model_4") ; j=4
+         "Model_3","Model_4") ; j=1
 
 for (j in 1:length(Model)) 
 {
   # Random Sampling ----
-  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Random_Sampling.Rmd"),
-         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"Random_Sampling"),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[j]),
-         verbose = TRUE,keep_md = FALSE)
-  #open_output_dir()
+  render(input = here("Non_Identical_r0","Rmarkdown","Random_Sampling.Rmd"),
+         output_format = "html_document",
+         output_file = "Random_Sampling",
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"Random_Sampling"),
+         params = list("Model_Path"=Model[j]))
   
   # OSMAC Method ----
-  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
-         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[j]),
-         verbose = TRUE,keep_md = FALSE)
-  #open_output_dir()
+  render(input = here("Non_Identical_r0","Rmarkdown","OSMAC_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "OSMAC_Method",
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
+         params = list("Model_Path"=Model[j]))
+  
+  render(input = here("Non_Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "r1_OSMAC_Method",
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
+         params = list("Model_Path"=Model[j]))
   
   # OSMAC Model Free Method ----
-  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Model_Free_Method.Rmd"),
[…]

### 2023-02-12 Non_Identical_r0/Rmarkdown/Summary/Summary_Rmarkdown.R

@@ -1,5 +1,4 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
@@ -8,11 +7,16 @@ Model<-c("Model_1","Model_2",
 # Best_Subsampling_Method ----
 for (i in 1:length(Model))
 {
-  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Summary","Best_Subsampling_Method.Rmd"),
-         out_dir=here("Non_Identical_r0","Summary","Classical",Model[i],"Best_Subsampling"),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[i]),
-         verbose = TRUE,keep_md = FALSE)
-  #open_output_dir()
+  # render(input=here("Non_Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "Best_Subsampling_Method",
+  #        output_dir=here("Non_Identical_r0","Summary",Model[i],"Best_Subsampling"),
+  #        params=list("Model_Path"=Model[i]))
+  
+  render(input=here("Non_Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "r1_Best_Subsampling_Method",
+         output_dir=here("Non_Identical_r0","Summary",Model[i],"Best_Subsampling"),
+         params=list("Model_Path"=Model[i]))
 }
 

### 2023-02-12 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC/r1_Simulation_Results_OSMAC_Sampling.R

@@ -1,0 +1,48 @@
+# Run for OSMAC Sampling----
+library(compiler)
+library(here)
+library(LaplacesDemon)
+
+enableJIT(1)
+
+# Load the No Correlated Data----
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","Init.RData"))
+
+# Load the OSMAC Sample----
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","r1_Run_OSMAC.RData"))
+
+# Real Model ----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
+                           Y=as.matrix(Simulated_Data[[2]]$Real_Model[,1]),
+                           X=as.matrix(Simulated_Data[[2]]$Real_Model[,-1]),
+                           Real_Data=as.matrix(Simulated_Data[[2]]$Real_Model),
+                           N=Simulated_Data$Basic$N,Model="Real_Model")
+
+# Assumed Model 1 ----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
+                           Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,1]),
+                           X=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,-1]),
+                           Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1")
+
+# Assumed Model 2 ----
+# Generate for Random sample of 1000 different times ---
+## Pi=MMSE and Pi=MVC Proportional probabilities ---
+Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
+                           Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,1]),
+                           X=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,-1]),
+                           Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_2")
+
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC_Model_Free/Simulation_Results_OSMAC_Sampling.R

@@ -6,10 +6,10 @@ library(LaplacesDemon)
 enableJIT(1)
 
 # Load the No Correlated Data----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC_Model_Free","Init.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC_Model_Free","Init.RData"))
 
 # Load the OSMAC Sample----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC_Model_Free","Run_OSMAC.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC_Model_Free","Run_OSMAC.RData"))
 
 All_Covariates<-c("X0","X1","X2","X1^2","X2^2")
 

### 2023-02-12 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC_Model_Free/r1_Simulation_Results_OSMAC_Sampling.R

@@ -1,0 +1,88 @@
+# Run for OSMAC Sampling----
+library(compiler)
+library(here)
+library(LaplacesDemon)
+
+enableJIT(1)
+
+# Load the No Correlated Data----
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC_Model_Free","Init.RData"))
+
+# Load the OSMAC Sample----
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC_Model_Free","r1_Run_OSMAC.RData"))
+
+All_Covariates<-c("X0","X1","X2","X1^2","X2^2")
+
+# Model 1 ----
+
+if(Model_Path=="Model_1")
+{
+  combs<-list(All_Covariates[-c(4,5)],
+              All_Covariates[-5],
+              All_Covariates[-4],
+              All_Covariates)
+  
+  # Generate for Random sample of 1000 different times ----
+  ## Pi=MMSE and Pi=MVC Proportional probabilities ---
+  Final_Parameter<-Run_OSMAC_MF(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
+                                Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                                X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                                alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
+                                All_Covariates=All_Covariates,
+                                combs=combs)
+}
+
+# Model 2 ----
+
+if(Model_Path=="Model_2")
+{
+  combs<-list(All_Covariates[-5],
+              All_Covariates[-c(4,5)],
+              All_Covariates[-4],
+              All_Covariates)
+  
+  # Generate for Random sample of 1000 different times ----
+  ## Pi=MMSE and Pi=MVC Proportional probabilities ---
+  Final_Parameter<-Run_OSMAC_MF(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
+                                Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
+                                X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
+                                alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
+                                All_Covariates=All_Covariates,
+                                combs=combs)
+}
+
+# Model 3 ----
+if(Model_Path=="Model_3")
+{
+  combs<-list(All_Covariates[-4],
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -38,12 +38,20 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
     #Sample.mMSE<-list()
     #Sample.mVc<-list()
     
-    ## mVC
+    ## mVc
+    PI.mVc <- sqrt((Y - P.prop)^2 * rowSums(X^2))
+    PI.mVc <- PI.mVc / sum(PI.mVc)
+    
+    ## mMSE
+    p.prop <- P.prop[idx.prop]
+    w.prop <- p.prop
+    W.prop <- solve(t(x.prop) %*% (x.prop * w.prop * pinv.prop))
+    PI.mMSE <- sqrt((Y - P.prop)^2 * rowSums((X%*%W.prop)^2))
+    PI.mMSE <- PI.mMSE / sum(PI.mMSE)
+    
     for (i in 1:length(r2)) 
     {
-      PI.mVc <- sqrt((Y - P.prop)^2 * rowSums(X^2))
-      PI.mVc <- PI.mVc / sum(PI.mVc)
-      
+      # mVc
       idx.mVc <- sample(1:n, r2[i]-r1, T, PI.mVc)
       x.mVc <- X[c(idx.mVc, idx.prop),]
       y.mVc <- Y[c(idx.mVc, idx.prop)]
@@ -65,11 +73,6 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       Bias_mVc[i,]<-Cordeiro(XData=x.mVc,With_bias = beta.mVc[i,])
       
       ## mMSE
-      p.prop <- P.prop[idx.prop]
-      w.prop <- p.prop
-      W.prop <- solve(t(x.prop) %*% (x.prop * w.prop * pinv.prop))
-      PI.mMSE <- sqrt((Y - P.prop)^2 * rowSums((X%*%W.prop)^2))
-      PI.mMSE <- PI.mMSE / sum(PI.mMSE)
       idx.mMSE <- sample(1:n, r2[i]-r1, T, PI.mMSE)
       x.mMSE <- X[c(idx.mMSE, idx.prop),]
       y.mMSE <- Y[c(idx.mMSE, idx.prop)]
@@ -97,7 +100,7 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/OSMAC_Algorithm_Model_Free.R

@@ -13,29 +13,27 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two Step OSMAC ----
-OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) {
-  
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) 
+{
   PI.prop <- rep(1/n, n)
   idx.prop <- sample(1:n, r1, T, PI.prop)
   
   y.prop <- Y[idx.prop]
   pinv.prop <- rep(n,r1)
   
-  beta.prop<-list()
-  beta.prop<-lapply(1:length(combs),function(i) {
-    glm(y.prop~X[idx.prop,colnames(X) %in% combs[[i]]]-1, family = "poisson")})
-   
-  for (i in 1:length(combs)) 
+  beta.prop<-lapply(1:length(combs),function(a) {
+    glm(y.prop~X[idx.prop,colnames(X) %in% combs[[a]]]-1, family = "poisson")})
+  
+  for (j in 1:length(combs)) 
   {
-    if (anyNA(beta.prop[[i]]$coefficients))
+    if (anyNA(beta.prop[[j]]$coefficients))
     {
       stop("There are NA or NaN values")
     }
   }
   
-  P.prop<-list()
-  P.prop<-lapply(1:length(combs), function(i)
-    exp(X[,colnames(X) %in% combs[[i]]] %*% beta.prop[[i]]$coefficients))
+  P.prop<-lapply(1:length(combs), function(a)
+    exp(X[,colnames(X) %in% combs[[a]]] %*% beta.prop[[a]]$coefficients))
   
   beta.mVc<-Utility_mVc<-Bias_mVc<-list()
   beta.mMSE<-Utility_mMSE<-Bias_mMSE<-list()
@@ -54,22 +52,36 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) {
   #Sample.mMSE<-list()
   #Sample.mVc<-list()
   
+  ## mVc
+  PI.mVc<-lapply(1:length(combs),function(a){
+    PI.mVc <- sqrt((Y - P.prop[[a]])^2 * rowSums(X[,All_Covariates %in% combs[[a]] ]^2)) #
+    return(PI.mVc / sum(PI.mVc))})
+  
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/OSMAC_Model_Free_Setup.R

@@ -4,7 +4,7 @@ library(LaplacesDemon)
 library(matrixStats)
 
 # Load the OSMAC algorithm
-source(here("Non_Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Model_Free",
+source(here("Non_Identical_r0","Simulation_Setup","R_Scripts","OSMAC_Model_Free",
             "OSMAC_Algorithm_Model_Free.R"))
 
 OSMAC_MF<-cmpfun(OSMAC_MF)
@@ -16,13 +16,13 @@ Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N)
   # From r0 and r conduct OSMAC subsampling for Logistic regression-----
   Parameter_mMSE<-replicate(length(combs),list()) ;
   Parameter_mVc<-replicate(length(combs),list()) ;
-
+  
   Bias_mMSE<-replicate(length(combs),list()) ; 
   Bias_mVc<-replicate(length(combs),list()) ; 
-
+  
   Utility_mMSE<-replicate(length(combs),list()) ; 
   Utility_mVc<-replicate(length(combs),list()) ;
-
+  
   # Sample_mMSE<-replicate(length(combs),list()) ;  
   # Sample_mVc<-replicate(length(combs),list()) ; 
   
@@ -47,12 +47,12 @@ Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N)
         # Sample_mVc[[j]][[i]]<-cbind(i,Results$Sample_mVc[,colnames(Results$Sample_mVc) %in% c("r2","Y","SP",combs[[j]]) ])
         
         colnames(Parameter_mMSE[[j]][[i]])<-colnames(Parameter_mVc[[j]][[i]])<-
-        colnames(Bias_mMSE[[j]][[i]])<-colnames(Bias_mVc[[j]][[i]])<-
+          colnames(Bias_mMSE[[j]][[i]])<-colnames(Bias_mVc[[j]][[i]])<-
           c("Subsample_Size",paste0("Theta",0:(length(combs[[j]])-1)))
-          
+        
         colnames(Utility_mMSE[[j]][[i]])<-colnames(Utility_mVc[[j]][[i]])<-
           c("Subsample_Size",paste0(c("A","D"),"-optimality"))
-          
+        
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/r1_OSMAC_Algorithm_Model_Free.R

@@ -1,0 +1,180 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two Step OSMAC ----
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) 
+{
+  PI.prop <- rep(1/n, n)
+  
+  beta.mVc<-Utility_mVc<-Bias_mVc<-list()
+  beta.mMSE<-Utility_mMSE<-Bias_mMSE<-list()
+  
+  for (a in 1:length(combs)) 
+  {
+    beta.mVc[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]])) #
+    Utility_mVc[[a]]<-matrix(nrow = length(r1),ncol = 3 ) #
+    Bias_mVc[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]])) #
+    
+    beta.mMSE[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]])) #
+    Utility_mMSE[[a]]<-matrix(nrow = length(r1),ncol = 3) #
+    Bias_mMSE[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]]))  #
+  }
+  
+  #Sample.mMSE<-list()
+  #Sample.mVc<-list()
+  
+  for (i in 1:length(r1)) 
+  {
+    idx.prop <- sample(1:n, r1[i], T, PI.prop)
+    
+    y.prop <- Y[idx.prop]
+    pinv.prop <- rep(n,r1[i])
+    
+    beta.prop<-lapply(1:length(combs),function(a) {
+      glm(y.prop~X[idx.prop,colnames(X) %in% combs[[a]]]-1, family = "poisson")})
+    
+    for (j in 1:length(combs)) 
+    {
+      if (anyNA(beta.prop[[j]]$coefficients))
+      {
+        stop("There are NA or NaN values")
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/r1_OSMAC_Model_Free_Setup.R

@@ -1,0 +1,136 @@
+library(here)
+library(compiler)
+library(LaplacesDemon)
+library(matrixStats)
+
+# Load the OSMAC algorithm
+source(here("Non_Identical_r0","Simulation_Setup","R_Scripts","OSMAC_Model_Free",
+            "r1_OSMAC_Algorithm_Model_Free.R"))
+
+OSMAC_MF<-cmpfun(OSMAC_MF)
+Cordeiro<-cmpfun(Cordeiro)
+
+# Using OSMAC to Sub-sample from Big Data----
+Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N)
+{
+  # From r0 and r conduct OSMAC subsampling for Logistic regression-----
+  Parameter_mMSE<-replicate(length(combs),list()) ;
+  Parameter_mVc<-replicate(length(combs),list()) ;
+  
+  Bias_mMSE<-replicate(length(combs),list()) ; 
+  Bias_mVc<-replicate(length(combs),list()) ; 
+  
+  Utility_mMSE<-replicate(length(combs),list()) ; 
+  Utility_mVc<-replicate(length(combs),list()) ;
+  
+  # Sample_mMSE<-replicate(length(combs),list()) ;  
+  # Sample_mVc<-replicate(length(combs),list()) ; 
+  
+  i=1
+  while(i <= Replicates)
+  {
+    tryCatch({
+      Results<-OSMAC_MF(r1,r2,Y,X,n=N,alpha,combs,All_Covariates)
+      
+      for (j in 1:length(combs)) 
+      {
+        Parameter_mMSE[[j]][[i]]<-Results$opt[[j]]$Est_Theta_mMSE
+        Parameter_mVc[[j]][[i]]<-Results$opt[[j]]$Est_Theta_mVc
+        
+        Bias_mMSE[[j]][[i]]<-Results$opt[[j]]$Bias_mMSE
+        Bias_mVc[[j]][[i]]<-Results$opt[[j]]$Bias_mVc
+        
+        Utility_mMSE[[j]][[i]]<-Results$opt[[j]]$Utility_mMSE
+        Utility_mVc[[j]][[i]]<-Results$opt[[j]]$Utility_mVc
+        
+        # Sample_mMSE[[j]][[i]]<-cbind(i,Results$Sample_mMSE[,colnames(Results$Sample_mMSE) %in% c("r2","Y","SP",combs[[j]]) ])
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R

@@ -3,7 +3,7 @@ library(compiler)
 library(LaplacesDemon)
 
 # Load the OSMAC algorithm
-source(here("Non_Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Algorithm.R"))
+source(here("Non_Identical_r0","Simulation_Setup","R_Scripts","OSMAC_Algorithm.R"))
 
 AlgTwoStp<-cmpfun(AlgTwoStp)
 Cordeiro<-cmpfun(Cordeiro)
@@ -14,13 +14,13 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model)
   # From r0 and r conduct OSMAC subsampling for Logistic regression-----
   Parameter_mMSE<-list()
   Parameter_mVc<-list()
-
+  
   Bias_mMSE<-list()
   Bias_mVc<-list()
-
+  
   Utility_mMSE<-list()
   Utility_mVc<-list()
-
+  
   #Sample_mMSE<-list()
   #Sample_mVc<-list()
   i=1
@@ -46,29 +46,29 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model)
     },error=function(e){ i=i})
     
   }
-
+  
   Final_param_mMSE<-do.call(rbind,Parameter_mMSE)
   Final_param_mVc<-do.call(rbind,Parameter_mVc)
-
+  
   Final_bias_mMSE<-do.call(rbind,Bias_mMSE)
   Final_bias_mVc<-do.call(rbind,Bias_mVc)
-
+  
   Final_utility_mMSE<-do.call(rbind,Utility_mMSE)
   Final_utility_mVc<-do.call(rbind,Utility_mVc)
   
   #Final_Sample_mMSE<-do.call(rbind,Sample_mMSE)
   #Final_Sample_mVc<-do.call(rbind,Sample_mVc)
-    
+  
   Results_OSMAC<-list("mMSE_Output"=cbind.data.frame("mMSE",Final_param_mMSE),
                       "mVc_Output"=cbind.data.frame("mVc",Final_param_mVc))
   colnames(Results_OSMAC$mMSE_Output)<-colnames(Results_OSMAC$mVc_Output)<-c("Type","Subsample_Size",
                                                                              paste0("Theta",0:(ncol(Real_Data[,-1])-1)))
-
+  
   Bias_OSMAC<-list("mMSE_Output"=cbind.data.frame("mMSE",Final_bias_mMSE),
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/Random_Sampling_Setup.R

@@ -24,13 +24,13 @@ Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_
   
   All_Parameter<-list()
   Est_Parameter <- matrix(NA,nrow = length(Choices),ncol = ncol(FullData))
-
+  
   All_Bias<-list()
   Bias <- matrix(NA,nrow = length(Choices),ncol = ncol(FullData))
-
+  
   All_optimality<-list()
   optimality <- matrix(NA,nrow = length(Choices),ncol = 3)
-
+  
   Final_Parameter<-Final_optimality<-Final_Bias<-list()
   
   for (k in 1:No_of_Models) 
@@ -68,18 +68,18 @@ Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_
   return(list("EstPar"=Final_Parameter,
               "Utility"=Final_optimality,
               "Bias"=Final_Bias#,"Subsampled_Data"=Final_Sample_RS
-              )
-         )
+  )
+  )
 }
 
 Run_RandomSample<-cmpfun(Run_RandomSample)
 
 #Save the Random Sample function for No Correlated Covariate Data ----
 save(Run_RandomSample,Cordeiro,
-     file=here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling","Run_RandomSample.RData"))
+     file=here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling","Run_RandomSample.RData"))
 
 rm(list = ls())
 
 # Run the Random sampling method ----
-source(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling",
+source(here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling",
             "Simulation_Results_Random_Sampling.R"))

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/Setup_Data.R

@@ -1,18 +1,18 @@
 library(here)
 
-Model_Path<-"Model_1"
+#Model_Path<-"Model_1"
 #Model_Path<-"Model_2"
 #Model_Path<-"Model_3"
-#Model_Path<-"Model_4"
+Model_Path<-"Model_4"
 
-# Random Sampling Data ----
-Base_Path<-"Random_Sampling"
-
-## No Correlated Covariate Data -----
-load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
-save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path"),
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
-                 Base_Path,"Init.RData"))        
+# # Random Sampling Data ----
+# Base_Path<-"Random_Sampling"
+# 
+# ## No Correlated Covariate Data -----
+# load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
+# save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path"),
+#      file = here("Non_Identical_r0","Simulation_Setup","Analysis",
+#                  Base_Path,"Init.RData"))
 
 # OSMAC Data ----
 Base_Path<-"OSMAC"
@@ -20,7 +20,7 @@ Base_Path<-"OSMAC"
 ## No Correlated Covariate Data -----
 load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
 save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis",
                  Base_Path,"Init.RData"))        
 
 remove(Base_Path)
@@ -31,7 +31,7 @@ Base_Path<-"OSMAC_Model_Free"
 ## No Correlated Covariate Data -----
 load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
 save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis",
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Algorithm.R

@@ -1,0 +1,209 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two step OSMAC ----
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
+  if(Model=="Real_Model")
+  {
+    PI.prop <- rep(1/n, n)
+    
+    beta.mVc<-matrix(nrow = length(r1),ncol = ncol(X) )
+    Utility_mVc<-matrix(nrow = length(r1),ncol = 3 )
+    Bias_mVc<-matrix(nrow = length(r1),ncol = ncol(X) )
+    
+    beta.mMSE<-matrix(nrow = length(r1),ncol = ncol(X) )
+    Utility_mMSE<-matrix(nrow = length(r1),ncol = 3 )
+    Bias_mMSE<-matrix(nrow = length(r1),ncol = ncol(X) )
+    
+    #Sample.mMSE<-list()
+    #Sample.mVc<-list()
+    
+    for (i in 1:length(r1)) 
+    {
+      idx.prop <- sample(1:n, r1[i], T, PI.prop)
+      x.prop <- X[idx.prop,]
+      y.prop <- Y[idx.prop]
+      pinv.prop <- rep(n,r1[i])
+      fit.prop <- glm(y.prop~x.prop-1,family = "poisson")
+      beta.prop <- fit.prop$coefficients
+      if (is.na(beta.prop[1]))
+        return(list(opt=NA, msg="first stage not converge"))
+      P.prop  <- exp(X %*% beta.prop)
+      
+      ## mVc
+      PI.mVc <- sqrt((Y - P.prop)^2 * rowSums(X^2))
+      PI.mVc <- PI.mVc / sum(PI.mVc)
+      
+      ## mMSE
[…]

### 2023-02-12 Non_Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Setup.R

@@ -1,0 +1,102 @@
+library(here)
+library(compiler)
+library(LaplacesDemon)
+
+# Load the OSMAC algorithm
+source(here("Non_Identical_r0","Simulation_Setup","R_Scripts","r1_OSMAC_Algorithm.R"))
+
+AlgTwoStp<-cmpfun(AlgTwoStp)
+Cordeiro<-cmpfun(Cordeiro)
+
+# Using OSMAC to Sub-sample from Big Data ----
+Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model)
+{
+  # From r0 and r conduct OSMAC subsampling for Logistic regression-----
+  Parameter_mMSE<-list()
+  Parameter_mVc<-list()
+  
+  Bias_mMSE<-list()
+  Bias_mVc<-list()
+  
+  Utility_mMSE<-list()
+  Utility_mVc<-list()
+  
+  #Sample_mMSE<-list()
+  #Sample_mVc<-list()
+  i=1
+  while(i <= Replicates)
+  {
+    tryCatch({
+      Results<-AlgTwoStp(r1,r2,Y,X,Real_Data,n=N,Model)
+      
+      Parameter_mMSE[[i]]<-Results$opt$Est_Theta_mMSE
+      Parameter_mVc[[i]]<-Results$opt$Est_Theta_mVc
+      
+      Bias_mMSE[[i]]<-Results$opt$Bias_mMSE
+      Bias_mVc[[i]]<-Results$opt$Bias_mVc
+      
+      Utility_mMSE[[i]]<-Results$opt$Utility_mMSE
+      Utility_mVc[[i]]<-Results$opt$Utility_mVc
+      
+      #Sample_mMSE[[i]]<-cbind(i,Results$opt$Sample_mMSE)
+      #Sample_mVc[[i]]<-cbind(i,Results$opt$Sample_mVc)
+      
+      print(i)
+      i<-i+1
+    },error=function(e){ i=i})
+    
+  }
+  
+  Final_param_mMSE<-do.call(rbind,Parameter_mMSE)
+  Final_param_mVc<-do.call(rbind,Parameter_mVc)
+  
+  Final_bias_mMSE<-do.call(rbind,Bias_mMSE)
+  Final_bias_mVc<-do.call(rbind,Bias_mVc)
+  
+  Final_utility_mMSE<-do.call(rbind,Utility_mMSE)
[…]

### 2023-02-12 Articles.Rmd
article plots location changed

@@
 
+LineType_mMSE<-c("twodash", 
+                 "dashed",
+                 "dotted","dotted","dotted",
+                 "solid")
+
 Selected_Models_mVc<-c("Random Sampling: Data Model",
@@
 
+LineType_mVc<-c("twodash", 
+                "dashed",
+                "dotted","dotted","dotted",
+                "solid")
+
 Theme_special<-function()
 {
-  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
+  theme(legend.key.width=unit(1.2,"cm"),
+        axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
         axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  #geom_point(size=1.75)+
+  geom_line(size=1)+
   scale_color_manual(values=Colors_mMSE)+
+  scale_linetype_manual(values=LineType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+  #geom_point(size=1.75)+
+  geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  scale_linetype_manual(values=LineType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   scale_color_manual(values=Colors_mMSE)+
+  scale_linetype_manual(values=LineType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   scale_color_manual(values=Colors_mVc)+
+  scale_linetype_manual(values=LineType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggsave(filename = "SMSE_MI_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mMSE.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-  ggsave(filename = "SMSE_MI_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mVc.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggsave(filename = "ACCURACY_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mMSE.eps"),device="eps",dpi=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggsave(filename = "ACCURACY_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mVc.eps"),device="eps",dpi=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mMSE.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mMSE.eps"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Uni_mVc.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mVc.eps"),res=300,width = 12,height = 12)
 ```

### 2023-02-12 r1_Articles.Rmd
article plots location changed

@@
 
+LineType_mMSE<-c("dashed",
+                 "dotted","dotted","dotted",
+                 "solid")
+
 Selected_Models_mVc<-c("Optimal subsampling mVc: Data Model",
@@
 
+LineType_mVc<-c("dashed",
+                "dotted","dotted","dotted",
+                "solid")
+
 Theme_special<-function()
 {
-  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
+  theme(legend.key.width=unit(1.2,"cm"),
+        axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
         axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
@@
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "r1_SMSE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "r1_SMSE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "r1_ACCURACY_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "r1_ACCURACY_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggsave(filename = "r1_SMSE_MI_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Uni_mMSE.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-  ggsave(filename = "r1_SMSE_MI_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Uni_mVc.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggsave(filename = "r1_ACCURACY_PR_TV_Uni_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Uni_mMSE.eps"),device="eps",dpi=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggsave(filename = "r1_ACCURACY_PR_TV_Uni_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Uni_mVc.eps"),device="eps",dpi=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mMSE.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Uni_mMSE.eps"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Uni_mVc.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Uni_mVc.eps"),res=300,width = 12,height = 12)
 ```

### 2023-02-15 Articles.Rmd
complex models included in the plots for articles rmarkdown

@@
 Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
-New_Labels<-c("DM",paste0("AM ",1:3))
+New_Labels<-c("DM",paste0("AM ",1:2), "CM")
 
@@
 Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
-New_Labels<-c("DM",paste0("AM ",1:3),"MR")
+New_Labels<-c("DM",paste0("AM ",1:2), "CM","MR")
 
@@
 Identical_ro$Model<-factor(Identical_ro$Model,
-                           levels = c("RS DM","RS AM 1","RS AM 2","RS AM 3",
-                                      "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
+                           levels = c("RS DM","RS AM 1","RS AM 2","RS AM 3","RS CM",
+                                      "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3","mMSE CM",
+                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3","mVc CM",
                                       "mMSE MR","mVc MR"))
@@
                                   `RS AM 3`="Random Sampling: Incorrect Model 3",
+                                  `RS CM` = "Random Sampling: Complex Model",
                                   `mMSE DM`="Optimal subsampling mMSE: Data Model",
@@
                                   `mMSE AM 3`="Optimal subsampling mMSE: Incorrect Model 3",
+                                  `mMSE CM` = "Optimal subsampling mMSE: Complex Model",
                                   `mVc DM`="Optimal subsampling mVc: Data Model",
@@
                                   `mVc AM 3`="Optimal subsampling mVc: Incorrect Model 3",
+                                  `mVc CM`="Optimal subsampling mVc: Complex Model",
                                   `mMSE MR`="Model Robust subsampling mMSE: Data Model",
@@
                         "Optimal subsampling mMSE: Incorrect Model 3",
+                        "Optimal subsampling mMSE: Complex Model",
                         "Model Robust subsampling mMSE: Data Model")
@@
               "#cc0000", 
-              "#ff578a","#ff578a","#ff578a",
+              "#ff578a","#ff578a","#ff578a","#603BDE",
               "darkgreen")
@@
                  "dashed",
-                 "dotted","dotted","dotted",
+                 "dotted","dotted","dotted","dotdash",
                  "solid")
+
+ShapeType_mMSE<-c(16,
+                  1,
+                  4,4,4,3,
+                  8)
 
@@
                        "Optimal subsampling mVc: Incorrect Model 3",
+                       "Optimal subsampling mVc: Complex Model",
                        "Model Robust subsampling mVc: Data Model")
@@
                 "dashed",
-                "dotted","dotted","dotted",
+                "dotted","dotted","dotted","dotdash",
                 "solid")
+
+ShapeType_mVc<-c(16,
+                 1,
+                 4,4,4,3,
+                 8)
 
@@
 {
-  theme(legend.key.width=unit(1.2,"cm"),
+  theme(legend.key.width=unit(1,"cm"),
         axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  #geom_point(size=1.75)+
-  geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE
+  theme_bw()+guides(colour = guide_legend(nrow = 3))+Theme_special()->Temp_plot_mMSE
 
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  #geom_point(size=1.75)+
-  geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc
+  theme_bw()+guides(colour = guide_legend(nrow = 3))+Theme_special()->Temp_plot_mVc
 
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+

### 2023-02-15 r1_Articles.Rmd
complex models included in the plots for articles rmarkdown

@@
 Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
-New_Labels<-c("DM",paste0("AM ",1:3),"MR")
+New_Labels<-c("DM",paste0("AM ",1:2),"CM","MR")
 
@@
 Identical_ro$Model<-factor(Identical_ro$Model,
-                           levels = c("mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
+                           levels = c("mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3","mMSE CM",
+                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3","mVc CM",
                                       "mMSE MR","mVc MR"))
@@
 Colors_mMSE<-c("#cc0000", 
-               "#ff578a","#ff578a","#ff578a",
+               "#ff578a","#ff578a","#ff578a","#603BDE",
                "darkgreen")
@@
 LineType_mMSE<-c("dashed",
-                 "dotted","dotted","dotted",
+                 "dotted","dotted","dotted","dotdash",
                  "solid")
+
+ShapeType_mMSE<-c(1,
+                  4,4,4,3,
+                  8)
 
@@
 Colors_mVc<-c("#cc0000", 
-              "#ff578a","#ff578a","#ff578a",
+              "#ff578a","#ff578a","#ff578a","#603BDE",
               "darkgreen")
@@
 LineType_mVc<-c("dashed",
-                "dotted","dotted","dotted",
+                "dotted","dotted","dotted","dotdash",
                 "solid")
+
+ShapeType_mVc<-c(1,
+                 4,4,4,3,
+                 8)
 

### 2023-02-16 Articles.Rmd
facet and x axis corrected

@@
                                           "Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",
-                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"))
+                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"),
+                               labels = c(expression("Data Model: "*X[1]*", "*X[2]),
+                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[1]^{2}),
+                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[2]^{2}),
+                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[1]^{2}*", "*X[2]^{2})))
 
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
   xlab("r")+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
   xlab("r")+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
   xlab("r")+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
   xlab("r")+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
   xlab("r")+

### 2023-02-16 r1_Articles.Rmd
facet and x axis corrected

@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average Model Information)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average Model Information)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(SMSE)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(SMSE)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+

### 2023-02-18 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R
New Probabilities updated correctly

@@ -89,18 +89,18 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
       
       Bias_Assumed_Old_mMSE_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mMSE
       Bias_Assumed_Old_mVc_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mVc
-      Bias_Assumed_New_mMSE_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mMSE
-      Bias_Assumed_New_mVc_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mVc
+      Bias_Assumed_New_mMSE_1[[i]]<-Results$opt$opt_New$opt_New_1$Bias_mMSE
+      Bias_Assumed_New_mVc_1[[i]]<-Results$opt$opt_New$opt_New_1$Bias_mVc
       
       Bias_Assumed_Old_mMSE_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mMSE
       Bias_Assumed_Old_mVc_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mVc
-      Bias_Assumed_New_mMSE_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mMSE
-      Bias_Assumed_New_mVc_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mVc
+      Bias_Assumed_New_mMSE_2[[i]]<-Results$opt$opt_New$opt_New_2$Bias_mMSE
+      Bias_Assumed_New_mVc_2[[i]]<-Results$opt$opt_New$opt_New_2$Bias_mVc
       
       Bias_Assumed_Old_mMSE_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mMSE
       Bias_Assumed_Old_mVc_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mVc
-      Bias_Assumed_New_mMSE_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mMSE
-      Bias_Assumed_New_mVc_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mVc
+      Bias_Assumed_New_mMSE_3[[i]]<-Results$opt$opt_New$opt_New_3$Bias_mMSE
[…]

### 2023-02-18 Non_Identical_r0/Simulation_Setup/Analysis/Random_Sampling/Simulation_Results_Random_Sampling.R
Classical removed from the chain folder Random Sampling

@@ -6,10 +6,10 @@ library(LaplacesDemon)
 enableJIT(1)
 
 # Load the No Correlated Data----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling","Init.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling","Init.RData"))
 
 # Load the Random Sample----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling","Run_RandomSample.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling","Run_RandomSample.RData"))
 
 # Real Model ----
 # Generate for Random sample of 1000 different times
@@ -26,11 +26,11 @@ Bias_RandomSample<-Final_Parameter$Bias[[1]]
 
 # Save the Results ----
 save(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample,#SelectedData_RandomSample,
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling",
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling",
                  "Results","Real_Model","Random_Sample_output.RData"))
 
 save(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample,#SelectedData_RandomSample,
-     file = here("Non_Identical_r0","Outputs","Classical",Model_Path,"Random_Sampling",
+     file = here("Non_Identical_r0","Outputs",Model_Path,"Random_Sampling",
                  "Real_Model","Random_Sample_output.RData"))
 
 # Assumed Model 1----
@@ -42,11 +42,11 @@ Bias_RandomSample<-Final_Parameter$Bias[[2]]
 
 # Save the Results ---
 save(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample,#SelectedData_RandomSample,
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling",
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling",
                  "Results","Assumed_Model_1","Random_Sample_output.RData"))
 
 save(Est_Param_RandomSample,Utility_RandomSample,Bias_RandomSample,#SelectedData_RandomSample,
[…]

### 2023-02-24 Non_Identical_r0/Rmarkdown/r1_OSMAC_Method.Rmd
Model Information updated throughout the project

@@
 library(data.table)
+library(ggpubr)
 

### 2023-02-24 Identical_r0/Rmarkdown/OSMAC_Command.R

@@ -4,7 +4,7 @@ library(rmarkdown)
 Model<-c("Model_1","Model_2",
          "Model_3","Model_4") ; j=4
 
-for (j in 1:length(Model)) 
+#for (j in 1:length(Model)) 
 {
   # OSMAC Method ----
   render(input=here("Identical_r0","Rmarkdown","OSMAC_Method.Rmd"),
@@ -13,10 +13,10 @@ for (j in 1:length(Model))
          output_dir=here("Identical_r0","htmloutputs",Model[j],"OSMAC"),
          params=list("Model_Path"=Model[j]))
   
-  render(input=here("Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
-         output_format = "html_document",
-         output_file = "r1_OSMAC_Method",
-         output_dir=here("Identical_r0","htmloutputs",Model[j],"OSMAC"),
-         params=list("Model_Path"=Model[j]))
+  # render(input=here("Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_OSMAC_Method",
+  #        output_dir=here("Identical_r0","htmloutputs",Model[j],"OSMAC"),
+  #        params=list("Model_Path"=Model[j]))
 }
 

### 2023-02-24 Identical_r0/Rmarkdown/Summary/Summary_Rmarkdown.R

@@ -5,7 +5,7 @@ Model<-c("Model_1","Model_2",
          "Model_3","Model_4"); i=4
 
 # Best_Subsampling_Method ----
-for (i in 1:length(Model))
+#for (i in 1:length(Model))
 {
   render(input=here("Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
          output_format = "html_document",

### 2023-02-24 Identical_r0/Simulation_Setup/Analysis/OSMAC/Simulation_Results_OSMAC_Sampling.R

@@ -31,7 +31,8 @@ if(Model_Path=="Model_1")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,
+                             Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 2----
@@ -50,7 +51,8 @@ if(Model_Path=="Model_2")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,
+                             Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 3----
@@ -69,7 +71,8 @@ if(Model_Path=="Model_3")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,
+                             Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 4----
@@ -88,5 +91,6 @@ if(Model_Path=="Model_4")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,
+                             Theta=Simulated_Data$Basic$Theta)
 }

### 2023-02-24 Identical_r0/Simulation_Setup/Analysis/OSMAC/r1_Simulation_Results_OSMAC_Sampling.R

@@ -31,7 +31,7 @@ if(Model_Path=="Model_1")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 2----
@@ -50,7 +50,7 @@ if(Model_Path=="Model_2")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 3----
@@ -69,7 +69,7 @@ if(Model_Path=="Model_3")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 4----
@@ -88,5 +88,5 @@ if(Model_Path=="Model_4")
                              N = Simulated_Data$Basic$N,
                              alpha = rep(1/4,length(combs)+1),
                              combs = combs,
-                             All_Covariates = All_Covariates)
+                             All_Covariates = All_Covariates,Theta=Simulated_Data$Basic$Theta)
 }

### 2023-02-24 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two step OSMAC ----
-AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates,Theta){
   Y_Real<-Real_Data[,1] #  Real Data
   X_Real<-Real_Data[,-1] # Real Data
   
@@ -249,7 +249,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
     V_Temp<-t(x_Real.mVc)%*% (x_Real.mVc * ((as.vector(y_Real.mVc)-pi)* pinv_Real.mVc)^2)   
     V_Final<-Mx %*% V_Temp %*% Mx
     
-    Utility_mVc_Real[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+    pi_1<- c(exp(x_Real.mVc %*% Theta))
+    Mx_1<-t(x_Real.mVc) %*% (x_Real.mVc * pi_1) 
+    
+    Utility_mVc_Real[i,]<-cbind(r2[i],tr(V_Final),det(Mx_1))
     Bias_mVc_Real[i,]<-Cordeiro(XData=x_Real.mVc,With_bias = beta.mVc_Real[i,])
     
     # Assumed Data Old probabilities
@@ -302,9 +305,17 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
       Mx[[a]] %*% V_Temp[[a]] %*% Mx[[a]]
     }) 
     
+    pi_1<- lapply(1:length(combs),function(a){
+      c(exp(x_Assumed.mVc[[a]] %*% Theta))
+    })
+    
+    Mx_1<-lapply(1:length(combs),function(a){
+      t(x_Assumed.mVc[[a]]) %*% (x_Assumed.mVc[[a]] * pi_1[[a]])
+    })
+    
     for (j in 1:length(combs)) 
     {
-      Utility_mVc_New[[j]][i,]<-cbind(r2[i],tr(V_Final[[j]]),det(solve(V_Final[[j]])))
[…]

### 2023-02-24 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R

@@ -9,7 +9,7 @@ AlgTwoStp<-cmpfun(AlgTwoStp)
 Cordeiro<-cmpfun(Cordeiro)
 
 # Using OSMAC to Sub-sample from Big Data ----
-Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
+Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates,Theta)
 {
   X_Real<-Real_Data[,-1]
   # From r0 and r conduct OSMAC subsampling for Logistic regression-----
@@ -60,7 +60,7 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
   while(i <= Replicates)
   {
     tryCatch({
-      Results<-AlgTwoStp(r1,r2,Y,X,n=N,Real_Data,alpha,combs,All_Covariates)
+      Results<-AlgTwoStp(r1,r2,Y,X,n=N,Real_Data,alpha,combs,All_Covariates,Theta)
       
       Parameter_Real_mMSE[[i]]<-Results$opt$opt_Real$Est_Theta_mMSE
       Parameter_Real_mVc[[i]]<-Results$opt$opt_Real$Est_Theta_mVc

### 2023-02-24 Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Algorithm.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two step OSMAC ----
-AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates,Theta){
   Y_Real<-Real_Data[,1] #  Real Data
   X_Real<-Real_Data[,-1] # Real Data
   
@@ -121,7 +121,6 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
       exp(X[,All_Covariates %in% combs[[a]] ] %*% beta.prop[[a]]) # Assumed Data
     })
     P_Real.prop  <- exp(X_Real %*% beta_Real.prop) # Real Data
-    
     
     ## mVc
     PI_Real.mVc <- sqrt((Y - P_Real.prop)^2 * rowSums(X_Real^2)) # Real Data
@@ -251,7 +250,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
     V_Temp<-t(x_Real.mVc)%*% (x_Real.mVc * ((as.vector(y_Real.mVc)-pi)* pinv_Real.mVc)^2)   
     V_Final<-Mx %*% V_Temp %*% Mx
     
-    Utility_mVc_Real[i,]<-cbind(r1[i],tr(V_Final),det(solve(V_Final)))
+    pi_1<- c(exp(x_Real.mVc %*% Theta))
+    Mx_1<- t(x_Real.mVc) %*% (x_Real.mVc * pi_1)
+    
+    Utility_mVc_Real[i,]<-cbind(r1[i],tr(V_Final),det(Mx_1))
     Bias_mVc_Real[i,]<-Cordeiro(XData=x_Real.mVc,With_bias = beta.mVc_Real[i,])
     
     # Assumed Data Old probabilities
@@ -276,9 +278,17 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
       Mx[[a]] %*% V_Temp[[a]] %*% Mx[[a]]
     }) 
     
[…]

### 2023-02-24 Non_Identical_r0/Rmarkdown/Random_Sampling_And_OSMAC.R

@@ -2,9 +2,9 @@ library(here)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
-         "Model_3","Model_4") ; j=1
+         "Model_3","Model_4") ; j=4
 
-for (j in 1:length(Model)) 
+#for (j in 1:length(Model)) 
 {
   # Random Sampling ----
   render(input = here("Non_Identical_r0","Rmarkdown","Random_Sampling.Rmd"),
@@ -12,7 +12,7 @@ for (j in 1:length(Model))
          output_file = "Random_Sampling",
          output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"Random_Sampling"),
          params = list("Model_Path"=Model[j]))
-  
+
   # OSMAC Method ----
   render(input = here("Non_Identical_r0","Rmarkdown","OSMAC_Method.Rmd"),
          output_format = "html_document",
@@ -20,11 +20,11 @@ for (j in 1:length(Model))
          output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
          params = list("Model_Path"=Model[j]))
   
-  render(input = here("Non_Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
-         output_format = "html_document",
-         output_file = "r1_OSMAC_Method",
-         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
-         params = list("Model_Path"=Model[j]))
+  # render(input = here("Non_Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_OSMAC_Method",
+  #        output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
+  #        params = list("Model_Path"=Model[j]))
   
   # OSMAC Model Free Method ----
   render(input = here("Non_Identical_r0","Rmarkdown","OSMAC_Model_Free_Method.Rmd"),
@@ -33,10 +33,10 @@ for (j in 1:length(Model))
          output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC_Model_Free"),
          params = list("Model_Path"=Model[j]))
   
-  render(input = here("Non_Identical_r0","Rmarkdown","r1_OSMAC_Model_Free_Method.Rmd"),
-         output_format = "html_document",
[…]

### 2023-02-24 Non_Identical_r0/Rmarkdown/Summary/Summary_Rmarkdown.R

@@ -5,18 +5,18 @@ Model<-c("Model_1","Model_2",
          "Model_3","Model_4"); i=4
 
 # Best_Subsampling_Method ----
-for (i in 1:length(Model))
+#for (i in 1:length(Model))
 {
-  # render(input=here("Non_Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
-  #        output_format = "html_document",
-  #        output_file = "Best_Subsampling_Method",
-  #        output_dir=here("Non_Identical_r0","Summary",Model[i],"Best_Subsampling"),
-  #        params=list("Model_Path"=Model[i]))
-  
-  render(input=here("Non_Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+  render(input=here("Non_Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
          output_format = "html_document",
-         output_file = "r1_Best_Subsampling_Method",
+         output_file = "Best_Subsampling_Method",
          output_dir=here("Non_Identical_r0","Summary",Model[i],"Best_Subsampling"),
          params=list("Model_Path"=Model[i]))
+  
+  # render(input=here("Non_Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_Best_Subsampling_Method",
+  #        output_dir=here("Non_Identical_r0","Summary",Model[i],"Best_Subsampling"),
+  #        params=list("Model_Path"=Model[i]))
 }
 

### 2023-02-24 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC/Simulation_Results_OSMAC_Sampling.R

@@ -6,10 +6,10 @@ library(LaplacesDemon)
 enableJIT(1)
 
 # Load the No Correlated Data----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Init.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","Init.RData"))
 
 # Load the OSMAC Sample----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Run_OSMAC.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","Run_OSMAC.RData"))
 
 # Real Model ----
 # Generate for Random sample of 1000 different times ---
@@ -18,7 +18,8 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
                            Y=as.matrix(Simulated_Data[[2]]$Real_Model[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Real_Model[,-1]),
                            Real_Data=as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N,Model="Real_Model")
+                           N=Simulated_Data$Basic$N,Model="Real_Model",
+                           Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 1 ----
 # Generate for Random sample of 1000 different times ---
@@ -27,7 +28,8 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
                            Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,-1]),
                            Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1")
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1",
+                           Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 2 ----
 # Generate for Random sample of 1000 different times ---
@@ -36,7 +38,8 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
                            Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,1]),
[…]

### 2023-02-24 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC/r1_Simulation_Results_OSMAC_Sampling.R

@@ -18,7 +18,7 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
                            Y=as.matrix(Simulated_Data[[2]]$Real_Model[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Real_Model[,-1]),
                            Real_Data=as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N,Model="Real_Model")
+                           N=Simulated_Data$Basic$N,Model="Real_Model",Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 1 ----
 # Generate for Random sample of 1000 different times ---
@@ -27,7 +27,7 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
                            Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,-1]),
                            Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1")
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1",Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 2 ----
 # Generate for Random sample of 1000 different times ---
@@ -36,7 +36,7 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
                            Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,-1]),
                            Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N, Model="Assumed_Model_2")
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_2",Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 3 ----
 # Generate for Random sample of 1000 different times ---
@@ -45,4 +45,4 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=c(100*(1:9)),r2=1000,
                            Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,1]),
[…]

### 2023-02-24 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC_Model_Free/Simulation_Results_OSMAC_Sampling.R

@@ -29,7 +29,7 @@ if(Model_Path=="Model_1")
                                 X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 2 ----
@@ -48,7 +48,7 @@ if(Model_Path=="Model_2")
                                 X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 3 ----
@@ -66,7 +66,7 @@ if(Model_Path=="Model_3")
                                 X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 4 ----
@@ -84,5 +84,5 @@ if(Model_Path=="Model_4")
                                 X=as.matrix(Simulated_Data[[2]]$Real_Model[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,Theta=Simulated_Data$Basic$Theta)
 }

### 2023-02-24 Non_Identical_r0/Simulation_Setup/Analysis/Random_Sampling/Simulation_Results_Random_Sampling.R

@@ -17,7 +17,7 @@ Final_Parameter<-Run_RandomSample(Replicates = Replicates,
                                   FullData = Simulated_Data[[2]]$Real_Model,
                                   N=Simulated_Data$Basic$N,
                                   Subsample_Size=Subsample_Size,Choices=c(100*(2:15)),
-                                  No_of_Models = 4)
+                                  No_of_Models = 4,Theta=Simulated_Data$Basic$Theta)
 
 Est_Param_RandomSample<-Final_Parameter$EstPar[[1]]
 Utility_RandomSample<-Final_Parameter$Utility[[1]]

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two step OSMAC ----
-AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model,Theta) {
   if(Model=="Real_Model")
   {
     PI.prop <- rep(1/n, n)
@@ -69,7 +69,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mVc[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<- c(exp(x.mVc %*% Theta))
+      Mx_1<-t(x.mVc) %*% (x.mVc * pi_1)
+      
+      Utility_mVc[i,]<-cbind(r2[i],tr(V_Final),det(Mx_1))
       Bias_mVc[i,]<-Cordeiro(XData=x.mVc,With_bias = beta.mVc[i,])
       
       ## mMSE
@@ -90,7 +93,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mMSE[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<-c(exp(x.mMSE %*% Theta))
+      Mx_1<-t(x.mMSE) %*% (x.mMSE * pi_1)
+      
+      Utility_mMSE[i,]<-cbind(r2[i],tr(V_Final),det(Mx_1))
       Bias_mMSE[i,]<-Cordeiro(XData=x.mMSE,With_bias = beta.mMSE[i,])
     }
     
@@ -165,7 +171,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mVc[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<- c(exp(x_Real.mVc %*% Theta))
+      Mx_1<-t(x_Real.mVc) %*% (x_Real.mVc * pi_1)
+      
[…]

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/OSMAC_Algorithm_Model_Free.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two Step OSMAC ----
-OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) 
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates,Theta) 
 {
   PI.prop <- rep(1/n, n)
   idx.prop <- sample(1:n, r1, T, PI.prop)
@@ -111,6 +111,12 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates)
       Utility_mVc[[j]][i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final))) #
     }
     
+    pi_1 <- c(exp(X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ] %*% Theta))
+    Mx_1 <- t(X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ]) %*% 
+                  (X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ] * pi_1)
+    
+    Utility_mVc[[1]][i,3]<-det(Mx_1) #
+    
     ## mMSE
     idx.mMSE <- sample(1:n, r2[i]-r1, T, pjoin.mMSE)
     
@@ -143,6 +149,11 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates)
       
       Utility_mMSE[[j]][i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final))) #
     }
+    
+    pi_1 <-c(exp(X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ] %*% Theta)) #
+    Mx_1 <- t(X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ]) %*% 
+                  (X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ] * pi_1) 
+    Utility_mMSE[[1]][i,3]<-det(Mx_1) #
   }
   
   #Sample_mVc<-do.call(rbind,Sample.mVc) #

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/OSMAC_Model_Free_Setup.R

@@ -11,7 +11,7 @@ OSMAC_MF<-cmpfun(OSMAC_MF)
 Cordeiro<-cmpfun(Cordeiro)
 
 # Using OSMAC to Sub-sample from Big Data----
-Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N)
+Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N,Theta)
 {
   # From r0 and r conduct OSMAC subsampling for Logistic regression-----
   Parameter_mMSE<-replicate(length(combs),list()) ;
@@ -30,7 +30,7 @@ Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N)
   while(i <= Replicates)
   {
     tryCatch({
-      Results<-OSMAC_MF(r1,r2,Y,X,n=N,alpha,combs,All_Covariates)
+      Results<-OSMAC_MF(r1,r2,Y,X,n=N,alpha,combs,All_Covariates,Theta)
       
       for (j in 1:length(combs)) 
       {

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/r1_OSMAC_Algorithm_Model_Free.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two Step OSMAC ----
-OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) 
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates,Theta) 
 {
   PI.prop <- rep(1/n, n)
   
@@ -112,6 +112,12 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates)
       Utility_mVc[[j]][i,]<-cbind(r1[i],tr(V_Final),det(solve(V_Final))) #
     }
     
+    pi_1 <- c(exp(X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ] %*% Theta))
+    Mx_1 <- t(X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ]) %*% 
+                  (X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ] * pi_1)
+    
+    Utility_mVc[[1]][i,3]<-det(Mx_1) #
+    
     ## mMSE
     idx.mMSE <- sample(1:n, r2-r1[i], T, pjoin.mMSE)
     
@@ -144,6 +150,12 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates)
       
       Utility_mMSE[[j]][i,]<-cbind(r1[i],tr(V_Final),det(solve(V_Final))) #
     }
+
+    pi_1 <-c(exp(X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ] %*% Theta)) #
+    Mx_1 <- t(X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ]) %*% 
+      (X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ] * pi_1) 
+    
+    Utility_mMSE[[1]][i,3]<-det(Mx_1) #
   }
   
   #Sample_mVc<-do.call(rbind,Sample.mVc) #

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R

@@ -9,7 +9,7 @@ AlgTwoStp<-cmpfun(AlgTwoStp)
 Cordeiro<-cmpfun(Cordeiro)
 
 # Using OSMAC to Sub-sample from Big Data ----
-Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model)
+Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model,Theta)
 {
   # From r0 and r conduct OSMAC subsampling for Logistic regression-----
   Parameter_mMSE<-list()
@@ -27,7 +27,7 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model)
   while(i <= Replicates)
   {
     tryCatch({
-      Results<-AlgTwoStp(r1,r2,Y,X,Real_Data,n=N,Model)
+      Results<-AlgTwoStp(r1,r2,Y,X,Real_Data,n=N,Model,Theta)
       
       Parameter_mMSE[[i]]<-Results$opt$Est_Theta_mMSE
       Parameter_mVc[[i]]<-Results$opt$Est_Theta_mVc

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/Random_Sampling_Setup.R

@@ -17,7 +17,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Using Random Sampling Sub-sample from Big Data ----
-Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_Models)
+Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_Models,Theta)
 {
   #RandomSample<-list()
   #Sample_RS<-list()
@@ -47,7 +47,9 @@ Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_
         Temp_Temp_Data<-Temp_Data[1:Choices[j],]
         Results<-glm(Y~.-1,data=Temp_Temp_Data,family = "poisson")
         Est_Parameter[j,]<-c(Choices[j],Results$coefficients)
-        optimality[j,]<-c(Choices[j], psych::tr(vcov(Results)), det(solve(summary(Results)$cov.unscaled)) )
+        pi<-c(exp(as.matrix(Temp_Temp_Data[,-1]) %*% Theta))
+        Mx<-t(as.matrix(Temp_Temp_Data[,-1])) %*% (as.matrix(Temp_Temp_Data[,-1]) * pi)
+        optimality[j,]<-c(Choices[j], psych::tr(vcov(Results)), det(Mx) )
         Bias[j,]<-c(Choices[j],Cordeiro(XData = as.matrix(Temp_Temp_Data[,-1]),
                                         With_bias = as.vector(Results$coefficients)))
       }

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/Setup_Data.R

@@ -5,14 +5,14 @@ library(here)
 #Model_Path<-"Model_3"
 Model_Path<-"Model_4"
 
-# # Random Sampling Data ----
-# Base_Path<-"Random_Sampling"
-# 
-# ## No Correlated Covariate Data -----
-# load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
-# save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path"),
-#      file = here("Non_Identical_r0","Simulation_Setup","Analysis",
-#                  Base_Path,"Init.RData"))
+# Random Sampling Data ----
+Base_Path<-"Random_Sampling"
+
+## No Correlated Covariate Data -----
+load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
+save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path"),
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis",
+                 Base_Path,"Init.RData"))
 
 # OSMAC Data ----
 Base_Path<-"OSMAC"

### 2023-02-24 Non_Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Algorithm.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two step OSMAC ----
-AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model,Theta) {
   if(Model=="Real_Model")
   {
     PI.prop <- rep(1/n, n)
@@ -64,13 +64,15 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       ru <- length(y.mVc)
       beta.mVc[i,] <- fit.mVc$coefficients
       
-      pi<- c(exp(x.mVc %*% beta.mVc[i,]))
-      Mx<-solve(t(x.mVc) %*% (x.mVc * pi * pinv.mVc))
-      V_Temp<- t(x.mVc) %*% (x.mVc * ((as.vector(y.mVc)-pi)*pinv.mVc)^2) 
-      
+      pi<- c(exp(x.mVc %*% beta.mVc[i,])); 
+      Mx<-solve(t(x.mVc) %*% (x.mVc * pi * pinv.mVc)); 
+      V_Temp<- t(x.mVc) %*% (x.mVc * ((as.vector(y.mVc)-pi)*pinv.mVc)^2); 
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mVc[i,]<-cbind(r1[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<- c(exp(x.mVc %*% Theta))
+      Mx_1<-t(x.mVc) %*% (x.mVc * pi_1)
+      
+      Utility_mVc[i,]<-cbind(r1[i],tr(V_Final),det(Mx_1))
       Bias_mVc[i,]<-Cordeiro(XData=x.mVc,With_bias = beta.mVc[i,])
       
       ## mMSE
@@ -85,13 +87,15 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       ru <- length(y.mMSE)
       beta.mMSE[i,] <- fit.mMSE$coefficients
       
-      pi<-c(exp(x.mMSE %*% beta.mMSE[i,]))
+      pi<-c(exp(x.mMSE %*% beta.mMSE[i,])); 
[…]

### 2023-02-27 Articles.Rmd
article plots for SMSE

@@
   ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 16)
-ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 16)
+# ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
+#   ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 16)
+ggarrange(p4,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 12)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%

### 2023-03-05 Manual.Rmd
manual updated with removing classical folder from the chain

@@
 1. Random Sampling, 
-2. Rare event random sampling, 
-3. Optimal Sub-sampling (OSMAC), and
-4. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).
+2. Optimal Sub-sampling (OSMAC), and
+3. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).
 
@@
 
-#### 2.2.1.3 RE Random_Sampling_Setup.R
-
-* A setup for rare event random sampling such that model parameters and model information are estimated at each simulation and are applied for the generated big data.
-
-#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]
+#### 2.2.1.3 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]
 
@@
 
-#### 2.2.1.6 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]
+#### 2.2.1.5 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]
 
@@
 
-#### 2.2.2.2 RE Random Sampling
-
-* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
-* **RE_RandomSample.RData** - RE Random sampling function for **Replicates**.
-* **Simulation_Results_RE_Random_Sampling.R** - R script to run the rare event random sampling method over **Replicates** on the **Init.RData** from **RE_RandomSample.RData**.
-* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **RE_Random_Sample_output.RData** is stored.
-
-#### 2.2.2.3 OSMAC [Non Identical r0]
+#### 2.2.2.2 OSMAC [Non Identical r0]
 
@@
 
-#### 2.2.2.4 OSMAC Model Free [Non Identical r0]
+#### 2.2.2.3 OSMAC Model Free [Non Identical r0]
 
@@
 
-#### 2.2.2.5 OSMAC [Identical r0]
+#### 2.2.2.4 OSMAC [Identical r0]
 
@@
 
-* **RE_and_Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.
+* **Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.
 
@@
 
-* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.
+* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.
 
@@
 
-* When running the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.
+* When running the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.
 

### 2023-03-05 Manual.Rmd
updated manual with adding link for article_plots

@@
 
-* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_PR_TV_Uni_mMSE.pdf** and **SMSE_MI_PR_TV_Uni_mVc.pdf**.
+* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **Article_Plots/SMSE_MI_PR_TV_Uni_mMSE.pdf** and **Article_Plots/SMSE_MI_PR_TV_Uni_mVc.pdf**.

### 2023-03-05 Manual.Rmd
updated manual by deleting classical

@@
 
-### 2.2.1 Classical/R_Scripts
+### 2.2.1 R_Scripts
 
@@
 
-* Data stored in **Generate_Big_Data** is transferred to **Classical/Analysis**.
+* Data stored in **Generate_Big_Data** is transferred to **Analysis**.
 
@@
 
-## 2.2.2 Classical/Analysis
+## 2.2.2 Analysis
 
@@
 
-* **Summary_Rmarkdown.R** in the **Rmarkdown/Classical/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.
+* **Summary_Rmarkdown.R** in the **Rmarkdown/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.
 
@@
 
-### 2.6.1 Summary/Classical/Model_[1 or 2 or 3 or 4]/Data/Efficiency
+### 2.6.1 Summary/Model_[1 or 2 or 3 or 4]/Data/Efficiency
 
@@
 
-* Using these data files only summarising through the files in **Rmarkdown/Classical/Summary** occurs.
+* Using these data files only summarising through the files in **Rmarkdown/Summary** occurs.
 

### 2024-12-08 Final_Seminar_Presentation.Rmd
included the code for the plot that is used in the final seminar presentation

--- 2023-02-16 Articles.Rmd
@@
 ---
-title: "Articles_Plots"
+title: "Final Seminar Presentation"
 author: "Amalan"
@@
 library(xtable)
-library(flextable)
 library(grid)
@@
                                           "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"),
-                               labels = c(expression("Data Model: "*X[1]*", "*X[2]),
-                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[1]^{2}),
-                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[2]^{2}),
-                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[1]^{2}*", "*X[2]^{2})))
+                               labels = c(expression("Data Generating Model: "*X[1]*", "*X[2]),
+                                          expression("Data Generating Model: "*X[1]*", "*X[2]*", "*X[1]^{2}),
+                                          expression("Data Generating Model: "*X[1]*", "*X[2]*", "*X[2]^{2}),
+                                          expression("Data Generating Model: "*X[1]*", "*X[2]*", "*X[1]^{2}*", "*X[2]^{2})))
 
@@
                                   `RS CM` = "Random Sampling: Complex Model",
-                                  `mMSE DM`="Optimal subsampling mMSE: Data Model",
-                                  `mMSE AM 1`="Optimal subsampling mMSE: Incorrect Model 1",
-                                  `mMSE AM 2`="Optimal subsampling mMSE: Incorrect Model 2",
-                                  `mMSE AM 3`="Optimal subsampling mMSE: Incorrect Model 3",
-                                  `mMSE CM` = "Optimal subsampling mMSE: Complex Model",
-                                  `mVc DM`="Optimal subsampling mVc: Data Model",
-                                  `mVc AM 1`="Optimal subsampling mVc: Incorrect Model 1",
-                                  `mVc AM 2`="Optimal subsampling mVc: Incorrect Model 2",
-                                  `mVc AM 3`="Optimal subsampling mVc: Incorrect Model 3",
-                                  `mVc CM`="Optimal subsampling mVc: Complex Model",
+                                  `mMSE DM`="Model-based subsampling mMSE: Data Model",
+                                  `mMSE AM 1`="Model-based subsampling mMSE: Incorrect Model 1",
+                                  `mMSE AM 2`="Model-based subsampling mMSE: Incorrect Model 2",
+                                  `mMSE AM 3`="Model-based subsampling mMSE: Incorrect Model 3",
+                                  `mMSE CM` = "Model-based subsampling mMSE: Complex Model",
+                                  `mVc DM`="Model-based subsampling mVc: Data Model",
+                                  `mVc AM 1`="Model-based subsampling mVc: Incorrect Model 1",
+                                  `mVc AM 2`="Model-based subsampling mVc: Incorrect Model 2",
+                                  `mVc AM 3`="Model-based subsampling mVc: Incorrect Model 3",
+                                  `mVc CM`="Model-based subsampling mVc: Complex Model",
                                   `mMSE MR`="Model Robust subsampling mMSE: Data Model",
@@
                         #"Random Sampling: Incorrect Model 3",
-                        "Optimal subsampling mMSE: Data Model",
-                        "Optimal subsampling mMSE: Incorrect Model 1",
-                        "Optimal subsampling mMSE: Incorrect Model 2",
-                        "Optimal subsampling mMSE: Incorrect Model 3",
-                        "Optimal subsampling mMSE: Complex Model",
+                        "Model-based subsampling mMSE: Data Model",
+                        "Model-based subsampling mMSE: Incorrect Model 1",
+                        "Model-based subsampling mMSE: Incorrect Model 2",
+                        "Model-based subsampling mMSE: Incorrect Model 3",
+                        "Model-based subsampling mMSE: Complex Model",
                         "Model Robust subsampling mMSE: Data Model")
@@
 
-Selected_Models_mVc<-c("Random Sampling: Data Model",
-                       #"Random Sampling: Incorrect Model 1",
-                       #"Random Sampling: Incorrect Model 2",
-                       #"Random Sampling: Incorrect Model 3",
-                       "Optimal subsampling mVc: Data Model",
-                       "Optimal subsampling mVc: Incorrect Model 1",
-                       "Optimal subsampling mVc: Incorrect Model 2",
-                       "Optimal subsampling mVc: Incorrect Model 3",
-                       "Optimal subsampling mVc: Complex Model",
-                       "Model Robust subsampling mVc: Data Model")
-
-# Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
-#                           "#FFC4D8","#E28490","#BB2C3E","#55141C", 
-#                           "#DDCC77")
-
-Colors_mVc<-c("black",#"grey","grey","grey",
-              "#cc0000", 
-              "#ff578a","#ff578a","#ff578a","#603BDE",
-              "darkgreen")
-
-LineType_mVc<-c("twodash", 
-                "dashed",
-                "dotted","dotted","dotted","dotdash",
-                "solid")
-
-ShapeType_mVc<-c(16,
-                 1,
-                 4,4,4,3,
-                 8)
-
 Theme_special<-function()
@@
   theme(legend.key.width=unit(1,"cm"),
-        axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
-        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
-        strip.text = element_text(colour = "black",size = 12,face="bold"),
+        axis.text.x = element_text(color = "black",size=14, angle = 45, hjust=0.75), #, vjust = 0.5
+        axis.text.y = element_text(color = "black",size=14), #, vjust = 0.5, hjust=1
+        strip.text = element_text(colour = "black",size = 16,face="bold"),
         panel.grid.minor.x = element_blank(),
-        axis.title= element_text(color = "black",face = "bold",size = 12),
-        legend.text = element_text(color = "black", size=11),
+        axis.title= element_text(color = "black",face = "bold",size = 16),
+        legend.text = element_text(color = "black", size=13),
         legend.position = "bottom",
@@
 }
-
-#Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]
 
@@
 
-Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mVc)+
-  scale_linetype_manual(values=LineType_mVc)+
-  scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
-  xlab("r")+
-  ylab("Average Model Information")+expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 3))+Theme_special()->Temp_plot_mVc
-
-Temp_legend_mVc<-get_legend(Temp_plot_mVc)
-
-Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mMSE)+
-  scale_linetype_manual(values=LineType_mMSE)+
-  scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
-  xlab("r")+
-  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p1
-
-Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mVc)+
-  scale_linetype_manual(values=LineType_mVc)+
-  scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
-  xlab("r")+
-  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p2
-
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
@@
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
+  geom_point(size=2.25)+geom_line(size=2)+
   scale_color_manual(values=Colors_mMSE)+
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p3
+  theme_bw()+Theme_special()->Final_Seminar
 
-Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mVc)+
-  scale_linetype_manual(values=LineType_mVc)+
-  scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
-  xlab("r")+
-  ylab("log(SMSE)")+#expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p4
-
-Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mMSE)+
-  scale_linetype_manual(values=LineType_mMSE)+
-  scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
-  xlab("r")+
-  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p5
-
-Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mVc)+
-  scale_linetype_manual(values=LineType_mVc)+
-  scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
-  xlab("r")+
-  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p6
-
-Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mMSE)+
-  scale_linetype_manual(values=LineType_mMSE)+
-  scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
-  xlab("r")+
-  ylab("log(SMSE)")+#expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p7
-
-Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.25)+geom_line(size=0.75)+
-  scale_color_manual(values=Colors_mVc)+
-  scale_linetype_manual(values=LineType_mVc)+
-  scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2, labeller = label_parsed)+
-  xlab("r")+
-  ylab("log(SMSE)")+#expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+Theme_special()->p8
-
-ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
-ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
-ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
-ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
-ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
-ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
-
-ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 16)
-ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 16)
-ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 12)
-ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 12)
-
-ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mMSE.pdf"),res=300,width = 12,height = 12)
-ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mVc.pdf"),res=300,width = 12,height = 12)
-
-ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggsave(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mMSE.eps"),device="eps",dpi=300,width = 12,height = 16)
-ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-  ggsave(filename = here("Article_Plots","SMSE_MI_PR_TV_Uni_mVc.eps"),device="eps",dpi=300,width = 12,height = 16)
-ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggsave(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mMSE.eps"),device="eps",dpi=300,width = 12,height = 12)
-ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggsave(filename = here("Article_Plots","ACCURACY_PR_TV_Uni_mVc.eps"),device="eps",dpi=300,width = 12,height = 12)
-
-ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mMSE.eps"),res=300,width = 12,height = 12)
-ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Uni_mVc.eps"),res=300,width = 12,height = 12)
+ggarrange(Final_Seminar,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggsave(filename = here("Article_Plots","Model_Robust_Results_1.png"),dpi=300,width = 16,height = 14)
 ```
